### 2018-09-03 Kolmogorov_Approx.tex
Initial ShareLaTeX Import

\def\year{2019}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai19}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required

\usepackage{amssymb}
\usepackage{amsmath,amsthm}
\usepackage{float}
\usepackage{url}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{amsthm} 
\usepackage[ruled,vlined,linesnumbered]{algorithm2e} 
\usepackage{makecell}
\usepackage{upgreek}
\onehalfspacing
\usepackage{pdfpages}
\usepackage{times}
\usepackage{multirow}
\usepackage[toc,page]{appendix}
\usepackage{listings}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{definition}[thm]{Definition}
\newtheorem{observation}[thm]{Observation}
\newtheorem{theorem}[thm]{Theorem}
\newtheorem{claim}[thm]{Claim}
\newtheorem{example}[thm]{Example}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{corollary}[thm]{Corollary}
\usepackage{color,soul}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes.geometric,shapes.arrows}
\usepackage{pgfplots}
\usepackage{multirow}

\DeclareMathOperator{\supp}{support}
\DeclareMathOperator{\support}{support}
\DeclareMathOperator{\Trim}{Trim}
\DeclareMathOperator{\LTrim}{LTrim}
\SetKwFunction{mEqOne}{mEqOne} 
\DeclareMathOperator{\KlmApprox}{KolmogorovApprox}
%\DeclareMathOperator{\OptTrim}{KolmogorovApprox}
\DeclareMathOperator{\OptTrim}{OptTrim}

  \pdfinfo{
	/Title (Deadline estimation by using an optimal approximation of discrete random variables with respect to the Kolmogorov distance
	)
	/Author ()}
\setcounter{secnumdepth}{0}

\begin{document}

\title{Optimal Approximation of Discrete Random Variables \\ for Estimation of Probabilities of Missing Deadlines}
\author{}
\maketitle
\begin{abstract}
We present an efficient algorithm that, given a discrete random variable $X$ and a number $m$, computes a random variable whose support if of size at most $m$ and whose Kolmogorov distance from $X$ is minimal. We present the algorithm, analyse its correctness and computational complexity, and present a detailed empirical evaluation that shows how it performs in practice. The main application that we examine, which is our motivation for this work, is estimation of the probability missing deadlines in series-parallel schedules. Since exact computation of these probabilities is NP-hard, we propose to use the algorithm described in this paper to obtain an approximation.   
\end{abstract}

\section{Introduction}

Various approaches for approximation of probability distributions are studied in the literature~\cite{AMCR83,pavlikov2016cvar,PS77,vidyasagar2012metric,cohen2015estimating,CohenGW18}. 
These approaches vary in the types random variables considered, how they are represented, and in the criteria used for evaluation of the quality of the approximations. In this paper we propose an approach for compressing the probability mass function of a random variable $X$ such that the errors added to queries such as $Pr(X\leq t)$, for  any $t>0$, is minimal. In other words, we minimise the Kolmogorov distance between the approximation and the original random variable. Our motivation for this is estimation of the probability for missing deadlines, as described, e.g.,in~\cite{cohen2015estimating} and in~\cite{Kashef18}. Specifically, when $X$ represents the probability distribution of the time to complete some complex schedule and we cannot afford to maintain the full table of its probability mass function, we propose an algorithm for producing a smaller table, whose size can be specified, such that probabilities for missing deadlines are preserved as much as possible.

The main contribution of this paper is an efficient algorithm for computing the best possible approximation of a given random variable with a random variable whose size is not above a prescribed threshold, where the measures of the quality of the approximation and of its size are as specified in the following two paragraphs.

We measure the quality of an approximation scheme by the distance between random variables and their approximations. Specifically, we use the Kolmogorov distance which is  commonly used for comparing random variables in statistical practice and literature. Given two random variables $X$ and $X'$ whose cumulative distribution functions (cdf) are $F_X$ and $F_{X'}$, respectively, the Kolmogorov distance between $X$ and $X'$ is $d_K(X,X')= \sup_t |F_X(t) - F_{X'}(t)|$ (see, e.g.,~\cite{gibbons2011nonparametric}). We say that $X'$ is a good approximation of $X$ if $d_K(X,X')$ is small. This distance is the basis for the often used Kolmogorov-Smirnoff test for comparing a sample to a distribution or two samples to each other.

The size of a random variable is measured here by the size of its support, the set of possible outcomes, $m=|\support(X)|=|\{x\colon Pr(X=x) \neq 0\}|$. When probability mass functions are maintained as explicit tables, as done in many implementations of statistical software, the size of the support of the variable is proportional to the amount of memory needed to store it and to the complexity of the computations that manipulate it.

Together, the exact notion of optimality of the approximation targeted in this paper is:
\begin{definition}
	A random variable $X'$ is an optimal $m$-approximation of a random variable $X$ if $|\support(X')| \leq m$ and there is no random variable $X''$ such that $|\support(X'')| \leq m$ and $d_K(X,X'') < d_K(X,X')$.
\end{definition}

In these terms, the main contribution of the paper is an efficient (polynomial time and memory) algorithm that takes $X$ and $m$ as parameters and constructs an optimal $m$-approximation of $X$.

The rest of the paper is organised as follows. In Section~\ref{sec:relwork} we describe how our work relates to other algorithms and problems studied in the literature. In Section~\ref{sec:alg} we detail the proposed algorithm, analyse its properties, and prove the main theorem. In Section~\ref{sec:exp} we demonstrate how the proposed approach performs on the problem of estimating the probability of missing deadlines in series-parallel schedules on randomly generated random variables and compare it to alternative approximation approaches from the literature. The paper is concluded with a discussion and with ideas for future work in Section~\ref{sec:discussion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related work}\label{sec:relwork}
The most relevant work related to this paper is the papers on approximations of random variables in the context of estimating deadlines~\cite{cohen2015estimating,CohenGW18}. In these papers, $X'$ is defined to be a good approximation of $X$ if $F_{X'}(t) > F_{X}(t)$ for any $t$ and $\sup_t F_{X'}(t) - F_{X}(t)$ is small. Note that this measure is not a proper distance measure because it is not symmetric. The motivation given in these papers for using this type of approximation is for cases where overestimation of the probability of missing a deadline is acceptable but underestimation is not. In Section~\ref{sec:exp}, we consider the same case-studies examined by Cohen et al. and show how the algorithm proposed in this paper performs relative to the algorithms proposed there when both over- and under- estimations are allowed. As expected, the Kolmogorov distance between the approximated and the original random variable is considerably smaller when using the algorithm proposed in this paper.

In the technical level, the problem we study in this paper is similar to the problem of approximating a set of 2-D points by a step function. The study of this problem was motivated by query optimisation and histogram constructions in database management systems~\cite{applf12,applf13,applf14,applf17,applf18,Fournier2011}. There are, however, two technically significant differences between the problem studied in the context of databases and the problem we analyse in this paper. The first difference is that in the context of approximation of random variables, the step function (which is the cumulative distribution function in our context)  must end with a value one, since we are dealing with random variables which sums to one. The second difference is that the first step is not counted because there is no need to put a value in the support of the approximated random variable to generate this first step. These cannot be addressed by adding a constant (two) to $m$ because the first step is always present and because the requirement to end with the value one, restricts the set of eligible step functions. See Section~\ref{sec:alg} for more details.

Another relevant prior work is the theory of Sparse Approximation (aka Sparse Representation) that deals with sparse solutions for systems of linear equations, as follows. 
Given a matrix $D \in \mathbb{R}^{n \times p}$ and a vector $x \in \mathbb{R}^n$, the most studied sparse representation problem is finding the sparsest possible representation $\alpha \in \mathbb{R}^p$ satisfying $x = D\alpha$:
\[
\min_{\alpha \in \mathbb{R}^p} \|\alpha\|_0 \text{ subject to } x = D\alpha
\]
where $\|\alpha\|_0 = |\{ i \in [p]: \alpha_i \neq 0 \}|$ is the $\ell_0$ pseudo-norm, counting the number of non-zero coordinates of $\alpha$. This problem is known to be NP-hard with a reduction to NP-complete subset selection problems.
In these terms, using also the $\ell_\infty$ norm that represents the maximal coordinate and the $\ell_1$ norm that represents the sum of the coordinates, our problem can be phrased as:
\[
\min_{\alpha \in [0,\infty)^p}\|x - D\alpha\|_{\infty} \text{ subject to }  \|\alpha\|_0 = m \text{ and } \|\alpha\|_1=1
\]
where $D$ is the lower unitriangular matrix, $x$ is related to $X$ such that the $i$th coordinate of $x$ is $F_X(x_i)$ where $\support(X)=\{x_1 < \cdots < x_n\}$ and $\alpha$ is related to $X'$ such that the $i$th coordinate of $\alpha$ is $f_{X'}(x_i)$. The functions $F_X$ and $f_{X'}$ represent, respectively, the cumulative distribution function of $X$ and the mass distribution function of $X'$, i.e.,  the coordinates of $x$ are positive and monotonically increasing and its last coordinate is one. We show that this specific sparse representation problem can be solved in $O(n^2m)$ time and $O(m^2)$ memory.

%The presented work is also related to the research on binning in statistical inference. Consider, for example, the problem of credit scoring~\cite{zeng2017comparison} that deals with separating good applicants from bad applicants where the Kolmogorov–Smirnov statistic KS is a standard measure. The KS comparison is often preceded by a procedure called binning where small values in the the probability mass function are moved to nearby values. There are many methods for binning~\cite{mays2001handbook,refaat2011credit,bolton2010logistic,siddiqi2012credit}.
%In this context, our algorithm can be considered as a binning strategy that provides optimality guarantees with respect to the Kolmogorov distance.

Our study is also related to the work of Pavlikov and Uryasev~\cite{pavlikov2016cvar}, where a procedure for producing a random variable $X'$ that optimally approximates a random variable $X$ is presented. Their approximation scheme, achieved using linear programming, is designed for a different notion of distance called CVaR. The contribution of the present work in this context is that our method is direct, not using linear programming, thus allowing tighter analysis of time and memory complexities. Also, our method is designed for minimising the Kolmogorov distance that is more prevalent in applications. For comparison, in Section~\ref{sec:exp} we briefly discuss the performance of linear programming approach similar to the one proposed in~\cite{pavlikov2016cvar} for the Kolmogorov distance and compare it our algorithm.

A problem very similar to ours is termed ``order reduction'' by Vidyasagar in~\cite{vidyasagar2012metric}. There, the author defines an information-theoretic based distance between discrete random variables and studies the problem of finding a variable whose support is of size $m$ and its distance from $X$ is as small as possible (where $X$ and $m$ are given). The only difference between this and the problem studied in this paper, is that Vidyasagar examines a different notion of distance. Vidyasagar proves that computing the distance (that he considers) between two probability distributions, and computing the optimal reduced order approximation, are both NP-hard problems, because they can both be reduced to nonstandard bin-packing problems. He then develops efficient greedy approximation algorithms. In contrast, our study shows that there are efficient solutions to these problems when the Kolmogorov distance is considered.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{An algorithm for optimal approximation}\label{sec:algEfficient}

\begin{algorithm}
	\DontPrintSemicolon
	Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.\;
    $f \gets 0$, $l \gets n$+1\; 
    \While{$c_{f +1} \leq \varepsilon$}{$f \gets f + 1$}

    \While{$c_{l -1} \geq  1-\varepsilon$}{$l \gets l -1$}

	$S \gets \emptyset$, $s \gets 0$,$b \gets f$, $e \gets f$\;
	\While{$e<l$}{
	    \While{$c_{e+1}-c_{b} \leq 2\varepsilon \wedge e+1 <l$}{$e \gets e+1$}
	    $S \gets S \cup \{(x_{b}, (c_b+c_e)/2 - s) \}$\;
        $s \gets  (c_b+c_e)/2$, $b \gets e+1$\;
	}
	$S \gets S \cup \{(x_{l}, 1 - s) \}$\;
    \Return{A r.v. $X'$ such that $Pr(X'{=}x)=c$ if there is $c$ such that $(x, c) \in S$ and $Pr(X'{=}x)=0$ otherwise.}

	\caption{$dual(X,\varepsilon)$}   
	\label{alg:dual}
\end{algorithm}

\SetKwRepeat{Do}{do}{while}
%which c? why -s? name without any meaning, cant understand

\begin{theorem}\label{the:complexityDual}
	The $dual(X,\varepsilon)$ algorithm runs in time $O(n)$, using $O(n)$ memory where $n=|\support(X)|$.
\end{theorem}
\begin{proof}
	This algorithm describes one pass over the random variable $X$. Lines 3-4 and lines 5-6 are easy to follow, each takes $O(n)$ in the worst case. Lines 8-12 also describe one pass over $X$ since the counter $e$ is updated to $e+1$ at most $n$ times. All together we get run-time complexity of $O(3n)$ = $O(n)$. We are constructing the set $S$ which is of size $n$ in the worst case, therefore, memory complexity is also $O(n)$. 
\end{proof}

\begin{algorithm}
	\DontPrintSemicolon
	Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $Pr(X \leq x_i)=c_i$ and $\supp(X)=\{x_1 < \cdots < x_n\}$.\;
    $E \gets \emptyset$\; 
    \For{$i \gets 1$ \textbf{to} $n-1$}{
    	\For{$j \gets i+1$ \textbf{to} $n-1$}{
        		\If{$i=1$} {
                	$E \gets E \cup \{ c_j \}$
                }
        		$E \gets E \cup \{ (c_j-c_i)/2 \}$
        }
        $E \gets E \cup \{ 1 - c_i \}$
    }
    Let $e_1<\cdots<e_{n'}$ be such that $E=\{e_1,\dots,e_{n'}\}$ \;

    \For{$i \gets 1 \textbf{ to } 2$}{
        $l\gets 1$, $r \gets n'$, $k \gets 1$ \;
        \Do{$k \neq k'$}{
                $k' \gets k$,$k \gets \lceil (l + r)/2 \rceil$\;
        		$X' \gets dual(X,e_k)$, $m' \gets |\supp(X')|$\;
        		\lIf{$m' < m$}{
        		    $l \gets k$
        		}
                \lIf{$m' > m$}{
        		    $r \gets k-1$
        		}
                \lIf{$m' = m$}{
        		    $r \gets k$
        		}
        }
        $m \gets m'$\;
    }
    \Return{X'}

	\caption{$approx(X,m)$}   
	\label{alg:naive}
\end{algorithm}

\begin{theorem}\label{the:complexityDual}
	The $approx(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|\support(X)|$.
\end{theorem}
\begin{proof}
	In the first part of the algorithm, lines 2-8, we construct the set $E$ which takes $O(n^2)$ run-time. In the second part of the algorithm, line 9, we sort the set $E$ which takes $O(n^2log(n^2)) = O(n^2log(n))$  run-time. The third part of the algorithm, lines 10-19, describes a binary sort over the set $E$ where in each step of the sort we run the $dual$ algorithm, which takes $O(n log(n^2)) = O(n log(n))$ run-time. We run this part twice then we get $O(2n log(n))$. All together, the run-time complexity is $O(n^2+n^2log(n)+2n log(n)) = O(n^2log(n))$ and the memory complexity is for set $E$ which is $n^2$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{An algorithm for optimal approximation}\label{sec:alg}
In the scope of this section, let $X$ be a given random variable with a finite support of size $n$, and let  $0<m\leq n$ be a given complexity bound. The section evolves by developing notations and by collecting facts towards an algorithm for finding an optimal $m$-approximation of $X$.

The first useful fact is that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:

\begin{lemma}\label{lem:supContained}
	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
\end{lemma}

\begin{proof}
	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.  Since we only "shifted" the probability mass of $X''$ to the support of $X$, we have that $f_{X'}$ is a probability mass function and therefore $X'$ is well defined. 	
	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
\end{proof}

%Next, note that every random variable $X''$ with support of size at most $m$ that is contained in $\support(X)$ can be described by first setting the (at most $m$) elements of the support of $X''$; then for every such option, determine $X''$ by setting probability values for the elements in the chosen support of $X'$, and setting $0$ for rest of the elements.

For a set $S\subseteq \support(X)$, let $\mathbb{X}_S$ denote the set of random variables whose supports are contained in $S$. In Step 1 below, we identify a random variable in $\mathbb{X}_S$  that minimizes the Kolmogorov distance from $X$. We denote the Kolmogorov distance between this variable and $X$ by $\varepsilon(X,S)$. Then, in Step 2, we show how to efficiently find a set $S \subseteq \support(X)$ whose size is smaller or equal to $m$ that minimizes $\varepsilon(X,S)$. Then, in Step 3, an optimal $m$-approximation is constructed by taking a minimal approximation in $\mathbb{X}_S$ where $S$ is the set of size $m$ that that minimizes $\varepsilon(X,S)$.

\subsection*{Step 1: Finding an $X'$ in $\mathbb{X}_S$ that minimizes $d_K(X,X')$}

We first fix a set $S\subseteq \support(X)$ and among all the random variables in $\mathbb{X}_S$ find one with a minimal distance from $X$. Denote the elements of $S$ in increasing order by $S=\{x_1<\dots<x_m\}$ and let $x_0=-\infty$ and $x_{m+1}=\infty$. Consider the following weight function:

\begin{definition}\label{def:weight} For $0\leq i \leq m$ let
	\[
	w(x_i,x_{i+1})=
	\begin{cases}
	P(x_i < X < x_{i+1}) & \text{if $i=0$ or $i = m$;} \\
	P(x_i < X < x_{i+1})/2 & \text{otherwise.} \\	
	\end{cases}
	\]
\end{definition}
For each $1 <  i \leq m$ let $\hat x_i$ be the maximal element of $\support(X)$ that is smaller than $x_i$. 
Note that, for $1\leq i \leq m$, $P(x_i < X < x_{i+1}) = F_X(\hat x_{i+1}) - F_X(x_i)$, a fact that we will use throughout this section.

\begin{definition}\label{def:error}
Let $\varepsilon(X,S) = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$.
\end{definition}

We first show that $\varepsilon(X,S)$ is a lower bound for the distance between random variable in $\mathbb{X}_S$ and $X$. Then, we present a random variable $X'\in \mathbb{X}_S$ such that $d_K(X,X')=\varepsilon(X,S)$. It then follows that $X'$ is closets to $X$ in $\mathbb{X}_S$.

%The intuition behind choosing these specific weights and $\varepsilon(X,S)$ being a lower bound is as follows.  Since for every $X'\in\mathbb{X}_S$ the probability mass of $X'$ for the elements not in $S$ are set to $0$, we have that $F_{X'}(\hat x_{i+1})=F_{X'}(x_i)$. Therefore the distance between $X'$ and $X$ at points $x_i$ and $\hat x_{i+1}$ that we have to take into additional account is increased by $F_X(\hat x_{i+1})-F_X(x_i) = P(x_i < X < x_{i+1})$.

%Formally we have the following.

\begin{proposition}\label{prop:minimal}
	If $X'\in\mathbb{X}_S$ then $d_K(X,X') \geq \varepsilon(X,S)$.
\end{proposition}

\begin{proof}

	By definition, for each $0\leq i\leq m$, $d_K(X,X') \geq \max \{|F_X(\hat x_{i+1}) - F_{X'}(\hat x_{i+1})|,|F_X(x_i) - F_{X'}(x_i)| \}$. Note that $F_{X'}(\hat x_{i+1})=F_{X'}(x_i)$ since the probability of  elements not in $S$ is  $0$.

	If $i=0$, that is $x_i=-\infty$, we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ and therefore $d_K(X,X') \geq |F_X(\hat x_{i+1})| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1})= w(x_i,x_{i+1})$.

	If $i =m$, that is $x_{i+1}=\infty$, we have that $F_X(\hat x_{i+1})=F_{X'}(\hat x_{i+1})=F_{X'}(x_i)=1$. 
	and therefore $d_K(X,X') \geq |1-F_X(\hat x_i)| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1}) = w(x_i,x_{i+1})$.

	%  we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ 
	% 
	% 
	% 
	% We break the proof for the closed intervals where each support variable $x_i$ is a proper number, and for the open intervals where a support variable is either $-\infty$ or $\infty$.

	Otherwise for every $1\leq i< m$,  we use the fact that $max\{|a|,|b|\} \geq |a-b|/2$ for every $a,b\in\mathbb{R}$, to deduce that $d_K(X,X') \geq 1/2| F_X(\hat x_{i+1}) - F_X(x_i) + F_{X'}(x_i) -F_{X'}(\hat x_{i+1})|$. So $d_K(X,X') \geq 1/2| F_X(\hat x_{i+1}) - F_X(x_i) | =P(x_1 < X < x_2)/2 = w(x_i,x_{i+1})$.

Since $d_K(X,X') {\geq}  w(x_i,x_{i+1})$ for any $0{\leq} i{\leq} m$, the proof follows by the definition of $\varepsilon(X,S)$.
\end{proof}

We next describe a random variable $X'\in\mathbb{X}_S$ in a distance of $\varepsilon(X,S)$ from $X$ by its probability mass function:

\begin{definition}\label{def:construction}
	Let $f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
\end{definition}

We first show that $X'$ is a properly defined random variable:

\begin{lemma}
	$f_{X'}$ is a probability mass function. 
\end{lemma}

\begin{proof}
	By definition $f_{X'}(x_{i})\geq 0$ for every $i$. To see that $\sum_i f_{X'}(x_{i}) =1$, 
	we have $\sum_i f_{X'}(x_{i}) = \sum_i (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) = 	
	\sum _{x_i\in S} f_{X}(x_i)) + w(x_0,x_1)+ \sum_{0 < i < m} 2 w(x_i,x_{i+1}) + w(x_m,x_{m+1}) = 
	\sum _{x_i\in S} P(X{=}x_i) + P(x_0 {<} X {<} x_1)+ \sum_{0 < i < m} P(x_i < X < x_{i+1}) +P(x_m < X < x_{m+1}) = 1$ since this is the entire support of $X$.	
\end{proof}

Note that, given $S$, $X'$ can be constructed in time linear in the size of the support of $X$.
Its main property, of course, is that the distance between the cumulative distribution functions of $X$ and of $X'$ are bounded by $w(x_i,x_{i+1})$, as follows:
\begin{lemma}\label{lem:balance}
	Let $x\in\support(X)$ and $0\leq i\leq m$ be such that $x_i\leq x \leq x_{i+1}$ then 
    \[
    -w(x_i,x_{i+1})\leq F_X(x)-F_{X'}(x)\leq  w(x_i,x_{i+1}).
    \]
    \end{lemma}

\begin{proof}	
	By induction on $i$.	First see that $F_{X'}(x) = 0$  for every $x_0<x < x_1$ and therefore $F_X(x)-F_{X'}(x) = F_X(x)-0 \leq F_X(\hat x_1)= F_X(\hat x_1)- F_X(x_0) = w(x_0,x_1)$. For $ x = x_1$ we have $F_X(x_1)-F_{X'}(x_1)=  F_X(\hat x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1) = 
	w(x_0,x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)) = -w(x_1,x_2)$.

	Next assume that $F_X(\hat x_i)-F_{X'}(\hat x_i) = w(x_{i-1},x_i)$.
	Then $F_X(x_i)-F_{X'}(x_i) =  F_X(\hat x_i) +f_{X}(x_i) - (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) =  w(x_{i-1},x_i) +f_{X}(x_{i}) - (w(x_{i-1},x_i) + w(x_{i},x_{i+1}) + f_{X}(x_{i})) = -w(x_{i},x_{i+1})$.

	As before we have that for all $x_i< x< x_{i+1}$, we have $F_X(x)-F_{X'}(x) = F_X(x)-F_{X'}(\hat x_{i+1}) \leq  F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1})$. Then $F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1}) = (F_X(x_i)+ P(x_i < x <x_{i+1})) - F_{X'}(x_i) = -w(x_{i},x_{i+1}) + 2w(x_{i},x_{i+1}) = w(x_{i},x_{i+1}) $.

	Finally, for $x_m\leq x \leq x_{m+1}$ we have that $F_{X'}(x_m)=1$ therefore $F_X(x_m)-F_{X'}(x_m) = (1- P(x_m<X < x_{m+1})) - 1 =  P(x_m<X < x_{m+1}) = w(x_m,x_{m+1})$, and for every $x_m<x<x_{m+1}$ we have $F_X(x) - F_{X'}(x) < (1- P(x_m<X < x_{m+1})) - 1 <  - P(x_m<X < x_{m+1}))  = -w(x_m,x_{m+1})$ as required.
\end{proof}

From Lemma \ref{lem:balance}, by the definition of $\varepsilon(X,S)$, we then have:
\begin{corollary} \label{col:Xprime}
	$d_K(X,X') = \varepsilon(X,S)$.
\end{corollary}
From Proposition~\ref{prop:minimal} we also have:
\begin{corollary} \label{col:Xprimeopt}
	$\varepsilon(X,S)$ is the Kolmogorov distance between $X$ and the variables closest to it in $\mathbb{X}_S$.
\end{corollary}

%\begin{proof}
%	We first see by induction that for every $1\leq i \leq m$ that $F_X(\hat x_i)-F_{X'}(\hat x_i)=w(x_{i-1},x_i)$ and $F_X(x_i)-F_{X'}(x_i) = -w(x_i,x_{i+1})$. 
%	
%	For $i=1$ we have  $F_X(\hat x_1)-F_{X'}(\hat x_1)= F_X(\hat x_1)-0 =  F_X(\hat x_1)- F_X(x_0) = w(x_0,x_1)$.
%	Then $F_X(x_i)-F_{X'}(x_i)=  F_X(\hat x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)| = 
%	w(x_0,x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)) = -w(x_1,x_2)$.
%	
%	Assume that $F_X(x_i)-F_{X'}(x_i) = -w(x_i,x_{i+1})$. Then $F_X(\hat x_{i+1})-F_{X'}(\hat x_{i}) = (F_X(x_i)+ P(x_i<X<x_{i+1}))-F_{X'}(x_i) = -w(x_i,x_{i+1})+2w(x_i,x_{i+1})=w(x_i,x_{i+1})$.
%	Therefore, we have $F_X(x_{i+1})-F_{X'}(x_{i+1}) = F_X(\hat x_{i+1}) +f_{X}(x_{i+1}) - (w(x_i,x_{i+1}) + w(x_{i+1},x_{i+2}) + f_{X}(x_{i+1})| = 
%	w(x_i,x_{i+1}) +f_{X}(x_{i+1}) - (w(x_i,x_{i+1}) + w(x_{i+1},x_{i+2}) + f_{X}(x_{i+1})) = -w(x_{i+1},x_{i+2})$.
%	
%	
%	[[DF: read again and see if special instructions are required for $i=0,m$, the last one]]
%	
%	
%	Finally see that for every $x_i<x< x_{i+1}\in \support(X)$, $F_{X'}(j)= F_{X'}(x_i) = F_{X'}(\hat x_{i+1}) $ and therefore  $-w(x_i,x_{i+1}) = F_X(x_i)-F_{X'}(x_i) \leq F_X(j)-F_{X'}(j)\leq F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1}) = w(x_i,x_{i+1})$. Therefore $|F_X(j)-F_{X'}(j)|\leq w(x_i,x_{i+1})$.
%	
%	Therefore for every $j\in \support(X)$ we have that $|F_X(j)-F_{X'}(j)|\leq max_i(w(x_i,x_{i+1})=\varepsilon(X,S)$. as required.	
%\end{proof}

%\begin{itemize}
%	\item The next lemma states a lower bound on the distance $d_K(X,X')$ when a range of elements is excluded from the support of $X'$.
%\end{itemize}
%
%
%\begin{lemma}\label{lem:geq}
%	For $x_1, x_2 \in \support(X) \cup \{-\infty,\infty\}$ such that $x_1 < x_2$, if $P(x_1 < X' < x_2)=0$  then 
%	$d_k(X,X') \geq P(x_1 < X < x_2)/2$.
%\end{lemma}
%\begin{proof}
%	Let $\hat x=\max \{x \in \support(X) \cap\{ -\infty, \infty\}  \colon x < x_2 \}$. By definition, $d_k(X,X') \geq \max \{|F_X(x_1) - F_{X'}(x_1)|, |F_X(\hat x) - F_{X'}(\hat x)| \}$. From Observation~\ref{obs:ab}, $d_k(X,X') \geq 1/2|F_X(x_1) - F_X(\hat x) + F_{X'}(\hat x) - F_{X'}(x_1)|$. Since it is given that $F_{X'}(\hat x) - F_{X'}(x_1) = P(x_1 < X' < x_2)=0$, $d_k(X,X') \geq 1/2|F_X(x_1) - F_X(\hat x) | =  P(x_1 < X \leq \hat x)/2 = P(x_1 < X < x_2)/2$.
%\end{proof}
%
%
%\begin{itemize}
%	\item The next lemma strengthen the lower bound.
%\end{itemize}
%
%
%\begin{lemma}\label{lem:geq2}
%	For $x_1, x_2 \in \support(X) \cup \{-\infty,\infty\}$ such that $x_1=-\infty$ or  $x_2=\infty$, if $P(x_1 < X' < x_2)=0$  then 
%	$d_k(X,X') \geq P(x_1 < X < x_2)$.
%\end{lemma}
%\begin{proof}
%	Let $\hat x=\max \{x \in \support(X) \cap\{ -\infty, \infty\}  \colon x < x_2 \}$. By definition $d_k(X,X') \geq \max \{|F_X(x_1) - F_{X'}(x_1)|, |F_X(\hat x) - F_{X'}(\hat x)| \}$. If $x_1=-\infty$ then $d_k(X,X') \geq \{|F_X(\hat x) - F_{X'}(\hat x)| \}$ since $F_X(-\infty) = F_{X'}(-\infty) = 0$. Furthermore, $F_{X'}(\hat x) = P(x_1 < X' < x_2)=0$. Therefore $d_k(X,X') \geq F_X(\hat x) = P(x_1 < X \leq \hat x) = P(x_1 < X < x_2)$. 
%	If $x_2=\infty$ then $d_k(X,X') \geq \{|F_X(x_1) - F_{X'}(x_1)| \}$ since $F_X(\hat{x}) = F_{X'}(\hat{x}) = F_X(\infty) = F_{X'}(\infty) = 1$. Furthermore, $F_{X'}(x_1) = 1$ since it is given that $P(x_1 < X' < x_2)=0$. Therefore we get that $d_k(X,X') \geq |F_X(x_1)-1| = |1-F_X(\hat x)-| = P(x_1 < X \leq \hat x) = P(x_1 < X < x_2)$.
%\end{proof}
%
%
%\begin{definition}\label{def:weight} For $x_1,x_2 \in \support(X) \cup \{-\infty,\infty\}$ let
%	\[
%	w(x_1,x_2)=
%	\begin{cases}
%	P(x_1 < X < x_2) & \text{if $x_1=-\infty$ or $x_2 = \infty$;} \\
%	P(x_1 < X < x_2)/2 & \text{otherwise.} \\	
%	\end{cases}
%	\]
%\end{definition} 
%
%
%\begin{definition}\label{def:error} For $S=\{x_1<\dots<x_m\} \subseteq \support(X)$, $x_0=-\infty$, and $x_{m+1}=\infty$, let
%	\[
%	\varepsilon(X,S) = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1}).
%	\]
%\end{definition} 
%
%\begin{itemize}
%	\item From here on, until the end of the section, $S$ is fixed.
%\end{itemize}

%
%\begin{proposition}
%	There is no $X'$ such that $\support(X')=S$ and $d_k(X,X') < \varepsilon(X,S)$.
%\end{proposition}
%\begin{proof}
%	Let $i$ be the index that maximizes $w(x_{i}, x_{i+1})$. If $0<i<n-1$ then $d_k(X,X') \geq w(x_{i}, x_{i+1})$ by Lemma~\ref{lem:geq}. If $i=0$ or $i=n+1$ the same follows from Lemma~\ref{lem:geq2}.
%\end{proof}

%
%\begin{lemma}
%	For $i>1$, if $F_{X'}(x_{i})-F_{X}(x_{i}) = w(x_{i}, x_{i+1})$ then $F_{X'}(x_{i+1})-F_{X}(x_{i+1}) = w(x_{i+1}, x_{i+2})$.
%\end{lemma}
%\begin{proof}
%	\begin{align}
%	&F_{X'}(x_{i+1})-F_{X}(x_{i+1}) = \\ \nonumber
%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - P(X<x_{i+1}) + P(X'<x_{i+1})  \\ \nonumber
%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - F_X(x_{i}) - P(x_{i}< X < x_{i+1}) + F_{X'}(x_{i}) \\ 
%	\label{eq:weight}
%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - F_X(x_{i}) - 2w(x_{i},x_{i+1}) + F_{X'}(x_{i})  \\ \label{eq:indHip}
%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - 2w(x_{i},x_{i+1}) +w(x_{i}, x_{i+1})  \\ \label{eq:construction}
%	& = w(x_{i},x_{i+1}) +w(x_{i+1},x_{i+2}) - 2w(x_{i},x_{i+1}) +w(x_{i}, x_{i+1}) \\ \nonumber
%	& = w(x_{i+1},x_{i+2}) \nonumber
%	\end{align}
%	
%	By Definition~\ref{def:weight} the probability $P(x_{i-1}< X < x_i) = 2w(x_{i-1},x_{i})$ as in Equation~\eqref{eq:weight}. Equation~\eqref{eq:indHip} is deduced by the induction hypothesis and Equation~\eqref{eq:construction} where
%	$f_{X'}(x_i) - f_{X}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1})$ is true by construction, see Definition\ref{def:construction}.
%\end{proof}

%\begin{lemma}
%	For $i>1$, if $F_{X'}(x_{i-1})-F_{X}(x_{i-1}) = w(x_{i-1}, x_{i})$ then $F_{X'}(x_{i})-F_{X}(x_i) = w(x_i, x_{i+1})$.
%\end{lemma}
%\begin{proof}
%	% TODO switch tdirections to fit the statement of the lemma
%	% TODO \eqref,  aligment
%	\begin{align}
%	&F_X(x_i)-F_{X'}(x_i) = \\
%	&f_{X}(x_i) - f_{X'}(x_i) + P(X<x_i) - P(X'<x_i)  = \\ \nonumber
%	&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + P(x_{i-1}< X < x_i)-F_{X'}(x_{i-1}) = \\
%	&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + 2w(x_{i-1},x_{i})-F_{X'}(x_{i-1}) =^* \\
%	&f_{X}(x_i) - f_{X'}(x_i) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) = \\
%	& -w(x_{i-1},x_i) - w(x_i,x_{i+1}) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) =\\ 
%	&- w(x_i,x_{i+1})
%	\end{align}
%	$*$ by induction hypothesis.
%	The probability $P(x_{i-1}< X < x_i) = 2w(x_{i-1},x_{i})$ by Definition~\ref{def:weight}, and
%	$f_{X'}(x_i) - f_{X}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1})$ by construction.
%\end{proof}
%
%\begin{lemma}
%	Base case: $i = 1, F_{X'}(x_{1})-F_{X}(x_{1}) = w(x_{1}, x_{2})$.
%\end{lemma}
%\begin{proof}
%	\begin{align*}
%	F_{X'}(x_{1})-F_{X}(x_{1}) &= \\
%	& = f_{X'}(x_{1}) - f_{X}(x_{1}) - w(x_0, x_1)  \\
%	& = w(x_{0},x_1) + w(x_1,x_{2}) - w(x_0, x_1)  \\
%	& = w(x_1,x_{2})
%	\end{align*}
%\end{proof}
%
%
%

%\begin{proof}
%	Define $X'$ to by $f_{X'}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
%	We need to show that $F_X(x_i)-F_{X'}(x_i) = -w(x_i, x_{i+1})$. Assume this is true for every $j<i$, the induction hypothesis hereby: $F_X(x_{i-1})-F_{X'}(x_{i-1}) = -w(x_{i-1}, x_{i})$.
%	\begin{align*}
%		&F_X(x_i)-F_{X'}(x_i) = \\
%		&f_{X}(x_i) - f_{X'}(x_i) + P(X<x_i) - P(X'<x_i)  = \\
%		&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + P(x_{i-1}< X < x_i)-F_{X'}(x_{i-1}) = \\
%		&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + 2w(x_{i-1},x_{i})-F_{X'}(x_{i-1}) =^* \\
%		&f_{X}(x_i) - f_{X'}(x_i) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) = \\
%		& -w(x_{i-1},x_i) - w(x_i,x_{i+1}) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) =\\ 
%		&- w(x_i,x_{i+1})
%	\end{align*}
%	$*$ by induction hypothesis.
%	The probability $P(x_{i-1}< X < x_i) = 2w(x_{i-1},x_{i})$ by definition~\ref{def:weight}, and
%	$f_{X'}(x_i) - f_{X}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1})$ by construction.
%	
%\end{proof}

%\begin{proposition}
%	For any random variable $X$ and an ordered set $S=\{x_1<\dots<x_m\} \subset \support(X)$ there is no random variable $X'$ such that $\support(X')=S$ and $d_k(X,X') < \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$ where, to simplify notations, we assume that $x_0=-\infty$ and $x_{m+1}=\infty$.
%\end{proposition}
%
%\begin{proof}
%	Let $i$ be the index that maximizes $w(x_{i}, x_{i+1})$. If $0<i<n-1$ then $d_k(X,X') \geq w(x_{i}, x_{i+1})$ by Lemma~\ref{lem:geq}. If $i=0$ or $i=n+1$ the same follows from Lemma~\ref{lem:geq2}.
%\end{proof}
%
%\begin{itemize}
%	\item The next lemma shows that there is a n not better approximation. 
%\end{itemize}
%
%
%
%\begin{proposition}
%	For any random variable $X$ and an ordered set $S=\{x_1<\dots<x_m\} \subset \support(X)$ there is a random variable $X'$ such that $\support(X')=S$ and $d_k(X,X') = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$ where, to simplify notations, we assume that $x_0=-\infty$ and $x_{m+1}=\infty$.
%\end{proposition}
%\begin{proof}
%Define $X'$ to by $f_{X'}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
%\end{proof}

%%%%%%%%%%%%%%%%%%%% New sec 3.2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Step 2: Finding a set $S$ that minimizes $\varepsilon(X,S)$}

We proceed to finding a set $S$ of size $m$ that minimizes $\varepsilon(X,S)$. To obtain that we use a graph search approach inspired by~\cite{chakravarty1982partitioning}. We construct a directed graph with a source and a target in which each source-to-target path of length smaller or equal to $m$ corresponds to a possible support set of the same size, and the weights along that path correspond to the weight as defined in Definition~\ref{def:weight}. Thus the problem of finding an $S$ of size $m$ that minimizes $\varepsilon(X,S)$ is reduced to the problem of finding a source-to-target path $\vec{p}$ of length smaller or equal to $m$ in that graph such that the maximal weight of an edge in $\vec{p}$ is minimal among all other such maximal edges in all other such paths.

More specifically, the vertices of the graph are $V=\support(X) \cup \{-\infty,\infty\}$ and the edges, $E$, are all the pairs $(x_1,x_2) \in V^2$ such that $x_1 < x_2$. The weight 
of each edge is as specified in Definition~\ref{def:weight}. Note that there is a one-to-one correspondence between a set $S \subseteq \support(X)$ of size $m$, and an $-\infty$-to-$\infty$ path $\vec{p}_S$ in $G$, obtained by removing the $-\infty$ and $\infty$ from the path in one direction and by adding these elements and sorting in the other direction. 
With this correspondence, the maximal weight of an edge on $\vec{p}_S$ is $\varepsilon(X,S)$. We denote this maximal weight of an edge  by $w(\vec{p}_S)$, and denote the set of all acyclic $-\infty$-to-$\infty$ paths in $G$ with at most $m$ edges by $paths_m(G, -\infty, \infty)$. Thus, the problem of finding the set $S$ with the minimal  $\varepsilon(X,S)$ is now reduced to the problem of finding a path $\vec{p}\in paths_m(G, -\infty, \infty)$ such that $w(\vec{p})$ is minimal among all $\{w(\vec{p'}) \colon \vec{p'}\in paths_m(G, -\infty, \infty)\}$. 
This problem can be solved by a variant of the Bellman-Ford algorithm and by the algorithm described in~\cite{guerin2002computing} that performs better in some cases.

%\begin{corollary}\label{cor:Bellman}
%$BellmanFord(G,m)$ returns a path $\vec{p}\in paths_m(G, s, t)$ such that $w(\vec{p})$ is minimal among all $\{w(\vec{p'}) | \vec{p'}\in paths_m(G, s, t)\}$.
%\end{corollary}

\subsection*{Step 3: Constructing the overall algorithm}

We combine Step 1 and Step 2 in the following algorithm called $\KlmApprox$ (Algorithm~\ref{alg:optapprox}) that follows naturally from the two steps. Given $X$ and $\support(X)$ we add $x_0=\infty,x_{n+1}=-\infty$ and construct the graph (line 2) as described  in Step 2 above. Then we execute a variant of the Bellman-Ford algorithm on $G$ for $m$ iterations, or the algorithm proposed in~\cite{guerin2002computing}, to obtain a path $\vec{p}$ (line 2). Finally, we use Definition~\ref{def:construction} to construct $X'$ from $\vec{p}$ (line 3).

\begin{algorithm}\label{alg:optapprox}
	%\setstretch{1.5}
	\DontPrintSemicolon
	Construct a weighted graph $G=(V,E)$ where $V=\support(X) \cup \{-\infty,\infty\}$, $E=\{(x_1,x_2) \in V^2\colon x_1 < x_2 \}$, and the weights are as in Definition~\ref{def:weight}.\; \vspace{0.2cm}

	Find a path $\vec{p}=(x_0,\dots,x_{m+1})\in paths_m(G, -\infty, \infty)\}$ such that $w(\vec{p}) = \min \{w(\vec{p}) \colon \vec{p}\in paths_m(G, -\infty, \infty)\}$.   \; 	\vspace{0.2cm}

	Return a random variable whose probability mass function is 
		$f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for all $i=1,\dots,m$ and zero otherwise. \;

	\caption{$\KlmApprox (X, m)$}  
	\label{alg:sequence}
\end{algorithm}

%\begin{algorithm}\label{alg:optapprox}
%	\DontPrintSemicolon
%	\SetKwFunction{Convolv}{Conv}
%	\SetKwFunction{getPartition}{getPartition}
%	\SetKwFunction{bellmanFordMinMaxM}{bellmanFordMinMaxM}
%	$\support(X)\cup \{x_0,x_{n+1}\}$\;
%	Construct $G=(V,E,s,t,w)$ according to Step 2 \;
%	$\vec{p}=(v_0,\dots,v_{m+1}) = Belmman-Ford(G,m)$  \;
%	\For{$0<i<m+1$ }{
%		$f_{X'}(x_{i}) = w(v_{i-1},v_i) + w(v_i,v_{i+1}) + f_{X}(x_i)$
%	}	
%	\Return $X'$\;
%	
%	\caption{$\KlmApprox (X, m)$}  
%	\label{alg:sequence}
%\end{algorithm}

\begin{theorem}\label{the:algo}
	$\KlmApprox$ returns an $m$-optimal-approximation of $X$.
\end{theorem}
\begin{proof}
By the construction of $G$ we get that the path $\vec{p}$ obtained in line 2 of  $\KlmApprox$ describes a set $S$ of support of size at most $m$ for which $\varepsilon(S,X)$ is minimal. Then from Definition \ref{def:construction} and Corollary \ref{col:Xprime} we construct $X'$ in lines 3 of 	$\KlmApprox$ such that $d_K(X,X') = \varepsilon(X,S)$. Therefore $X'$ is closets to $X$ among all random variables with support contained in $\support(X)$. From Lemma \ref{lem:supContained} we then get that $X'$ is an $m$-optimal-approximation of $X$.
\end{proof}

The memory and time  complexities of $\KlmApprox$ are as follows.

\begin{theorem}\label{the:complexity}
	The $\KlmApprox(X,m)$ algorithm runs in time $O(n^2m)$, using $O(n^2)$ memory where $n=|\support(X)|$.
\end{theorem}
\begin{proof}
	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory. Computing the shortest path can be achieved, for example, by the algorithm described in~\cite{guerin2002computing} in time $O(n^2 m)$ and no additional memory allocation.
\end{proof}
%\begin{proof}
%	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory. The number of edges in $G$ is $O(|E|)=O(n^2)$, for every edge the weight is at most the sum of all
%probabilities between the source node $s$ and the target node $t$, which can be calculated efficiently by aggregating the weights of already calculated edges. 
%	The construction is also the only stage that requires memory allocation, specifically $O(|E|+|V|)=O(n^2)$.
%	Next using the Bellman-Ford algorithm on $G$ for $m$ iterations   takes $O(m(|E|+|V|))\approx O(mn^2)$. [[DF: cite Corman or some algorithms book]]. 
%	Finally deriving the new random variable $X'$ from the computed path $\vec{p}$ takes $O(m)$ time: For every node $x_i$ in $\vec{p}$ (at most $m$ nodes), use the already calculated weights to find the probability mass function $f_{X'}(x_i)$. 
%	To conclude, the time complexity  of $\KlmApprox(X,m)$ is $O(n^2+mn^2+m)=O(mn^2)$ and memory complexity is $O(E+V)=O(n^2)$.
%\end{proof}

%%%%%%%%%OLD SEC 3.2 %%%%%%%%%%%%%%%%%%%%%%%%%%%5

%\subsection{Step 2: Finding an $S$ that minimizes $\varepsilon(X,S)$}
%Chakravarty, Orlin, and Rothblum~\cite{chakravarty1982partitioning} proposed a polynomial-time method that, given a certain objective functions (additive), finds an optimal consecutive partition. Their method involves the construction of a graph such that the (consecutive) set partitioning problem is reduced to the problem of finding the shortest path in that graph.

%The $\KlmApprox$ algorithm (Algorithm~\ref{alg:optapprox}) starts by constructing a directed weighted graph $G$ similar to the method of Chakravarty, Orlin, and Rothblum~\cite{chakravarty1982partitioning}. The nodes $V$ consist of the support of $X$ together with an extra two nodes, $-\infty$ and $\infty$ for technical reasons, whereas the edges $E$ connect every pair of nodes in one direction (lines 1-2). The weight $w$ of each edge $e=(x,y)\in E$ is determined by one of two cases as in Definition~\ref{def:weight}. 
%If nodes $x$ or $y$ are the $-\infty$ or $\infty$ nodes respectively then the weight is the probability of $X$ to get a value between $x$ and $y$, non inclusive, i.e., $w(e)=Pr(x<X<y)$. If $x$ and $y$ are not a $-\infty$ or $\infty$ nodes, here the weight is the probability of $X$ to get a value between $x$ and $y$, non inclusive, divided by two i.e., $w(e)=Pr(x<X<y)/2$. 
%The values taken are non inclusive, since we are interested only in the error value. The source node of the shortest path problem at hand corresponds to the $-\infty$ node added to $G$ in the construction phase, and the target node is the extra node $\infty$.
%The set of all solution paths in $G$, i.e., those starting at $-\infty$ and ending in $\infty$ with at most $m$ edges, is called $paths(G, -\infty, \infty)$. The goal is to find the path $l$ in $paths(G, -\infty, \infty)$ with the lightest bottleneck (line 3). This can be achieved by using the $Bellman-Ford$ algorithm with two tweaks. The first is to iterate the graph $G$ in order to find only paths with length of at most $m$ edges. The second is to find the lightest bottleneck as opposed to the traditional objective of finding the shortest path. This is performed by modifying the manner of ``relaxation'' to $bottleneck(x) = min[max(bottleneck(v),w(e))]$, done also in~\cite{guerin2002computing, shufan2011two}. Consequently, we find the lightest maximal edge in a path of length $\leq m$, which represents the minimal error, $\varepsilon(X,S)$, defined in Definition~\ref{def:error} where the nodes in path $l$ represent the elements in set $S$. The approximated random variable $X'$ is then derived from the resulting path $l$ (lines 4-5). Every node $x\in l$ represent a value in the new calculated random variable $X'$, we than iterate the path $l$ to find the probability of the event $f_{X'}(x)$ as described in Definition~\ref{def:construction}.

%\begin{algorithm}\label{alg:optapprox}
%	\DontPrintSemicolon
%	\SetKwFunction{Convolv}{Conv}
%	\SetKwFunction{getPartition}{getPartition}
%	\SetKwFunction{bellmanFordMinMaxM}{bellmanFordMinMaxM}
%	$S = \support(X)\cup \{\infty,-\infty\}$\;
%	$G=(V,E)=(S, \{ (x,y)  \colon  x<y \})$  \;
%	$(x_0,\dots,x_{m+1}) = l \in \operatorname{argmin}\limits_{l \in paths(G,-\infty,\infty),|l|\leq m}  \max \{ w(e)\colon e \in l  \}$  \;
%	\For{$0<i<m+1$ }{
%		$f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$
%	}	
%	\Return $X'$\;
%	
%	\caption{$\KlmApprox (X, m)$}  
%	\label{alg:sequence}
%\end{algorithm}

%\begin{algorithm}\label{alg:optapprox}
%	\DontPrintSemicolon
%	\SetKwFunction{Convolv}{Conv}
%	\SetKwFunction{getPartition}{getPartition}
%	\SetKwFunction{bellmanFordMinMaxM}{bellmanFordMinMaxM}
%	$S = \support(X)\cup \{\infty,-\infty\}$\;
%	$G=(V,E)=(S, \{e= (x,y) \in S^2 \colon  x<y \})$ \;
%	
%	\ForEach{$e=(x,y) \in  E $ }{
%		\If {$i=\infty \text{ OR } j=-\infty$}{
%			$w(e) = Pr(i<X<j)$
%		}
%		\Else{$w(e) = Pr(i<X<j)/2$}
%	}
%	
%	/* The following can be obtained, e.g., using the Bellman-Ford algorithm */\;
%	$l^*= \operatorname{argmin}\limits_{l \in paths(G, -\infty, \infty,|l|\leq m}  \max \{ w(e)\colon e \in l  \}$ \;
%	
%	\ForEach{$e=(i,j) \in  l^* $ }{
%		\If {$i=-\infty$}{
%			$f_{X'}(j) = f_{X}(j) + Pr(i\leq X<j)$
%		}
%		\ElseIf{$j==\infty$}{
%			$f_{X'}(i) = f_{X'}(i) + Pr(i\leq X<j)$
%		}
%		\Else{
%			$f_{X'}(i) = f_{X'}(i) + Pr(i\leq X<j)/2$\;
%			$f_{X'}(j) = f_{X}(j) + Pr(i\leq X<j)/2$\;
%		}
%		
%	}	
%	\Return $X'$\;
%	
%	\caption{$\KlmApprox (X, m)$}  
%	\label{alg:sequence}
%\end{algorithm}

%\begin{theorem}\label{the:algo}
%	$\KlmApprox(X,m)$ is an $m$-optimal-approximation of $X$.
%\end{theorem}
%\begin{proof}
%If we consider the vertexes $S= l \setminus \{-\infty,\infty\}$ for a path $l \in paths(G,-\infty,\infty)$ we have that $\max \{ w(e)\colon e \in l  \} = \varepsilon(X,S)$. Therefore, line 3 of the algorithm essentially computes a set $S \in \operatorname{argmin}_{S \subseteq \support(X), |S|\leq m} \varepsilon(X,S)$. By Corollary~\ref{col:Xprime}, the variable $X'$ constructed in lines 4 and 5 satisfies $d_K(X,X') = \varepsilon(X,S)$ and by the minimality of $S$ and by Proposition~\ref{prop:minimal}, it is an optimal approximation.
%\end{proof}

%\begin{theorem}\label{the:complexity}
%	The $\KlmApprox(X,m)$ algorithm runs in time $O(mn^2)$, using $O(n^2)$ memory where $n=|\support(X)|$.
%\end{theorem}

%\begin{proof}
%	Constructing the graph $G$ takes $O(n^2)$. The number of edges is $O(E)\approx O(n^2)$ and for every edge the weight is at most the sum of all probabilities between the source node $-\infty$ and the target node $\infty$, which can be done efficiently by aggregating the weights of already calculated edges. 
%	The construction is also the only stage that requires memory allocation, specifically $O(E+V)=O(n^2)$.
%	Finding the shortest path takes $O(m(E+V))\approx O(mn^2)$.

%	[[GW: put a reference to the work of the fellows from the Technion to avoid some of this?]]

%	Since $G$ is DAG (directed acyclic graph) finding a shortest path takes $O(E+V)$. We only need to find paths of length $\leq m$, which takes $O(m(E+V))$.
%	Deriving the new random variable $X'$ from the computed path $l$ takes $O(m)$. For every node $x_i$ in $l$ (at most $m$ nodes), use the already calculated weights to find the probability mass function $f_{X'}(x_i)$. 
%	To conclude, the worst case run-time complexity is $O(n^2+mn^2+m)=O(mn^2)$ and memory complexity is $O(E+V)=O(n^2)$.
%\end{proof}

\section{Experimental evaluation}\label{sec:exp}

We describe below several experiments that show how $\KlmApprox$ performs in practice in different applications and domains.
All algorithms were implemented in Python and the experiments were executed on a hardware comprised of an Intel i5-6500 CPU @ 3.20GHz processor and 8GB memory. The algorithms of Cohen et al. were taken "as is" from in the supplementary material to~\cite{cohen2015estimating}.

\paragraph{Repetitive support size minimization.} One use of support size minimization is when commutations that involve summations of random variables slow due to an exponential growth in the support of convolutions of random variables~\cite{cohen2015estimating}. A key action in coping with this situation is reduction of the  support size by replacing the summed random variable by an approximation of it that has a smaller support size. Previous work such as the work of Cohen et al. in ~\cite{cohen2015estimating,CohenGW18} handle this reduction using weaker or sub-optimal notion of approximation than ours, as discussed in Section~\ref{sec:relwork}.

As proven in Section~\ref{sec:alg}, given $m$, a single step of $\KlmApprox$ guarantees an optimal $m$-approximation. However in the setting considered here we need to repetitively use $\KlmApprox$, thus the optimality of the eventually obtained random variable is not guaranteed. In light of this, we tested the accuracy of the repetitive-$\KlmApprox$ to see how it performs against the tools of~\cite{cohen2015estimating,CohenGW18} using their benchmarks. These benchmarks are taken from the area of task trees with deadlines, a sub area of the well-established Hierarchical planning~\cite{thomas1988hierarchical,alford2016hierarchical,xiao2017hierarchical}.

%The case study examined in our experiments is the problem of task trees with deadlines~\cite{cohen2015estimating,CohenGW18}. Hierarchical planning is a well-established field in AI~\cite{thomas1988hierarchical,erol1994htn,erol1996complexity}, and is still relevant nowadays~\cite{alford2016hierarchical,xiao2017hierarchical}. A hierarchical plan is a method for representing problems of automated planning in which the dependency among tasks can be given in the form of networks, here we focus on hierarchical plans represented by task trees. The leaves in a task tree are \emph{primitive} actions (or tasks), and the internal nodes are either \emph{sequence} or \emph{parallel} actions. The plans we deal with are of stochastic nature, and the task duration is described as probability distributions in the leaf nodes. We assume that the distributions are independent but {\em not} necessarily identically distributed and that the random variables are discrete and have a finite support.

%A sequence node denotes a series of tasks that should be performed consecutively, whereas a parallel node denotes a set of tasks that begin at the same time. A \emph{valid} plan is one that is fulfilled before some given \emph{deadline}, i.e., its \emph{makespan} is less than or equal to the deadline. The objective in this context is to compute the probability that a given plan is valid, or more formally computing $P(X<T)$, where $X$ is a random variable representing the makespan of the plan and $T$ is the deadline. The problem of finding the probability that a task tree satisfies a deadline is known to be NP-hard. In fact, even the problem of summing a set of random variables is NP-hard~\cite{mohring2001scheduling}. This is an example of an explicitly given random variable that we need to estimate deadline meeting probabilities for.

%The first experiment we focus on is the problem of task trees with deadlines, and consider three types of task trees. The first type includes logistic problems of transporting packages by trucks and airplanes (from IPC2 http://ipc.icaps-conference.org/). Hierarchical plans of those logistic problems were generated by the JSHOP2 planner \cite{nau2003shop2}, one parallel node with all descendant task nodes being in sequence. 
%The second type consists of task trees used as execution plans for the ROBIL team entry in the DARPA robotics challenge (DRC simulation phase), and the third type is of linear plans (sequential task trees).
%The primitive tasks in all the trees are modeled as discrete random variables with support of size $M$ obtained by discretization of uniform distributions over various intervals. The number of tasks in a tree is denoted by $N$.

We estimated the probability for meeting deadlines in plans, as described in~~\cite{cohen2015estimating,CohenGW18}, and experimented with four different methods of approximation. The first two, $\OptTrim$~\cite{CohenGW18} and the $\Trim$~\cite{cohen2015estimating}, are taken from the repository provided by the authors and are designed for achieving only a one-sided Kolmogorov approximation - a  weaker notion of approximation then the Kolmogorov approximation analyzed in this work. The third method is a simple sampling scheme and the fourth is our Kolmogorov approximation obtained by the proposed $\KlmApprox$ algorithm. The parameters for the different methods were chosen in a compatible way, $M$ is the maximal support size, $N$ is the number of nodes of the plan network and $s$ is the number of samples. We ran also an exact computation as a reference to the approximated one in order to calculate the errors.

\begin{table}[th]
	\scriptsize
	\centering
	\renewcommand{\arraystretch}{1.3}
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		\multirow{2}{*}{Task Tree} & \multirow{2}{*}{$M$} & {Kolmogorov} & {$\OptTrim$} & {$\Trim$} & \multicolumn{2}{c|}{Sampling} \\ \cline{3-7} 
		&	& $m/N{=}10$ & $m/N{=}10$ & $\varepsilon\cdot N{=}0.1$ & $s{=}10^{4}$& $s{=}10^{6}$ \\ \hline
		\hline

		%N=34

		\multirow{2}{*}{Logistics} & 2& 0 & 0 &  0.0019 &  0.007 & 0.0009  \\ \Xcline{2-7}{1pt}
		{\tiny $(N=34)$}& 4& 0.0024 & 0.0046&  0.0068  &   0.0057 & 0.0005 \\\Xhline{1pt}

		%N=47
		\multirow{2}{*}{DRC-Drive}  
		&2	& 0.0014 & 0.004&  0.009  & 0.0072 & 0.0009  
		\\ \Xcline{2-7}{1pt}

		{\tiny $(N{=}47)$}& {4}& 0.001 & 0.008&  0.019   & 0.0075  & 0.0011 
		\\  \Xhline{1pt}

		%N=10
		\multirow{2}{*}{Sequential}  & {2} & 0.0093 & 0.015 &  0.024 & 0.0063 & 0.0008 \\ \Xcline{2-7}{1pt}  
		{\tiny $(N{=}10)$} & {4} & 0.008 & 0.024 &  0.04 & 0.008 & 0.0016 \\ \Xhline{1pt}

	\end{tabular}
	\caption{Comparison of estimated errors with respect to the reference exact computation on various task trees.}
	\label{tab:errors}
\end{table}

Table~\ref{tab:errors} shows the results of the experiment. The quality of the solutions obtained with the $\KlmApprox$ operator are better than those obtained by the $\Trim$ and $\OptTrim$ operators as expected. In some of the task trees, the sampling method produced better results than the approximation algorithm with $\KlmApprox$. Still, the $\KlmApprox$ approximation algorithm comes with an inherent advantage of providing an exact quality guarantees, as opposed to sampling where the best one can hope for is probabilistic guarantees.

\paragraph{Run time comparison.}
Similarly to accuracy and error computation, we also conducted empirical evaluation to examine the run-time in practice of the discussed algorithms. Figure~\ref{fig:runtime} presents a comparison of the run-time performances of an exact computation and approximated computations with $\KlmApprox$ and $\Trim$ as operators. We examined three versions of $KlmApprox$ each of which with different run-time,  The computation is a summation of a sequence of random variables with support size of $m{=}10$, where the number $n$ of variables varies from 6 to 19. In this experiment, we executed the $\KlmApprox$ operator with $m{=}10$ after performing each convolution between two random variables, in order to maintain a support size of 10 in all intermediate computations. 
Equivalently, we executed the $\Trim$ operator with $\varepsilon=0.1$.
The results clearly show the exponential run-time of the exact computation, caused by the convolution between two consecutive random variables. In fact, in the experiment with $N{=}20$, the exact computation ran out of memory. These results illuminate the advantage of the proposed $\KlmApprox$ algorithm that balances between solution quality and run-time performance -- while there exist other, faster, methods (e.g., $\Trim$), $\KlmApprox$ provides high-quality solutions in reasonable (polynomial) time, which is especially important when an exact computation is not feasible, due to time or memory.

\begin{figure}[htb]
    \label{fig:runtime}
	\scriptsize	
	\centering 
	\begin{tikzpicture}
	\begin{axis}[
	scale=.95,
    ymode=log,
	xlabel={Number of variables},
	ylabel={Run-time (seconds)},
	xmin=6, xmax=19,
	ymin=0, ymax=327,
	xtick={6,10,15,19},
	legend pos=outer north east,
	ymajorgrids=true,
	grid style=dashed,
	]

	\addplot[
	color=blue,
	mark=square,
	]
	coordinates { 
		(6 , 0.967791080475) 
		(7 , 1.26214194298) 
		(8 , 1.60830593109) 
		(9 , 1.97642302513) 
		(10, 2.28711390495) 
		(11, 2.67097711563) 
		(12, 3.01373195648) 
		(13, 3.3420279026) 
		(14, 3.71830201149) 
		(15, 4.08019995689) 
		(16, 4.3857190609) 
		(17, 5.30444002151)
		(18, 5.97745299339) 
		(19, 5.91222810745) 
	};
	\addlegendentry{$\OptTrim$}

    \addplot[
	color=black,
	mark=square,
	]
	coordinates { 
		(6 , 0.630314826965332) 
		(7 , 0.7709379196166992) 
		(8 , 0.7499942779541016) 
		(9 , 0.8746609687805176) 
		(10, 1.208768367767334) 
		(11, 1.1908512115478516) 
		(12, 1.3902842998504639) 
		(13, 1.6106953620910645) 
		(14, 1.7124199867248535) 
        (15, 1.7134194374084473)
		(16, 2.345730781555176) 
		(17, 2.131302833557129) 
		(18, 2.1731927394866943)
		(19, 2.9610767364501953) 
	};
	\addlegendentry{Kolmogorov Approx}

	\addplot[
	color=green,
	mark=x,
	]
	coordinates {
		(6  , 0.000465154647827)
		(7  , 0.000580787658691)
		(8  , 0.000672817230225)
		(9  , 0.000787973403931)
		(10 , 0.000914096832275)
		(11 , 0.00101804733276)
		(12 , 0.00112104415894)
		(13 , 0.0012149810791)
		(14 , 0.00134491920471)
		(15 , 0.00143694877625)
		(16 , 0.00155091285706)
		(17 , 0.00166893005371)
		(18 , 0.00178194046021)
		(19 , 0.00198793411255)
	};
	\addlegendentry{$\Trim$}

	\addplot[
	color=red,
	mark=x,
	]
	coordinates {
		(6  , 0.00977492332458)
		(7  , 0.0880949497223)
		(8  , 0.556006193161)
		(9  , 1.23386096954)
		(10 , 2.37807798386)
		(11 , 4.2376730442)
		(12 , 6.03167200089)
		(13 , 8.61568593979)
		(14 , 14.1664741039)
		(15 , 21.7874569893)
		(16 , 30.5902190208)
		(17 , 97.9485061169)
		(18, 186.025614977) 
		(19, 327.884781122) 
	};
	\addlegendentry{Exact (no trimming)}

	\addplot[
	color=orange,
	mark=x,
	]
	coordinates {
		(6  , 0.003989458084106445)
		(7  , 0.00398707389831543)
		(8  , 0.004992485046386719)
		(9  , 0.006980419158935547)
		(10 , 0.008974790573120117)
		(11 , 0.010970354080200195)
		(12 , 0.007979631423950195)
		(13 , 0.00997161865234375)
		(14 , 0.013960838317871094)
		(15 , 0.014958381652832031)
		(16 , 0.017947673797607422)
		(17 , 0.017951011657714844)
		(18, 0.018949508666992188) 
		(19, 0.026926517486572266) 
	};
	\addlegendentry{$nlog(n) \OptTrim$}

    \addplot[
	color=pink,
	mark=x,
	]
	coordinates {
		(6  , 0.04986763000488281)
		(7  , 0.0747988224029541)
		(8  , 0.0827784538269043)
		(9  , 0.11668658256530762)
		(10 , 0.12765932083129883)
		(11 , 0.14760947227478027)
		(12 , 0.16057085990905762)
		(13 , 0.23337483406066895)
		(14 , 0.1884934902191162)
		(15 , 0.2094745635986328)
		(16 , 0.23337602615356445)
		(17 , 0.3201446533203125)
		(18, 0.3011953830718994) 
		(19, 0.3091733455657959) 
	};
	\addlegendentry{$n^2log(n) \OptTrim$}
	\end{axis}
	\end{tikzpicture}
	\caption{Run-time of a long computation with $\OptTrim$, with $\Trim$, and without any trimming (exact computation).}
	\label{fig:runtime}
\end{figure}
\paragraph{Single step support minimisation.}
In order to better understand the quality gaps in practice between $\KlmApprox$, $\OptTrim$, and $\Trim$, we tested their relative errors when applied on single random variables with support size $n = 100$, and different $m$s. Note that the error obtained by $\KlmApprox$ is optimal while the other methods are not optimised for the Kolmogorv distance. In each instance of this experiment, a random variable is randomly generated by choosing the probabilities of each element in the support uniformly and then normalising these probabilities so that they sum to one.

Figure~\ref{fig:error} presents the error produced by the above methods. The depicted results are averages over fifty instances of random variables. The curves in the figure show the average error of $\OptTrim$ and $\Trim$ operators with comparison to the average error of the optimal approximation provided by $\KlmApprox$ as a function of $m$. It is evident from this graphs that increasing the support size of the approximation $m$ reduces the error, as expected, in all three methods. However, the (optimal) errors produced by the $\KlmApprox$ are significantly smaller, a half of the error produced by $\OptTrim$ and $\Trim$.

\begin{figure}[htb]
	\scriptsize	
	\centering 
	\begin{tikzpicture}
	\begin{axis}[
	scale=.8,
	xlabel={Support size, $m$},
	ylabel={Error, $d_K(X,X')$},
	xmin=2, xmax=50,
	ymin=0, ymax=0.5,
	xtick={2,4,8,10,20,50},
	legend pos=north west,
	ymajorgrids=true,
	grid style=dashed,
	]

	\addplot[
	color=blue,
	mark=square,
	]
	coordinates { 
		(2 , 0.246) 
		(4 , 0.121) 
		(8 , 0.0591) 
		(10 , 0.046) 
		(20, 0.0215) 
		(50, 0.0068)

	};
	\addlegendentry{$\KlmApprox$}

	\addplot[
	color=green,
	mark=x,
	]
	coordinates {
		(2 , 0.491) 
		(4 , 0.2428) 
		(8 , 0.1184) 
		(10 , 0.0929) 
		(20, 0.0430) 
		(50, 0.0136) 
	};
	\addlegendentry{$\OptTrim$}

	\addplot[
	color=red,
	mark=x,
	]
	coordinates {
		(2 , 0.494) 
		(4 , 0.2473) 
		(8 , 0.124) 
		(10 , 0.0988) 
		(20, 0.0494) 
		(50, 0.01971)  
	};
	\addlegendentry{$\Trim$}

	\end{axis}
	\end{tikzpicture}
	\caption{Error comparison between $\KlmApprox$, $\OptTrim$, and $\Trim$ on randomly generated random variables as function of $m$.}
	\label{fig:error}
\end{figure}

\paragraph{Comparison to Linear Programming.}
We also compared the run-time of $\KlmApprox$ with a linear programing (LP) algorithm that also guarantees optimality, as described and discussed for example in~\cite{pavlikov2016cvar}.
For that, we used the ``Minimize'' function of Wolfram Mathematica as a  state-of-the-art implementation of linear programing, encoding the problem by the LP problem $\min_{\alpha \in \mathbb{R}^n} \| x - \alpha\|_\infty$ subject to $\|\alpha\|_0 \leq m$ and $\| \alpha \|_1 =1$.
The run-time comparison results were clear and persuasive: $\KlmApprox$ significantly outperforms the LP algorithm. For a random variable with support size $n=10$ and $m=5$, the LP algorithm run-time was $850$ seconds, where the $\KlmApprox$ algorithm run-time was less than a tenth of a second. For $n=100$ and $m=5$, the $\KlmApprox$ algorithm run-time was 0.14 seconds and the LP algorithm took more than a day. 
Since it is not trivial to formally analyze the run-time of the LP algorithm, we conclude by the reported experiment that in this case the LP algorithm might not be as efficient as $\KlmApprox$ algorithm whose complexity is proven to be polynomial in Theorem~\ref{the:complexity}.

\section{Discussion and future work}\label{sec:discussion}
%Compact representations of distributions is mentioned in the literature in various contexts for various applications. In this paper, we are interested in finding optimal approximation of a random variables under the Kolmogorov metric which we define as optimal $m$-approximation. In order to achieve this optimal approximation two steps were taken, find the support of the optimal random variable and then calculate the pmf of each and every value in that support to minimize the error. Proofs of existences, optimality and run-time were detailed in Section~\ref{sec:alg} and the main algorithm was presented, the $\KlmApprox$ algorithm. Establishing the main contribution of this paper which is to present an optimal approximation scheme and to show it can be achieved in polynomial run-time. Furthermore, empirical evaluation was conducted on different domains and application to examine the algorithm performance in practice. We were interested in two aspects of performance - accuracy and run-time. Regarding to accuracy, as expected, the suggested $\KlmApprox$ algorithm results much smaller error compared to the other methods, sometimes, in more then factor 0f 2. Regarding to run-time, $\KlmApprox$ algorithm run-time is significantly much faster then LP approach. However, compared to other approximation methods accuracy vs. run-time is a trade off yet to be examined. Another interesting experiment that can be conducted in future work is to add the presented approach as one of the methods examined in~\cite{zeng2017comparison} and compare it to the binning approaches.

We developed an algorithm for computing optimal approximations of random variables where the approximation quality is measured by the Kolmogorov distance.
As demonstrated in the experiments, our algorithm improves on the approach of Cohen et al.~\cite{cohen2015estimating} and~\cite{CohenGW18} in that it finds an optimal two sided Kolmogorov approximation, and not just one sided. Beyond the Kolmogorov measure studied here we believe that similar approaches may apply also to total variation, to the Wasserstein distance, and to other measures of approximations. Another direction for future work is extensions to tables that represent other objects, not necessarily random variables. To this end, we need to extend the algorithm to support tables that do not always sum to one and tables that may contain negative entries.

\bibliographystyle{aaai}
\bibliography{library,Trim_Optimum}

\end{document}

### 2018-09-03 Kolmogorov_Approx.tex
Updates from ShareLaTeX

@@
 In the second part of the algorithm, line 9, we sort the set $E$ which takes $O(n^2log(n^2)) = O(n^2log(n))$  run-time.
-The third part of the algorithm, lines 10-19, describes a binary sort over the set $E$ where in each step of the sort we run the $dual$ algorithm, which takes $O(n log(n^2)) = O(n log(n))$ run-time.
+The third part of the algorithm, lines 10-19, describes a binary sort over the set $E$ where in each step of the sorting we run the $dual$ algorithm, which takes $O(n log(n^2)) = O(n log(n))$ run-time.
 We run this part twice then we get $O(2n log(n))$.

### 2018-09-05 Kolmogorov_Approx.tex
Updates from ShareLaTeX

@@
 \SetKwFunction{mEqOne}{mEqOne} 
-\DeclareMathOperator{\KlmApprox}{KolmogorovApprox}
+\DeclareMathOperator{\KlmApprox}{Approx}
 %\DeclareMathOperator{\OptTrim}{KolmogorovApprox}
@@
 
+The case study examined in this paper is the problem of task trees with deadlines~\cite{cohen2015estimating,CohenGW18}.
+Hierarchical planning is a well-established field in AI~\cite{thomas1988hierarchical,erol1994htn,erol1996complexity}, and is still relevant nowadays~\cite{alford2016hierarchical,xiao2017hierarchical}.
+A hierarchical plan is a method for representing problems of automated planning in which the dependency among tasks can be given in the form of networks, here we focus on hierarchical plans represented by task trees.
+The leaves in a task tree are \emph{primitive} actions (or tasks), and the internal nodes are either \emph{sequence} or \emph{parallel} actions.
+The plans we deal with are of stochastic nature, and the task duration is described as probability distributions in the leaf nodes.
+We assume that the distributions are independent but {\em not} necessarily identically distributed and that the random variables are discrete and have a finite support.
+
+A sequence node denotes a series of tasks that should be performed consecutively, whereas a parallel node denotes a set of tasks that begin at the same time.
+A \emph{valid} plan is one that is fulfilled before some given \emph{deadline}, i.e., its \emph{makespan} is less than or equal to the deadline.
+The objective in this context is to compute the probability that a given plan is valid, or more formally computing $P(X<T)$, where $X$ is a random variable representing the makespan of the plan and $T$ is the deadline.
+The problem of finding the probability that a task tree satisfies a deadline is known to be NP-hard~\cite{mohring2001scheduling}.
+In fact, even the problem of summing a set of random variables is NP-hard~\cite{mohring2001scheduling}.
+This is an example of an explicitly given random variable that we need to estimate deadline meeting probabilities for.
+
 We measure the quality of an approximation scheme by the distance between random variables and their approximations.
@@
 
-The size of a random variable is measured here by the size of its support, the set of possible outcomes, $m=|\support(X)|=|\{x\colon Pr(X=x) \neq 0\}|$.
+The size of a random variable is measured here by the size of its support, the set of possible outcomes, $|X|=|\support(X)|=|\{x\colon Pr(X=x) \neq 0\}|$.
 When probability mass functions are maintained as explicit tables, as done in many implementations of statistical software, the size of the support of the variable is proportional to the amount of memory needed to store it and to the complexity of the computations that manipulate it.
@@
 In the technical level, the problem we study in this paper is similar to the problem of approximating a set of 2-D points by a step function.
-The study of this problem was motivated by query optimisation and histogram constructions in database management systems~\cite{applf12,applf13,applf14,applf17,applf18,Fournier2011}.
+The study of this problem was motivated by query optimisation and histogram constructions in database management systems~\cite{applf12,applf13,applf14,applf17,applf18,Fournier2011} and computational geometry~\cite{diaz2001fitting,fournier2008fitting}.
 There are, however, two technically significant differences between the problem studied in the context of databases and the problem we analyse in this paper.
@@
 \section{An algorithm for optimal approximation}\label{sec:algEfficient}
+In the scope of this section, let $X$ be a given random variable with a finite support of size $n$, and let  $0<m\leq n$ be a given complexity bound.
+The section evolves by presenting two algorithms for finding an optimal $m$-approximation of $X$.
+The first algorithm is $binsearchApprox(X,m)$ (Algorithm~\ref{alg:naive}) which runs in time of $O(n^2log(n))$ and the second one $linApprox(X,m)$ (Algorithm~\ref{alg:linear}) which runs in time of $O(nlog(n))$.
+We present both $binsearchApprox(X,m)$ and $linApprox(X,m)$ since Algorithm~\ref{alg:linear} is based on Algorithm~\ref{alg:naive} but carry major run-time improvement.
+
+We begin our dissection by presenting a useful fact that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:
+
+\begin{lemma}\label{lem:supContained}
+	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
+\end{lemma}
+
+\begin{proof}
+	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
+	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.
+Since we only "shifted" the probability mass of $X''$ to the support of $X$, we have that $f_{X'}$ is a probability mass function and therefore $X'$ is well defined.
+	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
+	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
+\end{proof}
+
+Both of the algorithms presented in this section are using the dual problem in order to find the optimal $m$-approximation of $X$.
+The dual problem is: given a random variable $X$ with $|\support(X)| = n$, and some $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $|\support(X')|\leq m$ where $0< m \leq n$ and $d_K(X,X')$ is minimal.
+
+We do not assume anything about the representation of the random variable $X$ given as an input to the $dual(X,\varepsilon)$ algorithm.
+However, we transform the representation of every given $X$, to the form of sorted CDF as described in line 1 in the algorithm, which takes $O(nlog(n))$ run-time and has to done only once.
+The $dual(X,\varepsilon)$ gets as input a random variable $X$ and some $\varepsilon$, the random variable $X$ is represented as in line 1, $X_{CDF} =\{(x_i, c_i)\}_{i=1}^n$ such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.
+In lines 3-4 we perform a single pass over $X_{CDF}$ starting from index 1 to find the last index where the cumulative distribution function of $X$ is less than $\varepsilon$, this index is now $f$.
+In lines 5-6 in the algorithm we start from the last index of $X_{CDF}$ which is $n$, and in decreasing order seek for the last index where the cumulative distribution function of $X$ is less than $1-\varepsilon$, this index is now $l$.
+The last part of the algorithm is a pass on all elements in $X_{CDF}$ between the indices $f$ and $l$ in order to construct the $m$-approximation random variable of $X$, $X'$.
+In lines 9-10 we check if the difference between the first element in the current set of indices (which we call $b$) and the last element in the current set of indices (which we call $e+1$) is less that $2\varepsilon$.
+If yes, we add the pair $\{(x_{b}, (c_b+c_e)/2 - s) \}$ to the set $S$.
+Otherwise, we add one to the counter of $e$.
+Note, the reason we need $s$ is to return the random variable $X'$ in a PDF representation since our main motivation is sum of random variables, this part takes $O(n)$ run-time.
 
@@
 \begin{proof}
-	This algorithm describes one pass over the random variable $X$.
+	This algorithm describes a single pass over the random variable $X$.
 Lines 3-4 and lines 5-6 are easy to follow, each takes $O(n)$ in the worst case.
@@
 
+The first technique we present is the $binsearchApprox(X,m)$ algorithm which is based on the work done by D{\'i}az-B{\'a}nez and Mesa~\cite{diaz2001fitting}.
+There are couple of significant changes between our $binsearchApprox(X,m)$ algorithm and the algorithm suggested by D{\'i}az-B{\'a}nez and Mesa~\cite{diaz2001fitting} addressing the differences presented in the Related Work section~\ref{sec:relwork}.
+The algorithm $binsearchApprox(X,m)$ gets as input a random variable $X$ and some number $m$.
+Again, we do not mind the original representation of $X$ since we can transform it to a sorted CDF representation in $O(nlog(n))$ run-time as in line 1 which we call $X_{CDF}$.
+In lines 3-8 we compute all possible errors, in other words, all possible $d_{K}(X,X')$ such that $X'$ is an approximation of $X$ and $\support(X') \subseteq \support(X)$.
+The error is just the difference between the CDF values of every two elements in $X_{CDF}$.
+After computing the set $E$, we sort it (line 9) in order to perform a binary search in the last part of the algorithm.
+In lines 10-19 we perform a binary search over the set $E$, in every step of the binary search we run the $X' = dual(X,\varepsilon)$ algorithm.
+If the size of $|\support(X')|>m$ then we know that the error $\varepsilon$ is too small and need to extend the search in the right side of $E$, if the size of $|\support(X')|<m$ then we know that the error $\varepsilon$ is too big and need to extend the search in the left side of $E$, otherwise we found the correct $m$.
+We run the search twice to handle the extreme case where $m \notin \{\forall \varepsilon\in E: |dual(X,\varepsilon)|\}$ and return the smallest $m'$ closest to $m$.
+
 \begin{algorithm}
 	\DontPrintSemicolon
-	Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $Pr(X \leq x_i)=c_i$ and $\supp(X)=\{x_1 < \cdots < x_n\}$.\;
+	Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i=Pr(X \leq x_i)$ and $\supp(X)=\{x_1 < \cdots < x_n\}$.\;
     $E \gets \emptyset$\; 
@@
 
-	\caption{$approx(X,m)$}   
+	\caption{$binsearchApprox(X,m)$}   
 	\label{alg:naive}
@@
 \begin{theorem}\label{the:complexityDual}
-	The $approx(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|\support(X)|$.
+	The $binsearchApprox(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|\support(X)|$.
 \end{theorem}
@@
 We run this part twice then we get $O(2n log(n))$.
-All together, the run-time complexity is $O(n^2+n^2log(n)+2n log(n)) = O(n^2log(n))$ and the memory complexity is for set $E$ which is $n^2$.
+All together, the run-time complexity is $O(n^2+n^2log(n)+2n log(n)) = O(n^2log(n))$ and the memory complexity is for storing the set $E$ which is $O(n^2)$.
 \end{proof}
 
+As a step towards $linApprox(X,m)$ algorithm, we present the algorithm $saddlebackApprox(X,m)$ that takes $O(n^2)$ run-time, this technique is very similar to $linApprox(X,m)$ algorithm.
+The algorithm $saddlebackApprox(X,m)$ gets as input a random variable $X$ and some number $m$.
+Again, we represent $X$ as a sorted CDF in $O(nlog(n))$ run-time as in line 1 and call it $X_{CDF}$.
+In line 4 We describe implicitly the sorted matrix $E$, and in lines 3-7 we perform a search over this matrix, in every step of the search we run the $X' = dual(X,\varepsilon)$ algorithm.
+If the size of $|\support(X')|>m$ then we know that the error $e$ is too small and need to extend the search in the lower side of the matrix, if the size of $|\support(X')|<m$ then we know that the error $e$ is too big and need to extend the search in the right side of the matrix and store this $e$ in $S$.
+We store in set $S$ all possible candidates for the correct $e$ and in line 8 we get the maximal $m$ with the minimal $e$ value.
+
+\begin{algorithm}
+	\DontPrintSemicolon
+	Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i=Pr(X \leq x_i)$ and $\supp(X)=\{x_1 < \cdots < x_n\}$.\;
+    $i \gets 1$, $j \gets \lceil n/2 \rceil$, $S \gets \emptyset$\;
+
+	\While{$i < \lfloor n/2 \rfloor + 1 \wedge j \geq 2$}
+	{
+% 		$ e \gets \begin{cases}
+% 			c_j   & \text{if } i=\lfloor n/2 \rfloor+1; \\
+% 			1-c_i & \text{if } j=\lceil n/2 \rceil; \\
+% 			(c_{n+1-j} {-} c_i)/2  & \text{otherwise}
+% 		\end{cases}$\;
+
+		$X' \gets dual(X,e_{i,j})$, $m' \gets |\supp(X')|$\;
+
+		\lIf {$m'  > m$}
+		{
+			$j \gets j - 1$
+		}
+		\lIf {$m' \leq m$} {
+			$i \gets i + 1$, $S \gets S \cup (m',e)$			
+		}
+	}
+	$e \gets \min\{e\colon (m',e) \in \underset{(m',e)\in S}{\operatorname{arg\,max}}\, m'\}$\;
+	\Return{$dual(X,e)$}
+
+	\caption{$saddlebackApprox(X,m)$}   
+	\label{alg:saddleback}
+\end{algorithm}
+
+\begin{algorithm}
+		\DontPrintSemicolon
+		Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i=Pr(X \leq x_i)$ and $\supp(X)=\{x_1 < \cdots < x_n\}$.\;
+
+		$S \gets  \{ ((1, 1)),(\lceil n/2 \rceil+1,\lceil n/2 \rceil)) \}$, $S' \gets \emptyset$\;
+
+		\While{$S \neq S'$}
+		{
+			$S' \gets S$\;
+
+			$S \gets \displaystyle \bigcup_{s \in S} split(s)$\;
+
+			$e^- {\gets} median(\{ e_{i_1,j_1} \colon ((i_1,j_1),(i_2,j_2)) \in S \}) $\;
+
+			$X' \gets dual(X,e^-)$, $m' \gets |\supp(X')|$\;
+
+			\If {$m' \leq m$} {
+				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_1,j_1} {>} e^- \}$ \;
+			}
+
+			\Else %\If {$m'  > m$}
+			{
+				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_2,j_2} {\leq} e^- \}$ \;
+			}
+
+			$e^+ {\gets} median(\{ e_{i_2,j_2} \colon ((i_1,j_1),(i_2,j_2)) \in S \}) $\;
+			$X' \gets dual(X,e^+)$, $m' \gets |\supp(X')|$\;
+
+			\If {$m' \leq m$} {
+				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_1,j_1} {>} e^+ \}$ \;
+			}
+			\Else %{$m'  > m$}
+			{
+				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_2,j_2} {\leq} e^+ \}$ \;
+			}
+
+		}
+
+		$S'' \gets \{(|dual(X,e_{i,j})|,e_{i,j}) \colon ((i,j),(i,j)) \in S\}$\;
+
+		$e \gets \min\{e\colon (m',e) \in \underset{(m',e)\in S''}{\operatorname{arg\,max}}\, m'\}$\;
+		\Return{$dual(X,e)$}
+
+		\caption{$linApprox(X,m)$}   
+		\label{alg:linear}
+	\end{algorithm}
+
+	\begin{procedure}
+		\DontPrintSemicolon
+		$j^- \gets \lfloor (j_1+j_2)/2 \rfloor$,
+		$j^+ \gets \lceil (j_1+j_2)/2 \rceil$\;
+		$i^- \gets \lfloor (i_1+i_2)/2 \rfloor$,
+		$i^+ \gets \lceil (i_1+i_2)/2 \rceil$\;
+
+		\Return{$
+			\{ ((i_1, j_1), (i^-, j^-)),
+			((i_1, j^+), (i^-, j_2)),
+			((i^+, j_1), (i_2, j^-)),
+			((i^+, j^+), (i_2, j_2))    \}$}
+
+		\caption{{$split(((i_1,j_1),(i_2,j_2)))$}()}
+		\label{proc:split}
+	\end{procedure}
+
+	Let 
+	$$e_{i,j} = \begin{cases}
+	c_j   & \text{if } i=\lfloor n/2 \rfloor+1; \\
+	1-c_i & \text{if } j=\lceil n/2 \rceil; \\
+	(c_{n+1-j} {-} c_i)/2  & \text{otherwise}
+	\end{cases}$$
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{An algorithm for optimal approximation}\label{sec:alg}
-In the scope of this section, let $X$ be a given random variable with a finite support of size $n$, and let  $0<m\leq n$ be a given complexity bound.
+% \section{An algorithm for optimal approximation}\label{sec:alg}
+% In the scope of this section, let $X$ be a given random variable with a finite support of size $n$, and let  $0<m\leq n$ be a given complexity bound.
 The section evolves by developing notations and by collecting facts towards an algorithm for finding an optimal $m$-approximation of $X$.
 
-The first useful fact is that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:
-
-\begin{lemma}\label{lem:supContained}
-	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
-\end{lemma}
-
-\begin{proof}
-	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
-	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.
+% The first useful fact is that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:
+
+% \begin{lemma}\label{lem:supContained}
+% 	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
+% \end{lemma}
+
+% \begin{proof}
+% 	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
+% 	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.
 Since we only "shifted" the probability mass of $X''$ to the support of $X$, we have that $f_{X'}$ is a probability mass function and therefore $X'$ is well defined.
-	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
-	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
-\end{proof}
-
-%Next, note that every random variable $X''$ with support of size at most $m$ that is contained in $\support(X)$ can be described by first setting the (at most $m$) elements of the support of $X''$; then for every such option, determine $X''$ by setting probability values for the elements in the chosen support of $X'$, and setting $0$ for rest of the elements.
-
-For a set $S\subseteq \support(X)$, let $\mathbb{X}_S$ denote the set of random variables whose supports are contained in $S$.
+% 	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
+% 	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
+% \end{proof}
+
+% %Next, note that every random variable $X''$ with support of size at most $m$ that is contained in $\support(X)$ can be described by first setting the (at most $m$) elements of the support of $X''$; then for every such option, determine $X''$ by setting probability values for the elements in the chosen support of $X'$, and setting $0$ for rest of the elements.
+
+% For a set $S\subseteq \support(X)$, let $\mathbb{X}_S$ denote the set of random variables whose supports are contained in $S$.
 In Step 1 below, we identify a random variable in $\mathbb{X}_S$  that minimizes the Kolmogorov distance from $X$.
@@
 
-\subsection*{Step 1: Finding an $X'$ in $\mathbb{X}_S$ that minimizes $d_K(X,X')$}
-
-We first fix a set $S\subseteq \support(X)$ and among all the random variables in $\mathbb{X}_S$ find one with a minimal distance from $X$.
+% \subsection*{Step 1: Finding an $X'$ in $\mathbb{X}_S$ that minimizes $d_K(X,X')$}
+
+% We first fix a set $S\subseteq \support(X)$ and among all the random variables in $\mathbb{X}_S$ find one with a minimal distance from $X$.
 Denote the elements of $S$ in increasing order by $S=\{x_1<\dots<x_m\}$ and let $x_0=-\infty$ and $x_{m+1}=\infty$.
@@
 
-\begin{definition}\label{def:weight} For $0\leq i \leq m$ let
-	\[
-	w(x_i,x_{i+1})=
-	\begin{cases}
-	P(x_i < X < x_{i+1}) & \text{if $i=0$ or $i = m$;} \\
-	P(x_i < X < x_{i+1})/2 & \text{otherwise.} \\	
-	\end{cases}
-	\]
-\end{definition}
-For each $1 <  i \leq m$ let $\hat x_i$ be the maximal element of $\support(X)$ that is smaller than $x_i$. 
-Note that, for $1\leq i \leq m$, $P(x_i < X < x_{i+1}) = F_X(\hat x_{i+1}) - F_X(x_i)$, a fact that we will use throughout this section.
-
-\begin{definition}\label{def:error}
-Let $\varepsilon(X,S) = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$.
-\end{definition}
-
-We first show that $\varepsilon(X,S)$ is a lower bound for the distance between random variable in $\mathbb{X}_S$ and $X$.
+% \begin{definition}\label{def:weight} For $0\leq i \leq m$ let
+% 	\[
+% 	w(x_i,x_{i+1})=
+% 	\begin{cases}
+% 	P(x_i < X < x_{i+1}) & \text{if $i=0$ or $i = m$;} \\
+% 	P(x_i < X < x_{i+1})/2 & \text{otherwise.} \\	
+% 	\end{cases}
+% 	\]
+% \end{definition}
+% For each $1 <  i \leq m$ let $\hat x_i$ be the maximal element of $\support(X)$ that is smaller than $x_i$. 
+% Note that, for $1\leq i \leq m$, $P(x_i < X < x_{i+1}) = F_X(\hat x_{i+1}) - F_X(x_i)$, a fact that we will use throughout this section.
+
+% \begin{definition}\label{def:error}
+% Let $\varepsilon(X,S) = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$.
+% \end{definition}
+
+% We first show that $\varepsilon(X,S)$ is a lower bound for the distance between random variable in $\mathbb{X}_S$ and $X$.
 Then, we present a random variable $X'\in \mathbb{X}_S$ such that $d_K(X,X')=\varepsilon(X,S)$.
@@
 
-%The intuition behind choosing these specific weights and $\varepsilon(X,S)$ being a lower bound is as follows.
+% %The intuition behind choosing these specific weights and $\varepsilon(X,S)$ being a lower bound is as follows.
 Since for every $X'\in\mathbb{X}_S$ the probability mass of $X'$ for the elements not in $S$ are set to $0$, we have that $F_{X'}(\hat x_{i+1})=F_{X'}(x_i)$.
@@
 
-%Formally we have the following.
-
-\begin{proposition}\label{prop:minimal}
-	If $X'\in\mathbb{X}_S$ then $d_K(X,X') \geq \varepsilon(X,S)$.
-\end{proposition}
-
-\begin{proof}
-
-	By definition, for each $0\leq i\leq m$, $d_K(X,X') \geq \max \{|F_X(\hat x_{i+1}) - F_{X'}(\hat x_{i+1})|,|F_X(x_i) - F_{X'}(x_i)| \}$.
+% %Formally we have the following.
+
+% \begin{proposition}\label{prop:minimal}
+% 	If $X'\in\mathbb{X}_S$ then $d_K(X,X') \geq \varepsilon(X,S)$.
+% \end{proposition}
+
+% \begin{proof}
+
+% 	By definition, for each $0\leq i\leq m$, $d_K(X,X') \geq \max \{|F_X(\hat x_{i+1}) - F_{X'}(\hat x_{i+1})|,|F_X(x_i) - F_{X'}(x_i)| \}$.
 Note that $F_{X'}(\hat x_{i+1})=F_{X'}(x_i)$ since the probability of  elements not in $S$ is  $0$.
 
-	If $i=0$, that is $x_i=-\infty$, we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ and therefore $d_K(X,X') \geq |F_X(\hat x_{i+1})| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1})= w(x_i,x_{i+1})$.
-
-	If $i =m$, that is $x_{i+1}=\infty$, we have that $F_X(\hat x_{i+1})=F_{X'}(\hat x_{i+1})=F_{X'}(x_i)=1$. 
-	and therefore $d_K(X,X') \geq |1-F_X(\hat x_i)| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1}) = w(x_i,x_{i+1})$.
-
-	%  we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ 
-	% 
-	% 
-	% 
-	% We break the proof for the closed intervals where each support variable $x_i$ is a proper number, and for the open intervals where a support variable is either $-\infty$ or $\infty$.
-
-	Otherwise for every $1\leq i< m$,  we use the fact that $max\{|a|,|b|\} \geq |a-b|/2$ for every $a,b\in\mathbb{R}$, to deduce that $d_K(X,X') \geq 1/2| F_X(\hat x_{i+1}) - F_X(x_i) + F_{X'}(x_i) -F_{X'}(\hat x_{i+1})|$.
+% 	If $i=0$, that is $x_i=-\infty$, we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ and therefore $d_K(X,X') \geq |F_X(\hat x_{i+1})| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1})= w(x_i,x_{i+1})$.
+
+% 	If $i =m$, that is $x_{i+1}=\infty$, we have that $F_X(\hat x_{i+1})=F_{X'}(\hat x_{i+1})=F_{X'}(x_i)=1$. 
+% 	and therefore $d_K(X,X') \geq |1-F_X(\hat x_i)| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1}) = w(x_i,x_{i+1})$.
+
+% 	%  we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ 
+% 	% 
+% 	% 
+% 	% 
+% 	% We break the proof for the closed intervals where each support variable $x_i$ is a proper number, and for the open intervals where a support variable is either $-\infty$ or $\infty$.
+
+% 	Otherwise for every $1\leq i< m$,  we use the fact that $max\{|a|,|b|\} \geq |a-b|/2$ for every $a,b\in\mathbb{R}$, to deduce that $d_K(X,X') \geq 1/2| F_X(\hat x_{i+1}) - F_X(x_i) + F_{X'}(x_i) -F_{X'}(\hat x_{i+1})|$.
 So $d_K(X,X') \geq 1/2| F_X(\hat x_{i+1}) - F_X(x_i) | =P(x_1 < X < x_2)/2 = w(x_i,x_{i+1})$.
 
-Since $d_K(X,X') {\geq}  w(x_i,x_{i+1})$ for any $0{\leq} i{\leq} m$, the proof follows by the definition of $\varepsilon(X,S)$.
-\end{proof}
-
-We next describe a random variable $X'\in\mathbb{X}_S$ in a distance of $\varepsilon(X,S)$ from $X$ by its probability mass function:
-
-\begin{definition}\label{def:construction}
-	Let $f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
-\end{definition}
-
-We first show that $X'$ is a properly defined random variable:
-
-\begin{lemma}
-	$f_{X'}$ is a probability mass function. 
-\end{lemma}
-
-\begin{proof}
-	By definition $f_{X'}(x_{i})\geq 0$ for every $i$. To see that $\sum_i f_{X'}(x_{i}) =1$, 
-	we have $\sum_i f_{X'}(x_{i}) = \sum_i (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) = 	
-	\sum _{x_i\in S} f_{X}(x_i)) + w(x_0,x_1)+ \sum_{0 < i < m} 2 w(x_i,x_{i+1}) + w(x_m,x_{m+1}) = 
-	\sum _{x_i\in S} P(X{=}x_i) + P(x_0 {<} X {<} x_1)+ \sum_{0 < i < m} P(x_i < X < x_{i+1}) +P(x_m < X < x_{m+1}) = 1$ since this is the entire support of $X$.	
-\end{proof}
-
-Note that, given $S$, $X'$ can be constructed in time linear in the size of the support of $X$.
-Its main property, of course, is that the distance between the cumulative distribution functions of $X$ and of $X'$ are bounded by $w(x_i,x_{i+1})$, as follows:
-\begin{lemma}\label{lem:balance}
-	Let $x\in\support(X)$ and $0\leq i\leq m$ be such that $x_i\leq x \leq x_{i+1}$ then 
-    \[
-    -w(x_i,x_{i+1})\leq F_X(x)-F_{X'}(x)\leq  w(x_i,x_{i+1}).
-    \]
-    \end{lemma}
-
-\begin{proof}	
-	By induction on $i$.	First see that $F_{X'}(x) = 0$  for every $x_0<x < x_1$ and therefore $F_X(x)-F_{X'}(x) = F_X(x)-0 \leq F_X(\hat x_1)= F_X(\hat x_1)- F_X(x_0) = w(x_0,x_1)$.
+% Since $d_K(X,X') {\geq}  w(x_i,x_{i+1})$ for any $0{\leq} i{\leq} m$, the proof follows by the definition of $\varepsilon(X,S)$.
+% \end{proof}
+
+% We next describe a random variable $X'\in\mathbb{X}_S$ in a distance of $\varepsilon(X,S)$ from $X$ by its probability mass function:
+
+% \begin{definition}\label{def:construction}
+% 	Let $f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
+% \end{definition}
+
+% We first show that $X'$ is a properly defined random variable:
+
+% \begin{lemma}
+% 	$f_{X'}$ is a probability mass function. 
+% \end{lemma}
+
+% \begin{proof}
+% 	By definition $f_{X'}(x_{i})\geq 0$ for every $i$. To see that $\sum_i f_{X'}(x_{i}) =1$, 
+% 	we have $\sum_i f_{X'}(x_{i}) = \sum_i (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) = 	
+% 	\sum _{x_i\in S} f_{X}(x_i)) + w(x_0,x_1)+ \sum_{0 < i < m} 2 w(x_i,x_{i+1}) + w(x_m,x_{m+1}) = 
+% 	\sum _{x_i\in S} P(X{=}x_i) + P(x_0 {<} X {<} x_1)+ \sum_{0 < i < m} P(x_i < X < x_{i+1}) +P(x_m < X < x_{m+1}) = 1$ since this is the entire support of $X$.	
+% \end{proof}
+
+% Note that, given $S$, $X'$ can be constructed in time linear in the size of the support of $X$.
+% Its main property, of course, is that the distance between the cumulative distribution functions of $X$ and of $X'$ are bounded by $w(x_i,x_{i+1})$, as follows:
+% \begin{lemma}\label{lem:balance}
+% 	Let $x\in\support(X)$ and $0\leq i\leq m$ be such that $x_i\leq x \leq x_{i+1}$ then 
+%     \[
+%     -w(x_i,x_{i+1})\leq F_X(x)-F_{X'}(x)\leq  w(x_i,x_{i+1}).
+%     \]
+%     \end{lemma}
+
+% \begin{proof}	
+% 	By induction on $i$.	First see that $F_{X'}(x) = 0$  for every $x_0<x < x_1$ and therefore $F_X(x)-F_{X'}(x) = F_X(x)-0 \leq F_X(\hat x_1)= F_X(\hat x_1)- F_X(x_0) = w(x_0,x_1)$.
 For $ x = x_1$ we have $F_X(x_1)-F_{X'}(x_1)=  F_X(\hat x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1) =
-	w(x_0,x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)) = -w(x_1,x_2)$.
-
-	Next assume that $F_X(\hat x_i)-F_{X'}(\hat x_i) = w(x_{i-1},x_i)$.
-	Then $F_X(x_i)-F_{X'}(x_i) =  F_X(\hat x_i) +f_{X}(x_i) - (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) =  w(x_{i-1},x_i) +f_{X}(x_{i}) - (w(x_{i-1},x_i) + w(x_{i},x_{i+1}) + f_{X}(x_{i})) = -w(x_{i},x_{i+1})$.
-
-	As before we have that for all $x_i< x< x_{i+1}$, we have $F_X(x)-F_{X'}(x) = F_X(x)-F_{X'}(\hat x_{i+1}) \leq  F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1})$.
+% 	w(x_0,x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)) = -w(x_1,x_2)$.
+
+% 	Next assume that $F_X(\hat x_i)-F_{X'}(\hat x_i) = w(x_{i-1},x_i)$.
+% 	Then $F_X(x_i)-F_{X'}(x_i) =  F_X(\hat x_i) +f_{X}(x_i) - (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) =  w(x_{i-1},x_i) +f_{X}(x_{i}) - (w(x_{i-1},x_i) + w(x_{i},x_{i+1}) + f_{X}(x_{i})) = -w(x_{i},x_{i+1})$.
+
+% 	As before we have that for all $x_i< x< x_{i+1}$, we have $F_X(x)-F_{X'}(x) = F_X(x)-F_{X'}(\hat x_{i+1}) \leq  F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1})$.
 Then $F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1}) = (F_X(x_i)+ P(x_i < x <x_{i+1})) - F_{X'}(x_i) = -w(x_{i},x_{i+1}) + 2w(x_{i},x_{i+1}) = w(x_{i},x_{i+1}) $.
 
-	Finally, for $x_m\leq x \leq x_{m+1}$ we have that $F_{X'}(x_m)=1$ therefore $F_X(x_m)-F_{X'}(x_m) = (1- P(x_m<X < x_{m+1})) - 1 =  P(x_m<X < x_{m+1}) = w(x_m,x_{m+1})$, and for every $x_m<x<x_{m+1}$ we have $F_X(x) - F_{X'}(x) < (1- P(x_m<X < x_{m+1})) - 1 <  - P(x_m<X < x_{m+1}))  = -w(x_m,x_{m+1})$ as required.
-\end{proof}
-
-From Lemma \ref{lem:balance}, by the definition of $\varepsilon(X,S)$, we then have:
-\begin{corollary} \label{col:Xprime}
-	$d_K(X,X') = \varepsilon(X,S)$.
-\end{corollary}
-From Proposition~\ref{prop:minimal} we also have:
-\begin{corollary} \label{col:Xprimeopt}
-	$\varepsilon(X,S)$ is the Kolmogorov distance between $X$ and the variables closest to it in $\mathbb{X}_S$.
-\end{corollary}
-
-%\begin{proof}
-%	We first see by induction that for every $1\leq i \leq m$ that $F_X(\hat x_i)-F_{X'}(\hat x_i)=w(x_{i-1},x_i)$ and $F_X(x_i)-F_{X'}(x_i) = -w(x_i,x_{i+1})$. 
-%	
-%	For $i=1$ we have  $F_X(\hat x_1)-F_{X'}(\hat x_1)= F_X(\hat x_1)-0 =  F_X(\hat x_1)- F_X(x_0) = w(x_0,x_1)$.
-%	Then $F_X(x_i)-F_{X'}(x_i)=  F_X(\hat x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)| = 
-%	w(x_0,x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)) = -w(x_1,x_2)$.
-%	
-%	Assume that $F_X(x_i)-F_{X'}(x_i) = -w(x_i,x_{i+1})$. Then $F_X(\hat x_{i+1})-F_{X'}(\hat x_{i}) = (F_X(x_i)+ P(x_i<X<x_{i+1}))-F_{X'}(x_i) = -w(x_i,x_{i+1})+2w(x_i,x_{i+1})=w(x_i,x_{i+1})$.
-%	Therefore, we have $F_X(x_{i+1})-F_{X'}(x_{i+1}) = F_X(\hat x_{i+1}) +f_{X}(x_{i+1}) - (w(x_i,x_{i+1}) + w(x_{i+1},x_{i+2}) + f_{X}(x_{i+1})| = 
-%	w(x_i,x_{i+1}) +f_{X}(x_{i+1}) - (w(x_i,x_{i+1}) + w(x_{i+1},x_{i+2}) + f_{X}(x_{i+1})) = -w(x_{i+1},x_{i+2})$.
-%	
-%	
-%	[[DF: read again and see if special instructions are required for $i=0,m$, the last one]]
-%	
-%	
-%	Finally see that for every $x_i<x< x_{i+1}\in \support(X)$, $F_{X'}(j)= F_{X'}(x_i) = F_{X'}(\hat x_{i+1}) $ and therefore  $-w(x_i,x_{i+1}) = F_X(x_i)-F_{X'}(x_i) \leq F_X(j)-F_{X'}(j)\leq F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1}) = w(x_i,x_{i+1})$.
-Therefore $|F_X(j)-F_{X'}(j)|\leq w(x_i,x_{i+1})$.
-%	
-%	Therefore for every $j\in \support(X)$ we have that $|F_X(j)-F_{X'}(j)|\leq max_i(w(x_i,x_{i+1})=\varepsilon(X,S)$. as required.	
-%\end{proof}
-
-%\begin{itemize}
-%	\item The next lemma states a lower bound on the distance $d_K(X,X')$ when a range of elements is excluded from the support of $X'$.
-%\end{itemize}
-%
-%
-%\begin{lemma}\label{lem:geq}
-%	For $x_1, x_2 \in \support(X) \cup \{-\infty,\infty\}$ such that $x_1 < x_2$, if $P(x_1 < X' < x_2)=0$  then 
-%	$d_k(X,X') \geq P(x_1 < X < x_2)/2$.
-%\end{lemma}
-%\begin{proof}
-%	Let $\hat x=\max \{x \in \support(X) \cap\{ -\infty, \infty\}  \colon x < x_2 \}$.
-By definition, $d_k(X,X') \geq \max \{|F_X(x_1) - F_{X'}(x_1)|, |F_X(\hat x) - F_{X'}(\hat x)| \}$.
-From Observation~\ref{obs:ab}, $d_k(X,X') \geq 1/2|F_X(x_1) - F_X(\hat x) + F_{X'}(\hat x) - F_{X'}(x_1)|$.
-Since it is given that $F_{X'}(\hat x) - F_{X'}(x_1) = P(x_1 < X' < x_2)=0$, $d_k(X,X') \geq 1/2|F_X(x_1) - F_X(\hat x) | =  P(x_1 < X \leq \hat x)/2 = P(x_1 < X < x_2)/2$.
-%\end{proof}
-%
-%
-%\begin{itemize}
-%	\item The next lemma strengthen the lower bound.
-%\end{itemize}
-%
-%
-%\begin{lemma}\label{lem:geq2}
-%	For $x_1, x_2 \in \support(X) \cup \{-\infty,\infty\}$ such that $x_1=-\infty$ or  $x_2=\infty$, if $P(x_1 < X' < x_2)=0$  then 
-%	$d_k(X,X') \geq P(x_1 < X < x_2)$.
-%\end{lemma}
-%\begin{proof}
-%	Let $\hat x=\max \{x \in \support(X) \cap\{ -\infty, \infty\}  \colon x < x_2 \}$.
-By definition $d_k(X,X') \geq \max \{|F_X(x_1) - F_{X'}(x_1)|, |F_X(\hat x) - F_{X'}(\hat x)| \}$.
-If $x_1=-\infty$ then $d_k(X,X') \geq \{|F_X(\hat x) - F_{X'}(\hat x)| \}$ since $F_X(-\infty) = F_{X'}(-\infty) = 0$.
-Furthermore, $F_{X'}(\hat x) = P(x_1 < X' < x_2)=0$.
-Therefore $d_k(X,X') \geq F_X(\hat x) = P(x_1 < X \leq \hat x) = P(x_1 < X < x_2)$.
-%	If $x_2=\infty$ then $d_k(X,X') \geq \{|F_X(x_1) - F_{X'}(x_1)| \}$ since $F_X(\hat{x}) = F_{X'}(\hat{x}) = F_X(\infty) = F_{X'}(\infty) = 1$.
-Furthermore, $F_{X'}(x_1) = 1$ since it is given that $P(x_1 < X' < x_2)=0$.
-Therefore we get that $d_k(X,X') \geq |F_X(x_1)-1| = |1-F_X(\hat x)-| = P(x_1 < X \leq \hat x) = P(x_1 < X < x_2)$.
-%\end{proof}
-%
-%
-%\begin{definition}\label{def:weight} For $x_1,x_2 \in \support(X) \cup \{-\infty,\infty\}$ let
-%	\[
-%	w(x_1,x_2)=
-%	\begin{cases}
-%	P(x_1 < X < x_2) & \text{if $x_1=-\infty$ or $x_2 = \infty$;} \\
-%	P(x_1 < X < x_2)/2 & \text{otherwise.} \\	
-%	\end{cases}
-%	\]
-%\end{definition} 
-%
-%
-%\begin{definition}\label{def:error} For $S=\{x_1<\dots<x_m\} \subseteq \support(X)$, $x_0=-\infty$, and $x_{m+1}=\infty$, let
-%	\[
-%	\varepsilon(X,S) = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1}).
-%	\]
-%\end{definition} 
-%
-%\begin{itemize}
-%	\item From here on, until the end of the section, $S$ is fixed.
-%\end{itemize}
-
-%
-%\begin{proposition}
-%	There is no $X'$ such that $\support(X')=S$ and $d_k(X,X') < \varepsilon(X,S)$.
-%\end{proposition}
-%\begin{proof}
-%	Let $i$ be the index that maximizes $w(x_{i}, x_{i+1})$. If $0<i<n-1$ then $d_k(X,X') \geq w(x_{i}, x_{i+1})$ by Lemma~\ref{lem:geq}. If $i=0$ or $i=n+1$ the same follows from Lemma~\ref{lem:geq2}.
-%\end{proof}
-
-%
-%\begin{lemma}
-%	For $i>1$, if $F_{X'}(x_{i})-F_{X}(x_{i}) = w(x_{i}, x_{i+1})$ then $F_{X'}(x_{i+1})-F_{X}(x_{i+1}) = w(x_{i+1}, x_{i+2})$.
-%\end{lemma}
-%\begin{proof}
-%	\begin{align}
-%	&F_{X'}(x_{i+1})-F_{X}(x_{i+1}) = \\ \nonumber
-%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - P(X<x_{i+1}) + P(X'<x_{i+1})  \\ \nonumber
-%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - F_X(x_{i}) - P(x_{i}< X < x_{i+1}) + F_{X'}(x_{i}) \\ 
-%	\label{eq:weight}
-%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - F_X(x_{i}) - 2w(x_{i},x_{i+1}) + F_{X'}(x_{i})  \\ \label{eq:indHip}
-%	& = f_{X'}(x_{i+1}) - f_{X}(x_{i+1}) - 2w(x_{i},x_{i+1}) +w(x_{i}, x_{i+1})  \\ \label{eq:construction}
-%	& = w(x_{i},x_{i+1}) +w(x_{i+1},x_{i+2}) - 2w(x_{i},x_{i+1}) +w(x_{i}, x_{i+1}) \\ \nonumber
-%	& = w(x_{i+1},x_{i+2}) \nonumber
-%	\end{align}
-%	
-%	By Definition~\ref{def:weight} the probability $P(x_{i-1}< X < x_i) = 2w(x_{i-1},x_{i})$ as in Equation~\eqref{eq:weight}.
-Equation~\eqref{eq:indHip} is deduced by the induction hypothesis and Equation~\eqref{eq:construction} where
-%	$f_{X'}(x_i) - f_{X}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1})$ is true by construction, see Definition\ref{def:construction}.
-%\end{proof}
-
-%\begin{lemma}
-%	For $i>1$, if $F_{X'}(x_{i-1})-F_{X}(x_{i-1}) = w(x_{i-1}, x_{i})$ then $F_{X'}(x_{i})-F_{X}(x_i) = w(x_i, x_{i+1})$.
-%\end{lemma}
-%\begin{proof}
-%	% TODO switch tdirections to fit the statement of the lemma
-%	% TODO \eqref,  aligment
-%	\begin{align}
-%	&F_X(x_i)-F_{X'}(x_i) = \\
-%	&f_{X}(x_i) - f_{X'}(x_i) + P(X<x_i) - P(X'<x_i)  = \\ \nonumber
-%	&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + P(x_{i-1}< X < x_i)-F_{X'}(x_{i-1}) = \\
-%	&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + 2w(x_{i-1},x_{i})-F_{X'}(x_{i-1}) =^* \\
-%	&f_{X}(x_i) - f_{X'}(x_i) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) = \\
-%	& -w(x_{i-1},x_i) - w(x_i,x_{i+1}) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) =\\ 
-%	&- w(x_i,x_{i+1})
-%	\end{align}
-%	$*$ by induction hypothesis.
-%	The probability $P(x_{i-1}< X < x_i) = 2w(x_{i-1},x_{i})$ by Definition~\ref{def:weight}, and
-%	$f_{X'}(x_i) - f_{X}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1})$ by construction.
-%\end{proof}
-%
-%\begin{lemma}
-%	Base case: $i = 1, F_{X'}(x_{1})-F_{X}(x_{1}) = w(x_{1}, x_{2})$.
-%\end{lemma}
-%\begin{proof}
-%	\begin{align*}
-%	F_{X'}(x_{1})-F_{X}(x_{1}) &= \\
-%	& = f_{X'}(x_{1}) - f_{X}(x_{1}) - w(x_0, x_1)  \\
-%	& = w(x_{0},x_1) + w(x_1,x_{2}) - w(x_0, x_1)  \\
-%	& = w(x_1,x_{2})
-%	\end{align*}
-%\end{proof}
-%
-%
-%
-
-%\begin{proof}
-%	Define $X'$ to by $f_{X'}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
-%	We need to show that $F_X(x_i)-F_{X'}(x_i) = -w(x_i, x_{i+1})$. Assume this is true for every $j<i$, the induction hypothesis hereby: $F_X(x_{i-1})-F_{X'}(x_{i-1}) = -w(x_{i-1}, x_{i})$.
-%	\begin{align*}
-%		&F_X(x_i)-F_{X'}(x_i) = \\
-%		&f_{X}(x_i) - f_{X'}(x_i) + P(X<x_i) - P(X'<x_i)  = \\
-%		&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + P(x_{i-1}< X < x_i)-F_{X'}(x_{i-1}) = \\
-%		&f_{X}(x_i) - f_{X'}(x_i) + F_X(x_{i-1}) + 2w(x_{i-1},x_{i})-F_{X'}(x_{i-1}) =^* \\
-%		&f_{X}(x_i) - f_{X'}(x_i) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) = \\
-%		& -w(x_{i-1},x_i) - w(x_i,x_{i+1}) + 2w(x_{i-1},x_{i}) -w(x_{i-1}, x_{i}) =\\ 
-%		&- w(x_i,x_{i+1})
-%	\end{align*}
-%	$*$ by induction hypothesis.
-%	The probability $P(x_{i-1}< X < x_i) = 2w(x_{i-1},x_{i})$ by definition~\ref{def:weight}, and
-%	$f_{X'}(x_i) - f_{X}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1})$ by construction.
-%	
-%\end{proof}
-
-%\begin{proposition}
-%	For any random variable $X$ and an ordered set $S=\{x_1<\dots<x_m\} \subset \support(X)$ there is no random variable $X'$ such that $\support(X')=S$ and $d_k(X,X') < \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$ where, to simplify notations, we assume that $x_0=-\infty$ and $x_{m+1}=\infty$.
-%\end{proposition}
-%
-%\begin{proof}
-%	Let $i$ be the index that maximizes $w(x_{i}, x_{i+1})$. If $0<i<n-1$ then $d_k(X,X') \geq w(x_{i}, x_{i+1})$ by Lemma~\ref{lem:geq}. If $i=0$ or $i=n+1$ the same follows from Lemma~\ref{lem:geq2}.
-%\end{proof}
-%
-%\begin{itemize}
-%	\item The next lemma shows that there is a n not better approximation. 
-%\end{itemize}
-%
-%
-%
-%\begin{proposition}
-%	For any random variable $X$ and an ordered set $S=\{x_1<\dots<x_m\} \subset \support(X)$ there is a random variable $X'$ such that $\support(X')=S$ and $d_k(X,X') = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$ where, to simplify notations, we assume that $x_0=-\infty$ and $x_{m+1}=\infty$.
-%\end{proposition}
-%\begin{proof}
-%Define $X'$ to by $f_{X'}(x_i) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
-%\end{proof}
-
-%%%%%%%%%%%%%%%%%%%% New sec 3.2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Step 2: Finding a set $S$ that minimizes $\varepsilon(X,S)$}
-
-We proceed to finding a set $S$ of size $m$ that minimizes $\varepsilon(X,S)$.
+% 	Finally, for $x_m\leq x \leq x_{m+1}$ we have that $F_{X'}(x_m)=1$ therefore $F_X(x_m)-F_{X'}(x_m) = (1- P(x_m<X < x_{m+1})) - 1 =  P(x_m<X < x_{m+1}) = w(x_m,x_{m+1})$, and for every $x_m<x<x_{m+1}$ we have $F_X(x) - F_{X'}(x) < (1- P(x_m<X < x_{m+1})) - 1 <  - P(x_m<X < x_{m+1}))  = -w(x_m,x_{m+1})$ as required.
+% \end{proof}
+
+% From Lemma \ref{lem:balance}, by the definition of $\varepsilon(X,S)$, we then have:
+% \begin{corollary} \label{col:Xprime}
+% 	$d_K(X,X') = \varepsilon(X,S)$.
+% \end{corollary}
+% From Proposition~\ref{prop:minimal} we also have:
+% \begin{corollary} \label{col:Xprimeopt}
+% 	$\varepsilon(X,S)$ is the Kolmogorov distance between $X$ and the variables closest to it in $\mathbb{X}_S$.
+% \end{corollary}
+
+% \subsection*{Step 2: Finding a set $S$ that minimizes $\varepsilon(X,S)$}
+
+% We proceed to finding a set $S$ of size $m$ that minimizes $\varepsilon(X,S)$.
 To obtain that we use a graph search approach inspired by~\cite{chakravarty1982partitioning}.
@@
 
-More specifically, the vertices of the graph are $V=\support(X) \cup \{-\infty,\infty\}$ and the edges, $E$, are all the pairs $(x_1,x_2) \in V^2$ such that $x_1 < x_2$. The weight 
-of each edge is as specified in Definition~\ref{def:weight}.
+% More specifically, the vertices of the graph are $V=\support(X) \cup \{-\infty,\infty\}$ and the edges, $E$, are all the pairs $(x_1,x_2) \in V^2$ such that $x_1 < x_2$. The weight 
+% of each edge is as specified in Definition~\ref{def:weight}.
 Note that there is a one-to-one correspondence between a set $S \subseteq \support(X)$ of size $m$, and an $-\infty$-to-$\infty$ path $\vec{p}_S$ in $G$, obtained by removing the $-\infty$ and $\infty$ from the path in one direction and by adding these elements and sorting in the other direction.
-With this correspondence, the maximal weight of an edge on $\vec{p}_S$ is $\varepsilon(X,S)$.
+% With this correspondence, the maximal weight of an edge on $\vec{p}_S$ is $\varepsilon(X,S)$.
 We denote this maximal weight of an edge  by $w(\vec{p}_S)$, and denote the set of all acyclic $-\infty$-to-$\infty$ paths in $G$ with at most $m$ edges by $paths_m(G, -\infty, \infty)$.
 Thus, the problem of finding the set $S$ with the minimal  $\varepsilon(X,S)$ is now reduced to the problem of finding a path $\vec{p}\in paths_m(G, -\infty, \infty)$ such that $w(\vec{p})$ is minimal among all $\{w(\vec{p'}) \colon \vec{p'}\in paths_m(G, -\infty, \infty)\}$.
-This problem can be solved by a variant of the Bellman-Ford algorithm and by the algorithm described in~\cite{guerin2002computing} that performs better in some cases.
-
-%\begin{corollary}\label{cor:Bellman}
-%$BellmanFord(G,m)$ returns a path $\vec{p}\in paths_m(G, s, t)$ such that $w(\vec{p})$ is minimal among all $\{w(\vec{p'}) | \vec{p'}\in paths_m(G, s, t)\}$.
-%\end{corollary}
-
-\subsection*{Step 3: Constructing the overall algorithm}
-
-We combine Step 1 and Step 2 in the following algorithm called $\KlmApprox$ (Algorithm~\ref{alg:optapprox}) that follows naturally from the two steps.
+% This problem can be solved by a variant of the Bellman-Ford algorithm and by the algorithm described in~\cite{guerin2002computing} that performs better in some cases.
+
+% %\begin{corollary}\label{cor:Bellman}
+% %$BellmanFord(G,m)$ returns a path $\vec{p}\in paths_m(G, s, t)$ such that $w(\vec{p})$ is minimal among all $\{w(\vec{p'}) | \vec{p'}\in paths_m(G, s, t)\}$.
+% %\end{corollary}
+
+% \subsection*{Step 3: Constructing the overall algorithm}
+
+% We combine Step 1 and Step 2 in the following algorithm called $\KlmApprox$ (Algorithm~\ref{alg:optapprox}) that follows naturally from the two steps.
 Given $X$ and $\support(X)$ we add $x_0=\infty,x_{n+1}=-\infty$ and construct the graph (line 2) as described  in Step 2 above.
@@
 
-\begin{algorithm}\label{alg:optapprox}
-	%\setstretch{1.5}
-	\DontPrintSemicolon
-	Construct a weighted graph $G=(V,E)$ where $V=\support(X) \cup \{-\infty,\infty\}$, $E=\{(x_1,x_2) \in V^2\colon x_1 < x_2 \}$, and the weights are as in Definition~\ref{def:weight}.\; \vspace{0.2cm}
-
-	Find a path $\vec{p}=(x_0,\dots,x_{m+1})\in paths_m(G, -\infty, \infty)\}$ such that $w(\vec{p}) = \min \{w(\vec{p}) \colon \vec{p}\in paths_m(G, -\infty, \infty)\}$.   \; 	\vspace{0.2cm}
-
-	Return a random variable whose probability mass function is 
-		$f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for all $i=1,\dots,m$ and zero otherwise. \;
-
-	\caption{$\KlmApprox (X, m)$}  
-	\label{alg:sequence}
-\end{algorithm}
-
-%\begin{algorithm}\label{alg:optapprox}
+% \begin{algorithm}\label{alg:optapprox}
+% 	%\setstretch{1.5}
 % 	\DontPrintSemicolon
-%	\SetKwFunction{Convolv}{Conv}
-%	\SetKwFunction{getPartition}{getPartition}
-%	\SetKwFunction{bellmanFordMinMaxM}{bellmanFordMinMaxM}
-%	$\support(X)\cup \{x_0,x_{n+1}\}$\;
-%	Construct $G=(V,E,s,t,w)$ according to Step 2 \;
-%	$\vec{p}=(v_0,\dots,v_{m+1}) = Belmman-Ford(G,m)$  \;
-%	\For{$0<i<m+1$ }{
-%		$f_{X'}(x_{i}) = w(v_{i-1},v_i) + w(v_i,v_{i+1}) + f_{X}(x_i)$
-%	}	
-%	\Return $X'$\;
-%	
+% 	Construct a weighted graph $G=(V,E)$ where $V=\support(X) \cup \{-\infty,\infty\}$, $E=\{(x_1,x_2) \in V^2\colon x_1 < x_2 \}$, and the weights are as in Definition~\ref{def:weight}.\; \vspace{0.2cm}
+
+% 	Find a path $\vec{p}=(x_0,\dots,x_{m+1})\in paths_m(G, -\infty, \infty)\}$ such that $w(\vec{p}) = \min \{w(\vec{p}) \colon \vec{p}\in paths_m(G, -\infty, \infty)\}$.   \; 	\vspace{0.2cm}
+
+% 	Return a random variable whose probability mass function is 
+% 		$f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for all $i=1,\dots,m$ and zero otherwise. \;
+
 % 	\caption{$\KlmApprox (X, m)$}  
 % 	\label{alg:sequence}
-%\end{algorithm}
-
-\begin{theorem}\label{the:algo}
-	$\KlmApprox$ returns an $m$-optimal-approximation of $X$.
-\end{theorem}
-\begin{proof}
-By the construction of $G$ we get that the path $\vec{p}$ obtained in line 2 of  $\KlmApprox$ describes a set $S$ of support of size at most $m$ for which $\varepsilon(S,X)$ is minimal.
+% \end{algorithm}
+
+% \begin{theorem}\label{the:algo}
+% 	$\KlmApprox$ returns an $m$-optimal-approximation of $X$.
+% \end{theorem}
+% \begin{proof}
+% By the construction of $G$ we get that the path $\vec{p}$ obtained in line 2 of  $\KlmApprox$ describes a set $S$ of support of size at most $m$ for which $\varepsilon(S,X)$ is minimal.
 Then from Definition \ref{def:construction} and Corollary \ref{col:Xprime} we construct $X'$ in lines 3 of 	$\KlmApprox$ such that $d_K(X,X') = \varepsilon(X,S)$.
@@
 From Lemma \ref{lem:supContained} we then get that $X'$ is an $m$-optimal-approximation of $X$.
-\end{proof}
-
-The memory and time  complexities of $\KlmApprox$ are as follows.
-
-\begin{theorem}\label{the:complexity}
-	The $\KlmApprox(X,m)$ algorithm runs in time $O(n^2m)$, using $O(n^2)$ memory where $n=|\support(X)|$.
-\end{theorem}
-\begin{proof}
-	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory.
+% \end{proof}
+
+% The memory and time  complexities of $\KlmApprox$ are as follows.
+
+% \begin{theorem}\label{the:complexity}
+% 	The $\KlmApprox(X,m)$ algorithm runs in time $O(n^2m)$, using $O(n^2)$ memory where $n=|\support(X)|$.
+% \end{theorem}
+% \begin{proof}
+% 	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory.
 Computing the shortest path can be achieved, for example, by the algorithm described in~\cite{guerin2002computing} in time $O(n^2 m)$ and no additional memory allocation.
-\end{proof}
-%\begin{proof}
-%	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory. The number of edges in $G$ is $O(|E|)=O(n^2)$, for every edge the weight is at most the sum of all
-%probabilities between the source node $s$ and the target node $t$, which can be calculated efficiently by aggregating the weights of already calculated edges. 
-%	The construction is also the only stage that requires memory allocation, specifically $O(|E|+|V|)=O(n^2)$.
-%	Next using the Bellman-Ford algorithm on $G$ for $m$ iterations   takes $O(m(|E|+|V|))\approx O(mn^2)$. [[DF: cite Corman or some algorithms book]]. 
-%	Finally deriving the new random variable $X'$ from the computed path $\vec{p}$ takes $O(m)$ time: For every node $x_i$ in $\vec{p}$ (at most $m$ nodes), use the already calculated weights to find the probability mass function $f_{X'}(x_i)$.
-%	To conclude, the time complexity  of $\KlmApprox(X,m)$ is $O(n^2+mn^2+m)=O(mn^2)$ and memory complexity is $O(E+V)=O(n^2)$.
-%\end{proof}
-
-%%%%%%%%%OLD SEC 3.2 %%%%%%%%%%%%%%%%%%%%%%%%%%%5
-
-%\subsection{Step 2: Finding an $S$ that minimizes $\varepsilon(X,S)$}
-%Chakravarty, Orlin, and Rothblum~\cite{chakravarty1982partitioning} proposed a polynomial-time method that, given a certain objective functions (additive), finds an optimal consecutive partition.
-Their method involves the construction of a graph such that the (consecutive) set partitioning problem is reduced to the problem of finding the shortest path in that graph.
-
-%The $\KlmApprox$ algorithm (Algorithm~\ref{alg:optapprox}) starts by constructing a directed weighted graph $G$ similar to the method of Chakravarty, Orlin, and Rothblum~\cite{chakravarty1982partitioning}.
-The nodes $V$ consist of the support of $X$ together with an extra two nodes, $-\infty$ and $\infty$ for technical reasons, whereas the edges $E$ connect every pair of nodes in one direction (lines 1-2).
-The weight $w$ of each edge $e=(x,y)\in E$ is determined by one of two cases as in Definition~\ref{def:weight}.
-%If nodes $x$ or $y$ are the $-\infty$ or $\infty$ nodes respectively then the weight is the probability of $X$ to get a value between $x$ and $y$, non inclusive, i.e., $w(e)=Pr(x<X<y)$.
-If $x$ and $y$ are not a $-\infty$ or $\infty$ nodes, here the weight is the probability of $X$ to get a value between $x$ and $y$, non inclusive, divided by two i.e., $w(e)=Pr(x<X<y)/2$.
-%The values taken are non inclusive, since we are interested only in the error value.
-The source node of the shortest path problem at hand corresponds to the $-\infty$ node added to $G$ in the construction phase, and the target node is the extra node $\infty$.
-%The set of all solution paths in $G$, i.e., those starting at $-\infty$ and ending in $\infty$ with at most $m$ edges, is called $paths(G, -\infty, \infty)$.
-The goal is to find the path $l$ in $paths(G, -\infty, \infty)$ with the lightest bottleneck (line 3).
-This can be achieved by using the $Bellman-Ford$ algorithm with two tweaks.
-The first is to iterate the graph $G$ in order to find only paths with length of at most $m$ edges.
-The second is to find the lightest bottleneck as opposed to the traditional objective of finding the shortest path.
-This is performed by modifying the manner of ``relaxation'' to $bottleneck(x) = min[max(bottleneck(v),w(e))]$, done also in~\cite{guerin2002computing, shufan2011two}.
-Consequently, we find the lightest maximal edge in a path of length $\leq m$, which represents the minimal error, $\varepsilon(X,S)$, defined in Definition~\ref{def:error} where the nodes in path $l$ represent the elements in set $S$.
-The approximated random variable $X'$ is then derived from the resulting path $l$ (lines 4-5).
-Every node $x\in l$ represent a value in the new calculated random variable $X'$, we than iterate the path $l$ to find the probability of the event $f_{X'}(x)$ as described in Definition~\ref{def:construction}.
-
-%\begin{algorithm}\label{alg:optapprox}
-%	\DontPrintSemicolon
-%	\SetKwFunction{Convolv}{Conv}
-%	\SetKwFunction{getPartition}{getPartition}
-%	\SetKwFunction{bellmanFordMinMaxM}{bellmanFordMinMaxM}
-%	$S = \support(X)\cup \{\infty,-\infty\}$\;
-%	$G=(V,E)=(S, \{ (x,y)  \colon  x<y \})$  \;
-%	$(x_0,\dots,x_{m+1}) = l \in \operatorname{argmin}\limits_{l \in paths(G,-\infty,\infty),|l|\leq m}  \max \{ w(e)\colon e \in l  \}$  \;
-%	\For{$0<i<m+1$ }{
-%		$f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$
-%	}	
-%	\Return $X'$\;
-%	
-%	\caption{$\KlmApprox (X, m)$}  
-%	\label{alg:sequence}
-%\end{algorithm}
-
-%\begin{algorithm}\label{alg:optapprox}
-%	\DontPrintSemicolon
-%	\SetKwFunction{Convolv}{Conv}
-%	\SetKwFunction{getPartition}{getPartition}
-%	\SetKwFunction{bellmanFordMinMaxM}{bellmanFordMinMaxM}
-%	$S = \support(X)\cup \{\infty,-\infty\}$\;
-%	$G=(V,E)=(S, \{e= (x,y) \in S^2 \colon  x<y \})$ \;
-%	
-%	\ForEach{$e=(x,y) \in  E $ }{
-%		\If {$i=\infty \text{ OR } j=-\infty$}{
-%			$w(e) = Pr(i<X<j)$
-%		}
-%		\Else{$w(e) = Pr(i<X<j)/2$}
-%	}
-%	
-%	/* The following can be obtained, e.g., using the Bellman-Ford algorithm */\;
-%	$l^*= \operatorname{argmin}\limits_{l \in paths(G, -\infty, \infty,|l|\leq m}  \max \{ w(e)\colon e \in l  \}$ \;
-%	
-%	\ForEach{$e=(i,j) \in  l^* $ }{
-%		\If {$i=-\infty$}{
-%			$f_{X'}(j) = f_{X}(j) + Pr(i\leq X<j)$
-%		}
-%		\ElseIf{$j==\infty$}{
-%			$f_{X'}(i) = f_{X'}(i) + Pr(i\leq X<j)$
-%		}
-%		\Else{
-%			$f_{X'}(i) = f_{X'}(i) + Pr(i\leq X<j)/2$\;
-%			$f_{X'}(j) = f_{X}(j) + Pr(i\leq X<j)/2$\;
-%		}
-%		
-%	}	
-%	\Return $X'$\;
-%	
-%	\caption{$\KlmApprox (X, m)$}  
-%	\label{alg:sequence}
-%\end{algorithm}
-
-%\begin{theorem}\label{the:algo}
-%	$\KlmApprox(X,m)$ is an $m$-optimal-approximation of $X$.
-%\end{theorem}
-%\begin{proof}
-%If we consider the vertexes $S= l \setminus \{-\infty,\infty\}$ for a path $l \in paths(G,-\infty,\infty)$ we have that $\max \{ w(e)\colon e \in l  \} = \varepsilon(X,S)$.
-Therefore, line 3 of the algorithm essentially computes a set $S \in \operatorname{argmin}_{S \subseteq \support(X), |S|\leq m} \varepsilon(X,S)$.
-By Corollary~\ref{col:Xprime}, the variable $X'$ constructed in lines 4 and 5 satisfies $d_K(X,X') = \varepsilon(X,S)$ and by the minimality of $S$ and by Proposition~\ref{prop:minimal}, it is an optimal approximation.
-%\end{proof}
-
-%\begin{theorem}\label{the:complexity}
-%	The $\KlmApprox(X,m)$ algorithm runs in time $O(mn^2)$, using $O(n^2)$ memory where $n=|\support(X)|$.
-%\end{theorem}
-
-%\begin{proof}
-%	Constructing the graph $G$ takes $O(n^2)$.
-The number of edges is $O(E)\approx O(n^2)$ and for every edge the weight is at most the sum of all probabilities between the source node $-\infty$ and the target node $\infty$, which can be done efficiently by aggregating the weights of already calculated edges.
-%	The construction is also the only stage that requires memory allocation, specifically $O(E+V)=O(n^2)$.
-%	Finding the shortest path takes $O(m(E+V))\approx O(mn^2)$.
-
-%	[[GW: put a reference to the work of the fellows from the Technion to avoid some of this?]]
-
-%	Since $G$ is DAG (directed acyclic graph) finding a shortest path takes $O(E+V)$. We only need to find paths of length $\leq m$, which takes $O(m(E+V))$.
-%	Deriving the new random variable $X'$ from the computed path $l$ takes $O(m)$.
-For every node $x_i$ in $l$ (at most $m$ nodes), use the already calculated weights to find the probability mass function $f_{X'}(x_i)$.
-%	To conclude, the worst case run-time complexity is $O(n^2+mn^2+m)=O(mn^2)$ and memory complexity is $O(E+V)=O(n^2)$.
-%\end{proof}
+% \end{proof}
+% %\begin{proof}
+% %	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory. The number of edges in $G$ is $O(|E|)=O(n^2)$, for every edge the weight is at most the sum of all
+% %probabilities between the source node $s$ and the target node $t$, which can be calculated efficiently by aggregating the weights of already calculated edges. 
+% %	The construction is also the only stage that requires memory allocation, specifically $O(|E|+|V|)=O(n^2)$.
+% %	Next using the Bellman-Ford algorithm on $G$ for $m$ iterations   takes $O(m(|E|+|V|))\approx O(mn^2)$. [[DF: cite Corman or some algorithms book]]. 
+% %	Finally deriving the new random variable $X'$ from the computed path $\vec{p}$ takes $O(m)$ time: For every node $x_i$ in $\vec{p}$ (at most $m$ nodes), use the already calculated weights to find the probability mass function $f_{X'}(x_i)$.
+% %	To conclude, the time complexity  of $\KlmApprox(X,m)$ is $O(n^2+mn^2+m)=O(mn^2)$ and memory complexity is $O(E+V)=O(n^2)$.
+% %\end{proof}
 
@@
 
-As proven in Section~\ref{sec:alg}, given $m$, a single step of $\KlmApprox$ guarantees an optimal $m$-approximation.
+As proven in Section~\ref{sec:algEfficient}, given $m$, a single step of $\KlmApprox$ guarantees an optimal $m$-approximation.
 However in the setting considered here we need to repetitively use $\KlmApprox$, thus the optimality of the eventually obtained random variable is not guaranteed.
@@
 	\renewcommand{\arraystretch}{1.3}
-	\begin{tabular}{|c|c|c|c|c|c|c|}
+	\begin{tabular}{|p{1.05cm}|p{0.25cm}|p{0.93cm}|p{0.93cm}|p{1.05cm}|p{0.75cm}|p{0.75cm}|}
 		\hline
-		\multirow{2}{*}{Task Tree} & \multirow{2}{*}{$M$} & {Kolmogorov} & {$\OptTrim$} & {$\Trim$} & \multicolumn{2}{c|}{Sampling} \\ \cline{3-7} 
+		\multirow{2}{*}{Task Tree} & \multirow{2}{*}{$M$} & {$\KlmApprox$} & {$\OptTrim$} & {$\Trim$} & \multicolumn{2}{c|}{Sampling} \\ \cline{3-7} 
 		&	& $m/N{=}10$ & $m/N{=}10$ & $\varepsilon\cdot N{=}0.1$ & $s{=}10^{4}$& $s{=}10^{6}$ \\ \hline
@@
 Figure~\ref{fig:runtime} presents a comparison of the run-time performances of an exact computation and approximated computations with $\KlmApprox$ and $\Trim$ as operators.
-We examined three versions of $KlmApprox$ each of which with different run-time,  The computation is a summation of a sequence of random variables with support size of $m{=}10$, where the number $n$ of variables varies from 6 to 19.
+We examined three versions of $\KlmApprox$ each of which with different run-time,  The computation is a summation of a sequence of random variables with support size of $m{=}10$, where the number $n$ of variables varies from 6 to 19.
 In this experiment, we executed the $\KlmApprox$ operator with $m{=}10$ after performing each convolution between two random variables, in order to maintain a support size of 10 in all intermediate computations.
@@
 	xtick={6,10,15,19},
-	legend pos=outer north east,
+	legend pos=north west, style={font=\tiny\selectfont},
 	ymajorgrids=true,
@@
 	]
+
+	\addplot[
+	color=red,
+	mark=x,
+	]
+	coordinates {
+		(6  , 0.00977492332458)
+		(7  , 0.0880949497223)
+		(8  , 0.556006193161)
+		(9  , 1.23386096954)
+		(10 , 2.37807798386)
+		(11 , 4.2376730442)
+		(12 , 6.03167200089)
+		(13 , 8.61568593979)
+		(14 , 14.1664741039)
+		(15 , 21.7874569893)
+		(16 , 30.5902190208)
+		(17 , 97.9485061169)
+		(18, 186.025614977) 
+		(19, 327.884781122) 
+	};
+	\addlegendentry{Exact (no trimming)}
 
@@
     \addplot[
-	color=black,
-	mark=square,
+	color=pink,
+	mark=o,
 	]
 	coordinates {
-		(6 , 0.630314826965332) 
-		(7 , 0.7709379196166992) 
-		(8 , 0.7499942779541016) 
-		(9 , 0.8746609687805176) 
-		(10, 1.208768367767334) 
-		(11, 1.1908512115478516) 
-		(12, 1.3902842998504639) 
-		(13, 1.6106953620910645) 
-		(14, 1.7124199867248535) 
-        (15, 1.7134194374084473)
-		(16, 2.345730781555176) 
-		(17, 2.131302833557129) 
-		(18, 2.1731927394866943)
-		(19, 2.9610767364501953) 
+		(6  , 0.04986763000488281)
+		(7  , 0.0747988224029541)
+		(8  , 0.0827784538269043)
+		(9  , 0.11668658256530762)
+		(10 , 0.12765932083129883)
+		(11 , 0.14760947227478027)
+		(12 , 0.16057085990905762)
+		(13 , 0.23337483406066895)
+		(14 , 0.1884934902191162)
+		(15 , 0.2094745635986328)
+		(16 , 0.23337602615356445)
+		(17 , 0.3201446533203125)
+		(18, 0.3011953830718994) 
+		(19, 0.3091733455657959) 
 	};
-	\addlegendentry{Kolmogorov Approx}
+	\addlegendentry{$n^2log(n) \KlmApprox$}
+
+	\addplot[
+	color=orange,
+	mark=x,
+	]
+	coordinates {
+		(6  , 0.003989458084106445)
+		(7  , 0.00398707389831543)
+		(8  , 0.004992485046386719)
+		(9  , 0.006980419158935547)
+		(10 , 0.008974790573120117)
+		(11 , 0.010970354080200195)
+		(12 , 0.007979631423950195)
+		(13 , 0.00997161865234375)
+		(14 , 0.013960838317871094)
+		(15 , 0.014958381652832031)
+		(16 , 0.017947673797607422)
+		(17 , 0.017951011657714844)
+		(18, 0.018949508666992188) 
+		(19, 0.026926517486572266) 
+	};
+	\addlegendentry{$nlog(n) \KlmApprox$}
 
@@
 	\addlegendentry{$\Trim$}
-
-	\addplot[
-	color=red,
-	mark=x,
-	]
-	coordinates {
-		(6  , 0.00977492332458)
-		(7  , 0.0880949497223)
-		(8  , 0.556006193161)
-		(9  , 1.23386096954)
-		(10 , 2.37807798386)
-		(11 , 4.2376730442)
-		(12 , 6.03167200089)
-		(13 , 8.61568593979)
-		(14 , 14.1664741039)
-		(15 , 21.7874569893)
-		(16 , 30.5902190208)
-		(17 , 97.9485061169)
-		(18, 186.025614977) 
-		(19, 327.884781122) 
-	};
-	\addlegendentry{Exact (no trimming)}
-
-	\addplot[
-	color=orange,
-	mark=x,
-	]
-	coordinates {
-		(6  , 0.003989458084106445)
-		(7  , 0.00398707389831543)
-		(8  , 0.004992485046386719)
-		(9  , 0.006980419158935547)
-		(10 , 0.008974790573120117)
-		(11 , 0.010970354080200195)
-		(12 , 0.007979631423950195)
-		(13 , 0.00997161865234375)
-		(14 , 0.013960838317871094)
-		(15 , 0.014958381652832031)
-		(16 , 0.017947673797607422)
-		(17 , 0.017951011657714844)
-		(18, 0.018949508666992188) 
-		(19, 0.026926517486572266) 
-	};
-	\addlegendentry{$nlog(n) \OptTrim$}
-
-    \addplot[
-	color=pink,
-	mark=x,
-	]
-	coordinates {
-		(6  , 0.04986763000488281)
-		(7  , 0.0747988224029541)
-		(8  , 0.0827784538269043)
-		(9  , 0.11668658256530762)
-		(10 , 0.12765932083129883)
-		(11 , 0.14760947227478027)
-		(12 , 0.16057085990905762)
-		(13 , 0.23337483406066895)
-		(14 , 0.1884934902191162)
-		(15 , 0.2094745635986328)
-		(16 , 0.23337602615356445)
-		(17 , 0.3201446533203125)
-		(18, 0.3011953830718994) 
-		(19, 0.3091733455657959) 
-	};
-	\addlegendentry{$n^2log(n) \OptTrim$}
 	\end{axis}
@@
 
-\paragraph{Comparison to Linear Programming.}
-We also compared the run-time of $\KlmApprox$ with a linear programing (LP) algorithm that also guarantees optimality, as described and discussed for example in~\cite{pavlikov2016cvar}.
-For that, we used the ``Minimize'' function of Wolfram Mathematica as a  state-of-the-art implementation of linear programing, encoding the problem by the LP problem $\min_{\alpha \in \mathbb{R}^n} \| x - \alpha\|_\infty$ subject to $\|\alpha\|_0 \leq m$ and $\| \alpha \|_1 =1$.
-The run-time comparison results were clear and persuasive: $\KlmApprox$ significantly outperforms the LP algorithm.
+% \paragraph{Comparison to Linear Programming.}
+% We also compared the run-time of $\KlmApprox$ with a linear programing (LP) algorithm that also guarantees optimality, as described and discussed for example in~\cite{pavlikov2016cvar}.
+% For that, we used the ``Minimize'' function of Wolfram Mathematica as a  state-of-the-art implementation of linear programing, encoding the problem by the LP problem $\min_{\alpha \in \mathbb{R}^n} \| x - \alpha\|_\infty$ subject to $\|\alpha\|_0 \leq m$ and $\| \alpha \|_1 =1$.
+% The run-time comparison results were clear and persuasive: $\KlmApprox$ significantly outperforms the LP algorithm.
 For a random variable with support size $n=10$ and $m=5$, the LP algorithm run-time was $850$ seconds, where the $\KlmApprox$ algorithm run-time was less than a tenth of a second.
 For $n=100$ and $m=5$, the $\KlmApprox$ algorithm run-time was 0.14 seconds and the LP algorithm took more than a day.
-Since it is not trivial to formally analyze the run-time of the LP algorithm, we conclude by the reported experiment that in this case the LP algorithm might not be as efficient as $\KlmApprox$ algorithm whose complexity is proven to be polynomial in Theorem~\ref{the:complexity}.
+% Since it is not trivial to formally analyze the run-time of the LP algorithm, we conclude by the reported experiment that in this case the LP algorithm might not be as efficient as $\KlmApprox$ algorithm whose complexity is proven to be polynomial in Theorem~\ref{the:complexity}.
 

### 2018-09-05 Kolmogorov_Approx.tex
.
|support(X)| -> |X|

@@
 
-The size of a random variable is measured here by the size of its support, the set of possible outcomes, $|X|=|\support(X)|=|\{x\colon Pr(X=x) \neq 0\}|$.
+The size of a random variable is measured here by the size of its support, the set of possible outcomes, $|X|=|X|=|\{x\colon Pr(X=x) \neq 0\}|$.
 When probability mass functions are maintained as explicit tables, as done in many implementations of statistical software, the size of the support of the variable is proportional to the amount of memory needed to store it and to the complexity of the computations that manipulate it.
@@
 \begin{definition}
-	A random variable $X'$ is an optimal $m$-approximation of a random variable $X$ if $|\support(X')| \leq m$ and there is no random variable $X''$ such that $|\support(X'')| \leq m$ and $d_K(X,X'') < d_K(X,X')$.
+	A random variable $X'$ is an optimal $m$-approximation of a random variable $X$ if $|X'| \leq m$ and there is no random variable $X''$ such that $|X''| \leq m$ and $d_K(X,X'') < d_K(X,X')$.
 \end{definition}
@@
 Both of the algorithms presented in this section are using the dual problem in order to find the optimal $m$-approximation of $X$.
-The dual problem is: given a random variable $X$ with $|\support(X)| = n$, and some $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $|\support(X')|\leq m$ where $0< m \leq n$ and $d_K(X,X')$ is minimal.
+The dual problem is: given a random variable $X$ with $|X| = n$, and some $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $|X'|\leq m$ where $0< m \leq n$ and $d_K(X,X')$ is minimal.
 
@@
 \begin{theorem}\label{the:complexityDual}
-	The $dual(X,\varepsilon)$ algorithm runs in time $O(n)$, using $O(n)$ memory where $n=|\support(X)|$.
+	The $dual(X,\varepsilon)$ algorithm runs in time $O(n)$, using $O(n)$ memory where $n=|X|$.
 \end{theorem}
@@
 In lines 10-19 we perform a binary search over the set $E$, in every step of the binary search we run the $X' = dual(X,\varepsilon)$ algorithm.
-If the size of $|\support(X')|>m$ then we know that the error $\varepsilon$ is too small and need to extend the search in the right side of $E$, if the size of $|\support(X')|<m$ then we know that the error $\varepsilon$ is too big and need to extend the search in the left side of $E$, otherwise we found the correct $m$.
+If the size of $|X'|>m$ then we know that the error $\varepsilon$ is too small and need to extend the search in the right side of $E$, if the size of $|X'|<m$ then we know that the error $\varepsilon$ is too big and need to extend the search in the left side of $E$, otherwise we found the correct $m$.
 We run the search twice to handle the extreme case where $m \notin \{\forall \varepsilon\in E: |dual(X,\varepsilon)|\}$ and return the smallest $m'$ closest to $m$.
@@
                 $k' \gets k$,$k \gets \lceil (l + r)/2 \rceil$\;
-        		$X' \gets dual(X,e_k)$, $m' \gets |\supp(X')|$\;
+        		$X' \gets dual(X,e_k)$, $m' \gets |X'|$\;
         		\lIf{$m' < m$}{
@@
 \begin{theorem}\label{the:complexityDual}
-	The $binsearchApprox(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|\support(X)|$.
+	The $binsearchApprox(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|X|$.
 \end{theorem}
@@
 In line 4 We describe implicitly the sorted matrix $E$, and in lines 3-7 we perform a search over this matrix, in every step of the search we run the $X' = dual(X,\varepsilon)$ algorithm.
-If the size of $|\support(X')|>m$ then we know that the error $e$ is too small and need to extend the search in the lower side of the matrix, if the size of $|\support(X')|<m$ then we know that the error $e$ is too big and need to extend the search in the right side of the matrix and store this $e$ in $S$.
+If the size of $|X'|>m$ then we know that the error $e$ is too small and need to extend the search in the lower side of the matrix, if the size of $|X'|<m$ then we know that the error $e$ is too big and need to extend the search in the right side of the matrix and store this $e$ in $S$.
 We store in set $S$ all possible candidates for the correct $e$ and in line 8 we get the maximal $m$ with the minimal $e$ value.
@@
 
-		$X' \gets dual(X,e_{i,j})$, $m' \gets |\supp(X')|$\;
+		$X' \gets dual(X,e_{i,j})$, $m' \gets |X'|$\;
 
@@
 
-		$S \gets  \{ ((1, 1)),(\lceil n/2 \rceil+1,\lceil n/2 \rceil)) \}$, $S' \gets \emptyset$\;
+		$w \gets 2^{\lceil \log_2(n/2) \rceil}$,
+		$h \gets 2^{\lceil \log_2(n/2+1) \rceil}$ \;
+
+		$S \gets  \{ ((1, 1)),(w,h)) \}$, $S' \gets \emptyset$\;
 
@@
 		{
-			$S' \gets S$\;
-
-			$S \gets \displaystyle \bigcup_{s \in S} split(s)$\;
+			$S' \gets S$,
+			$S \gets  \bigcup_{s \in S} split(s)$\;
 
 			$e^- {\gets} median(\{ e_{i_1,j_1} \colon ((i_1,j_1),(i_2,j_2)) \in S \}) $\;		
+			$e^+ {\gets} median(\{ e_{i_2,j_2} \colon ((i_1,j_1),(i_2,j_2)) \in S \}) $\;
 
-			$X' \gets dual(X,e^-)$, $m' \gets |\supp(X')|$\;
+			\For{$ e \in \{ e^-,e^+ \}$} {
+				$X' \gets dual(X,e)$, $m' \gets |X'|$\;
 
 				\If {$m' \leq m$} {
-				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_1,j_1} {>} e^- \}$ \;
+					$S \gets$ $S \setminus \{ ((i_1,j_1),(i_2,j_2)) \in S \colon e_{i_1,j_1} > e \}$ \;
 				}
@@
 				{
-				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_2,j_2} {\leq} e^- \}$ \;
+					$S \gets$ $S \setminus \{ ((i_1,j_1),(i_2,j_2)) \in S \colon e_{i_2,j_2} \leq e \}$ \;
 				}
-
-			$e^+ {\gets} median(\{ e_{i_2,j_2} \colon ((i_1,j_1),(i_2,j_2)) \in S \}) $\;
-			$X' \gets dual(X,e^+)$, $m' \gets |\supp(X')|$\;
-
-			\If {$m' \leq m$} {
-				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_1,j_1} {>} e^+ \}$ \;
 			}
-			\Else %{$m'  > m$}
-			{
-				$S \gets S \setminus \{ ((i_1,j_1),(i_2,j_2)) {\in} S \colon e_{i_2,j_2} {\leq} e^+ \}$ \;
-			}
-
 		}
@@
 
-		\Return{$
+		\Return{\hspace{4cm}$
 			\{ ((i_1, j_1), (i^-, j^-)),
-			((i_1, j^+), (i^-, j_2)),
-			((i^+, j_1), (i_2, j^-)),
+			((i_1, j^+), (i^-, j_2))$,
+			$((i^+, j_1), (i_2, j^-)),
 			((i^+, j^+), (i_2, j_2))    \}$}
@@
 	$$e_{i,j} = \begin{cases}
-	c_j   & \text{if } i=\lfloor n/2 \rfloor+1; \\
-	1-c_i & \text{if } j=\lceil n/2 \rceil; \\
-	(c_{n+1-j} {-} c_i)/2  & \text{otherwise}
+	c_j   & \text{if } i > \lfloor n/2 \rfloor; \\
+	1-c_i & \text{if } j \geq \lceil n/2 \rceil; \\
+	(c_{n+1-j} {-} c_i)/2  & \text{otherwise}.
 	\end{cases}$$
@@
 % \begin{theorem}\label{the:complexity}
-% 	The $\KlmApprox(X,m)$ algorithm runs in time $O(n^2m)$, using $O(n^2)$ memory where $n=|\support(X)|$.
+% 	The $\KlmApprox(X,m)$ algorithm runs in time $O(n^2m)$, using $O(n^2)$ memory where $n=|X|$.
 % \end{theorem}

### 2018-09-05 Kolmogorov_Approx.tex
n/2 -> n
wrong e_{i,j}
After talking with Liat
no lemma corrected dual problem

@@
 \section{An algorithm for optimal approximation}\label{sec:algEfficient}
-In the scope of this section, let $X$ be a given random variable with a finite support of size $n$, and let  $0<m\leq n$ be a given complexity bound.
-The section evolves by presenting two algorithms for finding an optimal $m$-approximation of $X$.
-The first algorithm is $binsearchApprox(X,m)$ (Algorithm~\ref{alg:naive}) which runs in time of $O(n^2log(n))$ and the second one $linApprox(X,m)$ (Algorithm~\ref{alg:linear}) which runs in time of $O(nlog(n))$.
-We present both $binsearchApprox(X,m)$ and $linApprox(X,m)$ since Algorithm~\ref{alg:linear} is based on Algorithm~\ref{alg:naive} but carry major run-time improvement.
+In the scope of this section, let $X$ be a random variable such that $|X|=n$, and let  $0<m\leq n$.
+We present algorithms for finding optimal $m$-approximations of $X$.
+The first algorithm is $binsearchApprox(X,m)$ (Algorithm~\ref{alg:naive}) which runs in time of $O(n^2\log(n))$.
+The second algorithm, $linApprox(X,m)$ (Algorithm~\ref{alg:linear}), runs in time of $O(n\log(n))$.
+%We present both $binsearchApprox(X,m)$ and $linApprox(X,m)$ since Algorithm~\ref{alg:linear} is based on Algorithm~\ref{alg:naive} but carry major run-time improvement.
 
-We begin our dissection by presenting a useful fact that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:
+%We begin our dissection by presenting a useful fact that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:
+%
+%\begin{lemma}\label{lem:supContained}
+%	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
+%\end{lemma}
+%
+%\begin{proof}
+%	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
+%	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.
+Since we only "shifted" the probability mass of $X''$ to the support of $X$, we have that $f_{X'}$ is a probability mass function and therefore $X'$ is well defined.
+%	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
+%	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
+%\end{proof}
 
-\begin{lemma}\label{lem:supContained}
-	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
-\end{lemma}
-
-\begin{proof}
-	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
-	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.
-Since we only "shifted" the probability mass of $X''$ to the support of $X$, we have that $f_{X'}$ is a probability mass function and therefore $X'$ is well defined.
-	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
-	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
-\end{proof}
-
-Both of the algorithms presented in this section are using the dual problem in order to find the optimal $m$-approximation of $X$.
-The dual problem is: given a random variable $X$ with $|X| = n$, and some $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $|X'|\leq m$ where $0< m \leq n$ and $d_K(X,X')$ is minimal.
+The algorithms presented in this section are using a dual problem in order to find the optimal $m$-approximation of $X$.
+The dual problem is: given a random variable $X$ and $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $d_k(X,X')\leq \varepsilon$ and $|X'|$ is minimal.
 
@@
 	\DontPrintSemicolon
-	Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.\;
+	%Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.\;
     $f \gets 0$, $l \gets n$+1\; 
@@
 
-	\caption{$dual(X,\varepsilon)$}   
+	\caption{$dual(\{(x_i, c_i)\}_{i=1}^n,\varepsilon)$  }   
 	\label{alg:dual}
@@
 
-		\lIf {$m'  > m$}
+		\lIf {$m'  \leq m$}
 		{
@@
 		}
-		\lIf {$m' \leq m$} {
+		\lIf {$m' > m$} {
 			$i \gets i + 1$, $S \gets S \cup (m',e)$			
@@
 
-		$S \gets  \{ ((1, 1)),(w,h)) \}$, $S' \gets \emptyset$\;
+		$S \gets  \{ ((1, 1),(w,h)) \}$, $S' \gets \emptyset$\;
 
@@
 	$$e_{i,j} = \begin{cases}
-	c_j   & \text{if } i > \lfloor n/2 \rfloor; \\
-	1-c_i & \text{if } j \geq \lceil n/2 \rceil; \\
-	(c_{n+1-j} {-} c_i)/2  & \text{otherwise}.
+	c_j   & \text{if } j \leq n \wedge  i > n; \\
+	1-c_i & \text{if } i \leq n \wedge  j \geq n; \\
+	%(c_{n+1-j} {-} c_i)/2  & \text{if } i \leq n \wedge i{+}j\leq n{+}1; \\
+
+	%(c_{n+1-i} {-} c_i)/2  & \text{if } j \leq n \wedge i{+}j\leq n; \\
+
+	(c_{p-1 +i} {-} c_{p+1-j})/2  & \text{if } i \leq n \wedge i{+}j\leq n{+}1; \\
+
+	(c_{p-1 +i} {-} c_{p+1-i})/2  & \text{if } i \leq n \wedge i{+}j\leq n{+}1; \\
+
+	\infty  & \text{otherwise}.
 	\end{cases}$$
@@
 The algorithms of Cohen et al.
-were taken "as is" from in the supplementary material to~\cite{cohen2015estimating}.
+were taken ``as is" from in the supplementary material to~\cite{cohen2015estimating}.
 

### 2018-09-05 Kolmogorov_Approx.tex
Updates from ShareLaTeX

@@
 \setlength{\pdfpageheight}{11in}  %Required
+
+\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=100]{microtype}
 
@@
 \SetKwFunction{mEqOne}{mEqOne} 
-\DeclareMathOperator{\KlmApprox}{Approx}
-%\DeclareMathOperator{\OptTrim}{KolmogorovApprox}
+\DeclareMathOperator{\KlmApprox}{linApprox}
+\DeclareMathOperator{\BinsApprox}{binsApprox}
 \DeclareMathOperator{\OptTrim}{OptTrim}
@@
   \pdfinfo{
-	/Title (Deadline estimation by using an optimal approximation of discrete random variables with respect to the Kolmogorov distance
+	/Title (Optimal Approximation of Discrete Random Variables for Estimation of Probabilities of Missing Deadlines
 	)
@@
 
-Various approaches for approximation of probability distributions are studied in the literature~\cite{AMCR83,pavlikov2016cvar,PS77,vidyasagar2012metric,cohen2015estimating,CohenGW18}. 
+Various approaches for approximation of probability distributions are studied in the literature~\cite{PS77,AMCR83,vidyasagar2012metric,cohen2015estimating,pavlikov2016cvar,CohenGW18}. 
 These approaches vary in the types random variables considered, how they are represented, and in the criteria used for evaluation of the quality of the approximations.
@@
 In other words, we minimise the Kolmogorov distance between the approximation and the original random variable.
-Our motivation for this is estimation of the probability for missing deadlines, as described, e.g.,in~\cite{cohen2015estimating} and in~\cite{Kashef18}.
+Our motivation for this is estimation of the probability for missing deadlines, as described, e.g., in Cohen et al.~\cite{cohen2015estimating,CohenGW18} and in~\cite{Kashef18}.
 Specifically, when $X$ represents the probability distribution of the time to complete some complex schedule and we cannot afford to maintain the full table of its probability mass function, we propose an algorithm for producing a smaller table, whose size can be specified, such that probabilities for missing deadlines are preserved as much as possible.
@@
 The case study examined in this paper is the problem of task trees with deadlines~\cite{cohen2015estimating,CohenGW18}.
-Hierarchical planning is a well-established field in AI~\cite{thomas1988hierarchical,erol1994htn,erol1996complexity}, and is still relevant nowadays~\cite{alford2016hierarchical,xiao2017hierarchical}.
 A hierarchical plan is a method for representing problems of automated planning in which the dependency among tasks can be given in the form of networks, here we focus on hierarchical plans represented by task trees.
@@
 The objective in this context is to compute the probability that a given plan is valid, or more formally computing $P(X<T)$, where $X$ is a random variable representing the makespan of the plan and $T$ is the deadline.
-The problem of finding the probability that a task tree satisfies a deadline is known to be NP-hard~\cite{mohring2001scheduling}.
+The problem of finding the probability that a task tree satisfies a deadline is known to be NP-hard~\cite{cohen2015estimating}.
 In fact, even the problem of summing a set of random variables is NP-hard~\cite{mohring2001scheduling}.
-This is an example of an explicitly given random variable that we need to estimate deadline meeting probabilities for.
+This is an example of an explicitly given random variable that we need to estimate deadline missing probabilities for.
 
@@
 In Section~\ref{sec:relwork} we describe how our work relates to other algorithms and problems studied in the literature.
-In Section~\ref{sec:alg} we detail the proposed algorithm, analyse its properties, and prove the main theorem.
+In Section~\ref{sec:algEfficient} we detail the proposed algorithm, analyse its properties, and prove the main theorems.
 In Section~\ref{sec:exp} we demonstrate how the proposed approach performs on the problem of estimating the probability of missing deadlines in series-parallel schedules on randomly generated random variables and compare it to alternative approximation approaches from the literature.
@@
 These cannot be addressed by adding a constant (two) to $m$ because the first step is always present and because the requirement to end with the value one, restricts the set of eligible step functions.
-See Section~\ref{sec:alg} for more details.
+See Section~\ref{sec:algEfficient} for more details.
 
@@
 
-Our study is also related to the work of Pavlikov and Uryasev~\cite{pavlikov2016cvar}, where a procedure for producing a random variable $X'$ that optimally approximates a random variable $X$ is presented.
+Our study is also related to the work of Pavlikov and Uryasev~\shortcite{pavlikov2016cvar}, where a procedure for producing a random variable $X'$ that optimally approximates a random variable $X$ is presented.
 Their approximation scheme, achieved using linear programming, is designed for a different notion of distance called CVaR.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{An algorithm for optimal approximation}\label{sec:algEfficient}
-In the scope of this section, let $X$ be a random variable such that $|X|=n$, and let  $0<m\leq n$.
-We present algorithms for finding optimal $m$-approximations of $X$.
-The first algorithm is $binsearchApprox(X,m)$ (Algorithm~\ref{alg:naive}) which runs in time of $O(n^2\log(n))$.
-The second algorithm, $linApprox(X,m)$ (Algorithm~\ref{alg:linear}), runs in time of $O(n\log(n))$.
-%We present both $binsearchApprox(X,m)$ and $linApprox(X,m)$ since Algorithm~\ref{alg:linear} is based on Algorithm~\ref{alg:naive} but carry major run-time improvement.
+\section{Algorithms for optimal approximation}\label{sec:algEfficient}
+%In the scope of this section, let $X$ be a random variable ket $m$ be such that  $0<m\leq |X|$. We present algorithms for finding optimal $m$-approximations of $X$.
 
-%We begin our dissection by presenting a useful fact that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:
-%
-%\begin{lemma}\label{lem:supContained}
-%	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
-%\end{lemma}
-%
-%\begin{proof}
-%	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
-%	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.
-Since we only "shifted" the probability mass of $X''$ to the support of $X$, we have that $f_{X'}$ is a probability mass function and therefore $X'$ is well defined.
-%	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
-%	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
-%\end{proof}
-
-The algorithms presented in this section are using a dual problem in order to find the optimal $m$-approximation of $X$.
+We begin with presenting an algorithm for solving a problem that is dual to the $m$-approximation problem.
 The dual problem is: given a random variable $X$ and $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $d_k(X,X')\leq \varepsilon$ and $|X'|$ is minimal.
 
-We do not assume anything about the representation of the random variable $X$ given as an input to the $dual(X,\varepsilon)$ algorithm.
-However, we transform the representation of every given $X$, to the form of sorted CDF as described in line 1 in the algorithm, which takes $O(nlog(n))$ run-time and has to done only once.
-The $dual(X,\varepsilon)$ gets as input a random variable $X$ and some $\varepsilon$, the random variable $X$ is represented as in line 1, $X_{CDF} =\{(x_i, c_i)\}_{i=1}^n$ such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.
-In lines 3-4 we perform a single pass over $X_{CDF}$ starting from index 1 to find the last index where the cumulative distribution function of $X$ is less than $\varepsilon$, this index is now $f$.
-In lines 5-6 in the algorithm we start from the last index of $X_{CDF}$ which is $n$, and in decreasing order seek for the last index where the cumulative distribution function of $X$ is less than $1-\varepsilon$, this index is now $l$.
+We assume that the input to Algorithm~\ref{alg:dual} that solves the dual problem is a representation of the variable $X$ as a sorted CDF, i.e.,  as an array $X_{CDF}=\{(x_i, c_i)\}_{i=1}^n$ such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.
+In lines 2 we perform a single pass over $X_{CDF}$ starting from index 1 to find the last index where the cumulative distribution function of $X$ is less than $\varepsilon$, this index is now $f$.
+In line 3 we start from the last index of $X_{CDF}$ which is $n$, and in decreasing order seek for the last index where the cumulative distribution function of $X$ is less than $1-\varepsilon$, this index is now $l$.
 The last part of the algorithm is a pass on all elements in $X_{CDF}$ between the indices $f$ and $l$ in order to construct the $m$-approximation random variable of $X$, $X'$.
-In lines 9-10 we check if the difference between the first element in the current set of indices (which we call $b$) and the last element in the current set of indices (which we call $e+1$) is less that $2\varepsilon$.
+In lines 6-7 we check if the difference between the first element in the current set of indices (which we call $b$) and the last element in the current set of indices (which we call $e+1$) is less than $2\varepsilon$.
 If yes, we add the pair $\{(x_{b}, (c_b+c_e)/2 - s) \}$ to the set $S$.
 Otherwise, we add one to the counter of $e$.
-Note, the reason we need $s$ is to return the random variable $X'$ in a PDF representation since our main motivation is sum of random variables, this part takes $O(n)$ run-time.
 
@@
     $f \gets 0$, $l \gets n$+1\; 
-    \While{$c_{f +1} \leq \varepsilon$}{$f \gets f + 1$}
+    \lWhile{$c_{f +1} \leq \varepsilon$}{$f \gets f + 1$}
 
-    \While{$c_{l -1} \geq  1-\varepsilon$}{$l \gets l -1$}
+    \lWhile{$c_{l -1} \geq  1-\varepsilon$}{$l \gets l -1$}
 
@@
 
-\begin{theorem}\label{the:complexityDual}
-	The $dual(X,\varepsilon)$ algorithm runs in time $O(n)$, using $O(n)$ memory where $n=|X|$.
+\begin{theorem}\label{the:correctnessDual}
+	If  $\{(x_i, c_i)\}_{i=1}^n$ is such that $c_i=Pr(X \leq x_i)$ and $\supp(X)=\{x_1 < \cdots < x_n\}$ then  
+    $$dual(\{(x_i, c_i)\}_{i=1}^n,\varepsilon) \in \underset{X'\in \bar{\mathcal{B}}(X,\varepsilon)}{\operatorname{arg\,min}}\, |X'|$$  where $\bar{\mathcal{B}}(X,\varepsilon)=\{X'\colon d_K(X,X')\leq \varepsilon\}$.
 \end{theorem}
 \begin{proof}
-	This algorithm describes a single pass over the random variable $X$.
-Lines 3-4 and lines 5-6 are easy to follow, each takes $O(n)$ in the worst case.
-Lines 8-12 also describe one pass over $X$ since the counter $e$ is updated to $e+1$ at most $n$ times.
-All together we get run-time complexity of $O(3n)$ = $O(n)$.
+The number of level sets of the CDF of $X'$ is minimal: (1) The first and the last sets are of maximal length; (2) By construction, an extension of any of the other sets to the right will generate a random variable whose Kolmogorov distance from $X$ is bigger than $\varepsilon$; and (3) Extension of a level set to the left may either leave the number of level sets unchanged or combine it with the previous set, which will enlarge the Kolmogorov distance because it is equivalent to extending the previous set to the right.
+\end{proof}
+
+\begin{theorem}\label{the:complexityDual}
+	$dual(\{(x_i, c_i)\}_{i=1}^n,\varepsilon)$ runs in time $O(n)$, using $O(n)$ memory.
+\end{theorem}
+\begin{proof}
+This algorithm describes a single pass over $\{(x_i, c_i)\}_{i=1}^n$.
+Line 2 and line 3 are easy to follow, each takes $O(n)$ in the worst case.
+Lines 5-9 also describe a single pass since the counter $e$ is updated to $e+1$ at most $n$ times.
+All together we get run-time complexity of $O(n)$.
 We are constructing the set $S$ which is of size $n$ in the worst case, therefore, memory complexity is also $O(n)$.
@@
 
-The first technique we present is the $binsearchApprox(X,m)$ algorithm which is based on the work done by D{\'i}az-B{\'a}nez and Mesa~\cite{diaz2001fitting}.
-There are couple of significant changes between our $binsearchApprox(X,m)$ algorithm and the algorithm suggested by D{\'i}az-B{\'a}nez and Mesa~\cite{diaz2001fitting} addressing the differences presented in the Related Work section~\ref{sec:relwork}.
-The algorithm $binsearchApprox(X,m)$ gets as input a random variable $X$ and some number $m$.
+The first technique we present is the $binsApprox(X,m)$ algorithm which is based on the work done by D{\'i}az-B{\'a}nez and Mesa~\cite{diaz2001fitting}.
+There are couple of significant changes between our $binsApprox(X,m)$ algorithm and the algorithm suggested by D{\'i}az-B{\'a}nez and Mesa~\shortcite{diaz2001fitting} addressing the differences presented in the Related work section.
+The algorithm $binsApprox(X,m)$ gets as input a random variable $X$ and some number $m$.
 Again, we do not mind the original representation of $X$ since we can transform it to a sorted CDF representation in $O(nlog(n))$ run-time as in line 1 which we call $X_{CDF}$.
@@
 The error is just the difference between the CDF values of every two elements in $X_{CDF}$.
-After computing the set $E$, we sort it (line 9) in order to perform a binary search in the last part of the algorithm.
+After computing the set $E$, we sort it (line 9) in order to perform a binary search.
 In lines 10-19 we perform a binary search over the set $E$, in every step of the binary search we run the $X' = dual(X,\varepsilon)$ algorithm.
@@
     \For{$i \gets 1 \textbf{ to } 2$}{
-        $l\gets 1$, $r \gets n'$, $k \gets 1$ \;
-        \Do{$k \neq k'$}{
+        $l\gets 1$, $r \gets n'$, $k \gets 1$, $k' \gets 0$ \;
+        \While{$k \neq k'$}{
                 $k' \gets k$,$k \gets \lceil (l + r)/2 \rceil$\;
-        		$X' \gets dual(X,e_k)$, $m' \gets |X'|$\;
+        		$m' \gets |dual(X,e_k)|$\;
         		\lIf{$m' < m$}{
@@
     }
-    \Return{X'}
+    \Return{$dual(X,e_k)$}
 
-	\caption{$binsearchApprox(X,m)$}   
+	\caption{$binsApprox(X,m)$}   
 	\label{alg:naive}
@@
 
-\begin{theorem}\label{the:complexityDual}
-	The $binsearchApprox(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|X|$.
+\begin{theorem}\label{the:correctnessBinsearch}
+
+    $binsApprox(X,m) \in \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
+\end{theorem}
+\begin{proof}
+Since lines 10-18 is a binary search of the smallest $e_k\in E$ such that $|dual(X,e_k)|\leq m$, we only need to prove that $E=E'=\{ d_K(X,dual(X,m)) \colon m=1,\dots,n\}$.
+To see that this is true, note that every element in $E'$ corresponds to a distance of a level set of the CDF of $dual(X,m)$ from the CDF of $X$.
+Line 6 of the algorithm adds all the distances from level sets of height zero, Line 8 adds the distances from level sets of heigt one, and Line 7 adds all the distances from all other possible level sets.
+\end{proof}
+
+\begin{theorem}\label{the:complexityBinsearch}
+	The $binsApprox(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|X|$.
 \end{theorem}
@@
 
-As a step towards $linApprox(X,m)$ algorithm, we present the algorithm $saddlebackApprox(X,m)$ that takes $O(n^2)$ run-time, this technique is very similar to $linApprox(X,m)$ algorithm.
-The algorithm $saddlebackApprox(X,m)$ gets as input a random variable $X$ and some number $m$.
-Again, we represent $X$ as a sorted CDF in $O(nlog(n))$ run-time as in line 1 and call it $X_{CDF}$.
-In line 4 We describe implicitly the sorted matrix $E$, and in lines 3-7 we perform a search over this matrix, in every step of the search we run the $X' = dual(X,\varepsilon)$ algorithm.
-If the size of $|X'|>m$ then we know that the error $e$ is too small and need to extend the search in the lower side of the matrix, if the size of $|X'|<m$ then we know that the error $e$ is too big and need to extend the search in the right side of the matrix and store this $e$ in $S$.
-We store in set $S$ all possible candidates for the correct $e$ and in line 8 we get the maximal $m$ with the minimal $e$ value.
+Towards an improved algorithm let us introduce the matrix $E=(e_{i,j})_{i,j=1}^\infty$ defined by:
+	$$e_{i,j} = \begin{cases}
+	1-c_{n+1-j}   & \text{if } j \leq n \wedge  i = n ; \\
+	c_i & \text{if } i \leq n \wedge  j = n + 1; \\
+	( c_i - c_{n+1-j})/2  & \text{if } i < n \wedge j \leq n \wedge i{+}j\geq n; \\
+	0  & \text{if }  i{+}j < n; \\
+	1  & \text{otherwise}.
+	\end{cases}$$
+Where $c_1,\dots,c_n$ are as in the first line of Algorithm~\ref{alg:naive}.
+It is easy to see that the set of values in this matrix are the elements of the set $E$ in Algorithm~\ref{alg:naive}.
+An additional useful fact is that $E$ is a sorted matrix:
+\begin{lemma}\label{the:sortedMatrix}
+	If $i\leq i'$ and $j\leq j'$ then $e_{i,j}\leq e_{i',j'}$.
+\end{lemma}
+\begin{proof}
+CDF representation of a random variable is a monotonically increasing function.
+Therefore, $\forall i,j$, $ 0\leq c_i - c_{n+1-j}\leq c_i - c_{n+1-(j+1)} $ and $ \forall i,j$, $0 \leq c_i - c_{n+1-j}\leq c_{i+1} - c_{n+1-j} $, moreover, 0 is the minimal value of $E$.
+The elements in the last row and the last column in $E$ are keeping the terms of sorted matrix.
+It suffices to compare row $n$ with row $n-1$ and show that $1-c_{n+1-j}\geq ( c_{n-1} - c_{n+1-j})/2$.
+After some manipulation we get that $2-c_{n+1-j}\geq c_{n-1}$ which is true because $0 \leq c\leq 1$.
+Next, it is suffice to compare column $n$ with only column $n+1$ and show that $c_i\geq ( c_{i} - c_{n+1-n})/2$.
+After some manipulation we get that $2c_i\geq c_{i}-c_1$ which is true because $0 \leq c_1 \leq c_i\leq 1$.
+\end{proof}
+
+The fact that this matrix is sorted allows us to use the saddleback search algorithm listed as Algorithm~\ref{alg:saddleback}.
+The algorithm starts at the top right entry of the matrix $(e_{i,j})_{i=1..n,j=1..(n+1)}$ and traverses it as follows.
+If it hits an entry $e$ such that $|dual(X,e)| \leq m$ it goes left, otherwise it goes down.
+This assures that the minimal $e$ such that $|dual(X,e)| \leq m$ is visited after at most $n+1$ steps.
+Data is collected along the traversal and the optimal random variable is found by brute-force.
 
@@
 	Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i=Pr(X \leq x_i)$ and $\supp(X)=\{x_1 < \cdots < x_n\}$.\;
-    $i \gets 1$, $j \gets \lceil n/2 \rceil$, $S \gets \emptyset$\;
+    $i \gets 1$, $j \gets n$+1, $S \gets \emptyset$\;
 
-	\While{$i < \lfloor n/2 \rfloor + 1 \wedge j \geq 2$}
+	\While{$i < n \wedge j \geq 1$}
 	{	
-% 		$ e \gets \begin{cases}
-% 			c_j   & \text{if } i=\lfloor n/2 \rfloor+1; \\
-% 			1-c_i & \text{if } j=\lceil n/2 \rceil; \\
-% 			(c_{n+1-j} {-} c_i)/2  & \text{otherwise}
-% 		\end{cases}$\;
-
-		$X' \gets dual(X,e_{i,j})$, $m' \gets |X'|$\;
+		$m' \gets |dual(X,e_{i,j})|$\;
 
@@
 
-	\caption{$saddlebackApprox(X,m)$}   
+	\caption{$sdlbkApprox(X,m)$}   
 	\label{alg:saddleback}
 \end{algorithm}
+
+\begin{theorem}\label{the:correctnessSaddleback}
+
+    $sdlbkApprox(X,m) {\in} \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
+\end{theorem}
+\begin{proof}
+The algorithm traverses all the frontier between those $e$s that satisfy $|dual(X,e)| \leq m$ and those that do not satisfy it.
+Since all the entries that satisfy the condition are recorded in $S$ and considered in the brute-force phase in line 7, the minimal satisfying $e$ is found.
+\end{proof}
+
+\begin{theorem}\label{the:complexitySaddleback}
+	The $sdlbkApprox(X,m)$ algorithm runs in time $O(n^2)$, using $O(n)$ memory where $n=|X|$.
+\end{theorem}
+\begin{proof}
+	At each step of the loop in lines 3-6, either $j$ decreases or $i$ increases, thus the loop can be executed at most $2n$ times.
+Since we execute $dual$ once ion a loop round, the total time complexity is $O(n^2)$.
+Storing visited states in $S$ on line 6 requires  $O(n)$ memory.
+\end{proof}
+
+The problem with the saddleback algorithm is that it needs to run $dual$ at every step so it has a quadratic time complexity.
+Since we cannot find the required entry of the matrix in less than $n$ steps, we can only reduce the complexity by proposing an algorithm that does not executes $dual$ in all the steps, only in $\log(n)$ of them.
+Such an algorithm, based on Section~2.1 in~\cite{Fournier2011}, is listed as Algorithm~\ref{alg:linear}.
+The algorithm maintains a set $S$ of sub-matrices.
+At each round of its execution, each sub-matrix is split to four and then about three quarters of the matrix are discarded.
+At the end, at most four scalar matrices remain containing the index of the entry we seek.
 
@@
 
-		$w \gets 2^{\lceil \log_2(n/2) \rceil}$,
-		$h \gets 2^{\lceil \log_2(n/2+1) \rceil}$ \;
-
-		$S \gets  \{ ((1, 1),(w,h)) \}$, $S' \gets \emptyset$\;
+		$S \gets  \{ ((1, 1),(n,n+1)) \}$, $S' \gets \emptyset$\;
 
@@
 			\For{$ e \in \{ e^-,e^+ \}$} {
-				$X' \gets dual(X,e)$, $m' \gets |X'|$\;
+				$m' \gets |dual(X,e)|$\;
 
@@
 	\end{algorithm}
+{
+	\begin{algorithm}
+		\DontPrintSemicolon
 
-	\begin{procedure}
-		\DontPrintSemicolon
 		$j^- \gets \lfloor (j_1+j_2)/2 \rfloor$,
@@
 
-		\caption{{$split(((i_1,j_1),(i_2,j_2)))$}()}
+		\caption{$split(((i_1,j_1),(i_2,j_2)))$}
 		\label{proc:split}
-	\end{procedure}
+	\end{algorithm}
+}
 
-	Let 
-	$$e_{i,j} = \begin{cases}
-	c_j   & \text{if } j \leq n \wedge  i > n; \\
-	1-c_i & \text{if } i \leq n \wedge  j \geq n; \\
-	%(c_{n+1-j} {-} c_i)/2  & \text{if } i \leq n \wedge i{+}j\leq n{+}1; \\
+\begin{theorem}\label{the:correctnessLinear}
 
-	%(c_{n+1-i} {-} c_i)/2  & \text{if } j \leq n \wedge i{+}j\leq n; \\
+    $linApprox(X,m) {\in} \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
+\end{theorem}
+\begin{proof}
+In line~10 we only discard sub-matrices whose minimal entry (at the top left) is larger than an entry that we prefer.
+In line~12 we only discard sub-matrices whose maximal entry (at the bottom right) is smaller or equal to an entry that does not meet our condition.
+\end{proof}
 
-	(c_{p-1 +i} {-} c_{p+1-j})/2  & \text{if } i \leq n \wedge i{+}j\leq n{+}1; \\
-
-	(c_{p-1 +i} {-} c_{p+1-i})/2  & \text{if } i \leq n \wedge i{+}j\leq n{+}1; \\
-
-	\infty  & \text{otherwise}.
-	\end{cases}$$
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{An algorithm for optimal approximation}\label{sec:alg}
-% In the scope of this section, let $X$ be a given random variable with a finite support of size $n$, and let  $0<m\leq n$ be a given complexity bound.
-The section evolves by developing notations and by collecting facts towards an algorithm for finding an optimal $m$-approximation of $X$.
-
-% The first useful fact is that it is enough to limit our search to approximations $X'$s such that $\support(X') \subseteq \support(X)$:
-
-% \begin{lemma}\label{lem:supContained}
-% 	For every random variable $X''$ there is a random variable $X'$ such that $\support(X') \subseteq \support(X)$ and $d_{K}(X,X')\leq d_{K}(X,X'')$.
-% \end{lemma}
-
-% \begin{proof}
-% 	Let $\{x_1 <\cdots<x_n\} = \support(X)$, and let $x_0 = -\infty, x_{n+1}=\infty$. Consider the random variable $X'$ whose probability mass function is
-% 	$f_{X'}(x_i) = P(x_{i-1} < X'' \leq x_i)$ for $i=1,\dots,n-1$,  $f_{X'}(x_n) = P(x_{n-1} < X'')$, and $F_{X'}(x)=0$ if $x\notin \support(X)$.
-Since we only "shifted" the probability mass of $X''$ to the support of $X$, we have that $f_{X'}$ is a probability mass function and therefore $X'$ is well defined.
-% 	By construction, $|F_{X}(x_i)-F_{X'}(x_i)| = |F_{X}(x_i)-F_{X''}(x_i)|$ for every  $0 <  i < n$. For $i=n$ we have $|F_{X}(x_n)-F_{X'}(x_n)| = |1-1|=0$.
-% 	Since $|F_{X}(x)-F_{X'}(x)| = |F_{X}(x_i)-F_{X'}(x_i)|$ for every  $0\leq   i  \leq  n$  and $x_i<x<x_{i+1}$, we have that $d_K(X,X')=max_{i}|F_{X}(x_i)-F_{X'}(x_i)|\leq max_{i}|F_{X}(x_i)-F_{X''}(x_i)|\leq d_K(X,X'')$.
-% \end{proof}
-
-% %Next, note that every random variable $X''$ with support of size at most $m$ that is contained in $\support(X)$ can be described by first setting the (at most $m$) elements of the support of $X''$; then for every such option, determine $X''$ by setting probability values for the elements in the chosen support of $X'$, and setting $0$ for rest of the elements.
-
-% For a set $S\subseteq \support(X)$, let $\mathbb{X}_S$ denote the set of random variables whose supports are contained in $S$.
-In Step 1 below, we identify a random variable in $\mathbb{X}_S$  that minimizes the Kolmogorov distance from $X$.
-We denote the Kolmogorov distance between this variable and $X$ by $\varepsilon(X,S)$.
-Then, in Step 2, we show how to efficiently find a set $S \subseteq \support(X)$ whose size is smaller or equal to $m$ that minimizes $\varepsilon(X,S)$.
-Then, in Step 3, an optimal $m$-approximation is constructed by taking a minimal approximation in $\mathbb{X}_S$ where $S$ is the set of size $m$ that that minimizes $\varepsilon(X,S)$.
-
-% \subsection*{Step 1: Finding an $X'$ in $\mathbb{X}_S$ that minimizes $d_K(X,X')$}
-
-% We first fix a set $S\subseteq \support(X)$ and among all the random variables in $\mathbb{X}_S$ find one with a minimal distance from $X$.
-Denote the elements of $S$ in increasing order by $S=\{x_1<\dots<x_m\}$ and let $x_0=-\infty$ and $x_{m+1}=\infty$.
-Consider the following weight function:
-
-% \begin{definition}\label{def:weight} For $0\leq i \leq m$ let
-% 	\[
-% 	w(x_i,x_{i+1})=
-% 	\begin{cases}
-% 	P(x_i < X < x_{i+1}) & \text{if $i=0$ or $i = m$;} \\
-% 	P(x_i < X < x_{i+1})/2 & \text{otherwise.} \\	
-% 	\end{cases}
-% 	\]
-% \end{definition}
-% For each $1 <  i \leq m$ let $\hat x_i$ be the maximal element of $\support(X)$ that is smaller than $x_i$. 
-% Note that, for $1\leq i \leq m$, $P(x_i < X < x_{i+1}) = F_X(\hat x_{i+1}) - F_X(x_i)$, a fact that we will use throughout this section.
-
-% \begin{definition}\label{def:error}
-% Let $\varepsilon(X,S) = \max\limits_{i=0,\dots,m} w(x_{i}, x_{i+1})$.
-% \end{definition}
-
-% We first show that $\varepsilon(X,S)$ is a lower bound for the distance between random variable in $\mathbb{X}_S$ and $X$.
-Then, we present a random variable $X'\in \mathbb{X}_S$ such that $d_K(X,X')=\varepsilon(X,S)$.
-It then follows that $X'$ is closets to $X$ in $\mathbb{X}_S$.
-
-% %The intuition behind choosing these specific weights and $\varepsilon(X,S)$ being a lower bound is as follows.
-Since for every $X'\in\mathbb{X}_S$ the probability mass of $X'$ for the elements not in $S$ are set to $0$, we have that $F_{X'}(\hat x_{i+1})=F_{X'}(x_i)$.
-Therefore the distance between $X'$ and $X$ at points $x_i$ and $\hat x_{i+1}$ that we have to take into additional account is increased by $F_X(\hat x_{i+1})-F_X(x_i) = P(x_i < X < x_{i+1})$.
-
-% %Formally we have the following.
-
-% \begin{proposition}\label{prop:minimal}
-% 	If $X'\in\mathbb{X}_S$ then $d_K(X,X') \geq \varepsilon(X,S)$.
-% \end{proposition}
-
-% \begin{proof}
-
-% 	By definition, for each $0\leq i\leq m$, $d_K(X,X') \geq \max \{|F_X(\hat x_{i+1}) - F_{X'}(\hat x_{i+1})|,|F_X(x_i) - F_{X'}(x_i)| \}$.
-Note that $F_{X'}(\hat x_{i+1})=F_{X'}(x_i)$ since the probability of  elements not in $S$ is  $0$.
-
-% 	If $i=0$, that is $x_i=-\infty$, we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ and therefore $d_K(X,X') \geq |F_X(\hat x_{i+1})| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1})= w(x_i,x_{i+1})$.
-
-% 	If $i =m$, that is $x_{i+1}=\infty$, we have that $F_X(\hat x_{i+1})=F_{X'}(\hat x_{i+1})=F_{X'}(x_i)=1$. 
-% 	and therefore $d_K(X,X') \geq |1-F_X(\hat x_i)| = |F_X(\hat x_{i+1}) - F_{X}(x_i)| =  P(x_i < X < x_{i+1}) = w(x_i,x_{i+1})$.
-
-% 	%  we have that $F_X(x_i)=F_{X'}(x_i)=F_{X'}(\hat x_{i+1})=0$ 
-% 	% 
-% 	% 
-% 	% 
-% 	% We break the proof for the closed intervals where each support variable $x_i$ is a proper number, and for the open intervals where a support variable is either $-\infty$ or $\infty$.
-
-% 	Otherwise for every $1\leq i< m$,  we use the fact that $max\{|a|,|b|\} \geq |a-b|/2$ for every $a,b\in\mathbb{R}$, to deduce that $d_K(X,X') \geq 1/2| F_X(\hat x_{i+1}) - F_X(x_i) + F_{X'}(x_i) -F_{X'}(\hat x_{i+1})|$.
-So $d_K(X,X') \geq 1/2| F_X(\hat x_{i+1}) - F_X(x_i) | =P(x_1 < X < x_2)/2 = w(x_i,x_{i+1})$.
-
-% Since $d_K(X,X') {\geq}  w(x_i,x_{i+1})$ for any $0{\leq} i{\leq} m$, the proof follows by the definition of $\varepsilon(X,S)$.
-% \end{proof}
-
-% We next describe a random variable $X'\in\mathbb{X}_S$ in a distance of $\varepsilon(X,S)$ from $X$ by its probability mass function:
-
-% \begin{definition}\label{def:construction}
-% 	Let $f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for $i=1,\dots,m$ and $f_{X'}(x)=0$ for $x \notin S$.
-% \end{definition}
-
-% We first show that $X'$ is a properly defined random variable:
-
-% \begin{lemma}
-% 	$f_{X'}$ is a probability mass function. 
-% \end{lemma}
-
-% \begin{proof}
-% 	By definition $f_{X'}(x_{i})\geq 0$ for every $i$. To see that $\sum_i f_{X'}(x_{i}) =1$, 
-% 	we have $\sum_i f_{X'}(x_{i}) = \sum_i (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) = 	
-% 	\sum _{x_i\in S} f_{X}(x_i)) + w(x_0,x_1)+ \sum_{0 < i < m} 2 w(x_i,x_{i+1}) + w(x_m,x_{m+1}) = 
-% 	\sum _{x_i\in S} P(X{=}x_i) + P(x_0 {<} X {<} x_1)+ \sum_{0 < i < m} P(x_i < X < x_{i+1}) +P(x_m < X < x_{m+1}) = 1$ since this is the entire support of $X$.	
-% \end{proof}
-
-% Note that, given $S$, $X'$ can be constructed in time linear in the size of the support of $X$.
-% Its main property, of course, is that the distance between the cumulative distribution functions of $X$ and of $X'$ are bounded by $w(x_i,x_{i+1})$, as follows:
-% \begin{lemma}\label{lem:balance}
-% 	Let $x\in\support(X)$ and $0\leq i\leq m$ be such that $x_i\leq x \leq x_{i+1}$ then 
-%     \[
-%     -w(x_i,x_{i+1})\leq F_X(x)-F_{X'}(x)\leq  w(x_i,x_{i+1}).
-%     \]
-%     \end{lemma}
-
-% \begin{proof}	
-% 	By induction on $i$.	First see that $F_{X'}(x) = 0$  for every $x_0<x < x_1$ and therefore $F_X(x)-F_{X'}(x) = F_X(x)-0 \leq F_X(\hat x_1)= F_X(\hat x_1)- F_X(x_0) = w(x_0,x_1)$.
-For $ x = x_1$ we have $F_X(x_1)-F_{X'}(x_1)=  F_X(\hat x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1) =
-% 	w(x_0,x_1) +f_{X}(x_1) - (w(x_0,x_1) + w(x_1,x_2) + f_{X}(x_1)) = -w(x_1,x_2)$.
-
-% 	Next assume that $F_X(\hat x_i)-F_{X'}(\hat x_i) = w(x_{i-1},x_i)$.
-% 	Then $F_X(x_i)-F_{X'}(x_i) =  F_X(\hat x_i) +f_{X}(x_i) - (w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)) =  w(x_{i-1},x_i) +f_{X}(x_{i}) - (w(x_{i-1},x_i) + w(x_{i},x_{i+1}) + f_{X}(x_{i})) = -w(x_{i},x_{i+1})$.
-
-% 	As before we have that for all $x_i< x< x_{i+1}$, we have $F_X(x)-F_{X'}(x) = F_X(x)-F_{X'}(\hat x_{i+1}) \leq  F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1})$.
-Then $F_X(\hat x_{i+1})-F_{X'}(\hat x_{i+1}) = (F_X(x_i)+ P(x_i < x <x_{i+1})) - F_{X'}(x_i) = -w(x_{i},x_{i+1}) + 2w(x_{i},x_{i+1}) = w(x_{i},x_{i+1}) $.
-
-% 	Finally, for $x_m\leq x \leq x_{m+1}$ we have that $F_{X'}(x_m)=1$ therefore $F_X(x_m)-F_{X'}(x_m) = (1- P(x_m<X < x_{m+1})) - 1 =  P(x_m<X < x_{m+1}) = w(x_m,x_{m+1})$, and for every $x_m<x<x_{m+1}$ we have $F_X(x) - F_{X'}(x) < (1- P(x_m<X < x_{m+1})) - 1 <  - P(x_m<X < x_{m+1}))  = -w(x_m,x_{m+1})$ as required.
-% \end{proof}
-
-% From Lemma \ref{lem:balance}, by the definition of $\varepsilon(X,S)$, we then have:
-% \begin{corollary} \label{col:Xprime}
-% 	$d_K(X,X') = \varepsilon(X,S)$.
-% \end{corollary}
-% From Proposition~\ref{prop:minimal} we also have:
-% \begin{corollary} \label{col:Xprimeopt}
-% 	$\varepsilon(X,S)$ is the Kolmogorov distance between $X$ and the variables closest to it in $\mathbb{X}_S$.
-% \end{corollary}
-
-% \subsection*{Step 2: Finding a set $S$ that minimizes $\varepsilon(X,S)$}
-
-% We proceed to finding a set $S$ of size $m$ that minimizes $\varepsilon(X,S)$.
-To obtain that we use a graph search approach inspired by~\cite{chakravarty1982partitioning}.
-We construct a directed graph with a source and a target in which each source-to-target path of length smaller or equal to $m$ corresponds to a possible support set of the same size, and the weights along that path correspond to the weight as defined in Definition~\ref{def:weight}.
-Thus the problem of finding an $S$ of size $m$ that minimizes $\varepsilon(X,S)$ is reduced to the problem of finding a source-to-target path $\vec{p}$ of length smaller or equal to $m$ in that graph such that the maximal weight of an edge in $\vec{p}$ is minimal among all other such maximal edges in all other such paths.
-
-% More specifically, the vertices of the graph are $V=\support(X) \cup \{-\infty,\infty\}$ and the edges, $E$, are all the pairs $(x_1,x_2) \in V^2$ such that $x_1 < x_2$. The weight 
-% of each edge is as specified in Definition~\ref{def:weight}.
-Note that there is a one-to-one correspondence between a set $S \subseteq \support(X)$ of size $m$, and an $-\infty$-to-$\infty$ path $\vec{p}_S$ in $G$, obtained by removing the $-\infty$ and $\infty$ from the path in one direction and by adding these elements and sorting in the other direction.
-% With this correspondence, the maximal weight of an edge on $\vec{p}_S$ is $\varepsilon(X,S)$.
-We denote this maximal weight of an edge  by $w(\vec{p}_S)$, and denote the set of all acyclic $-\infty$-to-$\infty$ paths in $G$ with at most $m$ edges by $paths_m(G, -\infty, \infty)$.
-Thus, the problem of finding the set $S$ with the minimal  $\varepsilon(X,S)$ is now reduced to the problem of finding a path $\vec{p}\in paths_m(G, -\infty, \infty)$ such that $w(\vec{p})$ is minimal among all $\{w(\vec{p'}) \colon \vec{p'}\in paths_m(G, -\infty, \infty)\}$.
-% This problem can be solved by a variant of the Bellman-Ford algorithm and by the algorithm described in~\cite{guerin2002computing} that performs better in some cases.
-
-% %\begin{corollary}\label{cor:Bellman}
-% %$BellmanFord(G,m)$ returns a path $\vec{p}\in paths_m(G, s, t)$ such that $w(\vec{p})$ is minimal among all $\{w(\vec{p'}) | \vec{p'}\in paths_m(G, s, t)\}$.
-% %\end{corollary}
-
-% \subsection*{Step 3: Constructing the overall algorithm}
-
-% We combine Step 1 and Step 2 in the following algorithm called $\KlmApprox$ (Algorithm~\ref{alg:optapprox}) that follows naturally from the two steps.
-Given $X$ and $\support(X)$ we add $x_0=\infty,x_{n+1}=-\infty$ and construct the graph (line 2) as described  in Step 2 above.
-Then we execute a variant of the Bellman-Ford algorithm on $G$ for $m$ iterations, or the algorithm proposed in~\cite{guerin2002computing}, to obtain a path $\vec{p}$ (line 2).
-Finally, we use Definition~\ref{def:construction} to construct $X'$ from $\vec{p}$ (line 3).
-
-% \begin{algorithm}\label{alg:optapprox}
-% 	%\setstretch{1.5}
-% 	\DontPrintSemicolon
-% 	Construct a weighted graph $G=(V,E)$ where $V=\support(X) \cup \{-\infty,\infty\}$, $E=\{(x_1,x_2) \in V^2\colon x_1 < x_2 \}$, and the weights are as in Definition~\ref{def:weight}.\; \vspace{0.2cm}
-
-% 	Find a path $\vec{p}=(x_0,\dots,x_{m+1})\in paths_m(G, -\infty, \infty)\}$ such that $w(\vec{p}) = \min \{w(\vec{p}) \colon \vec{p}\in paths_m(G, -\infty, \infty)\}$.   \; 	\vspace{0.2cm}
-
-% 	Return a random variable whose probability mass function is 
-% 		$f_{X'}(x_{i}) = w(x_{i-1},x_i) + w(x_i,x_{i+1}) + f_{X}(x_i)$ for all $i=1,\dots,m$ and zero otherwise. \;
-
-% 	\caption{$\KlmApprox (X, m)$}  
-% 	\label{alg:sequence}
-% \end{algorithm}
-
-% \begin{theorem}\label{the:algo}
-% 	$\KlmApprox$ returns an $m$-optimal-approximation of $X$.
-% \end{theorem}
-% \begin{proof}
-% By the construction of $G$ we get that the path $\vec{p}$ obtained in line 2 of  $\KlmApprox$ describes a set $S$ of support of size at most $m$ for which $\varepsilon(S,X)$ is minimal.
-Then from Definition \ref{def:construction} and Corollary \ref{col:Xprime} we construct $X'$ in lines 3 of 	$\KlmApprox$ such that $d_K(X,X') = \varepsilon(X,S)$.
-Therefore $X'$ is closets to $X$ among all random variables with support contained in $\support(X)$.
-From Lemma \ref{lem:supContained} we then get that $X'$ is an $m$-optimal-approximation of $X$.
-% \end{proof}
-
-% The memory and time  complexities of $\KlmApprox$ are as follows.
-
-% \begin{theorem}\label{the:complexity}
-% 	The $\KlmApprox(X,m)$ algorithm runs in time $O(n^2m)$, using $O(n^2)$ memory where $n=|X|$.
-% \end{theorem}
-% \begin{proof}
-% 	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory.
-Computing the shortest path can be achieved, for example, by the algorithm described in~\cite{guerin2002computing} in time $O(n^2 m)$ and no additional memory allocation.
-% \end{proof}
-% %\begin{proof}
-% %	Constructing the graph $G$ as described in Step 2 takes $O(n^2)$ time and memory. The number of edges in $G$ is $O(|E|)=O(n^2)$, for every edge the weight is at most the sum of all
-% %probabilities between the source node $s$ and the target node $t$, which can be calculated efficiently by aggregating the weights of already calculated edges. 
-% %	The construction is also the only stage that requires memory allocation, specifically $O(|E|+|V|)=O(n^2)$.
-% %	Next using the Bellman-Ford algorithm on $G$ for $m$ iterations   takes $O(m(|E|+|V|))\approx O(mn^2)$. [[DF: cite Corman or some algorithms book]]. 
-% %	Finally deriving the new random variable $X'$ from the computed path $\vec{p}$ takes $O(m)$ time: For every node $x_i$ in $\vec{p}$ (at most $m$ nodes), use the already calculated weights to find the probability mass function $f_{X'}(x_i)$.
-% %	To conclude, the time complexity  of $\KlmApprox(X,m)$ is $O(n^2+mn^2+m)=O(mn^2)$ and memory complexity is $O(E+V)=O(n^2)$.
-% %\end{proof}
+\begin{theorem}\label{the:complexityLinear}
+	The $linApprox(X,m)$ algorithm runs in time $O(n \log(n))$, using $O(1)$ memory where $n=|X|$.
+\end{theorem}
+\begin{proof}
+The dimension of each matrix is halved in each round, thus the loop is executed $O(\log(n))$ rounds.
+Since $dual$ is called one in each round and a finite number of times at the end, the time complexity is $O(n \log(n))$.
+\end{proof}
 
@@
 Previous work such as the work of Cohen et al.
-in ~\cite{cohen2015estimating,CohenGW18} handle this reduction using weaker or sub-optimal notion of approximation than ours, as discussed in Section~\ref{sec:relwork}.
+in ~\shortcite{cohen2015estimating,CohenGW18} handle this reduction using weaker or sub-optimal notion of approximation than ours, as discussed in Section~\ref{sec:relwork}.
 
@@
 In light of this, we tested the accuracy of the repetitive-$\KlmApprox$ to see how it performs against the tools of~\cite{cohen2015estimating,CohenGW18} using their benchmarks.
-These benchmarks are taken from the area of task trees with deadlines, a sub area of the well-established Hierarchical planning~\cite{thomas1988hierarchical,alford2016hierarchical,xiao2017hierarchical}.
+These benchmarks are taken from the area of task trees with deadlines, a sub area of the well-established hierarchical planning~\cite{thomas1988hierarchical,alford2016hierarchical,xiao2017hierarchical}.
 
@@
 
-We estimated the probability for meeting deadlines in plans, as described in~~\cite{cohen2015estimating,CohenGW18}, and experimented with four different methods of approximation.
+We estimated the probability for meeting deadlines in plans, as described in Cohen et al.~\shortcite{cohen2015estimating,CohenGW18}, and experimented with four different methods of approximation.
 The first two, $\OptTrim$~\cite{CohenGW18} and the $\Trim$~\cite{cohen2015estimating}, are taken from the repository provided by the authors and are designed for achieving only a one-sided Kolmogorov approximation - a  weaker notion of approximation then the Kolmogorov approximation analyzed in this work.
@@
 	\renewcommand{\arraystretch}{1.3}
-	\begin{tabular}{|p{1.05cm}|p{0.25cm}|p{0.93cm}|p{0.93cm}|p{1.05cm}|p{0.75cm}|p{0.75cm}|}
+	\begin{tabular}{|p{1.05cm}|p{0.2cm}|p{0.98cm}|p{0.93cm}|p{1.05cm}|p{0.75cm}|p{0.75cm}|}
 		\hline
@@
 Similarly to accuracy and error computation, we also conducted empirical evaluation to examine the run-time in practice of the discussed algorithms.
-Figure~\ref{fig:runtime} presents a comparison of the run-time performances of an exact computation and approximated computations with $\KlmApprox$ and $\Trim$ as operators.
-We examined three versions of $\KlmApprox$ each of which with different run-time,  The computation is a summation of a sequence of random variables with support size of $m{=}10$, where the number $n$ of variables varies from 6 to 19.
-In this experiment, we executed the $\KlmApprox$ operator with $m{=}10$ after performing each convolution between two random variables, in order to maintain a support size of 10 in all intermediate computations.
+Figure~\ref{fig:runtime} presents a comparison of the run-time performances of an exact computation and approximated computations with $\KlmApprox$, $\BinsApprox$, $\OptTrim$ and $\Trim$ as operators.
+We examined four versions of approximation each of which with different run-time but only $\KlmApprox$ and $\BinsApprox$ produce optimal Kolmogorov approximation.
+The computation is a summation of a sequence of random variables with support size of $m{=}10$, where the number $n$ of variables varies from 6 to 19.
+In this experiment, we executed the approximation algorithm with $m{=}10$ after performing each convolution between two random variables, in order to maintain a support size of 10 in all intermediate computations.
 Equivalently, we executed the $\Trim$ operator with $\varepsilon=0.1$.
@@
 In fact, in the experiment with $N{=}20$, the exact computation ran out of memory.
-These results illuminate the advantage of the proposed $\KlmApprox$ algorithm that balances between solution quality and run-time performance -- while there exist other, faster, methods (e.g., $\Trim$), $\KlmApprox$ provides high-quality solutions in reasonable (polynomial) time, which is especially important when an exact computation is not feasible, due to time or memory.
+These results illuminate the advantage of the proposed $\KlmApprox$ algorithm that balances between solution quality and run-time performance -- while there exist other, faster, methods (e.g., $\Trim$), $\KlmApprox$ provides high-quality solutions in $O(n log(n))$ time, which is especially important when an exact computation is not feasible, due to time or memory.
+In general, Figure~\ref{fig:runtime} is consistent with the theory and show a good fit to the complexity analysis presented in Section~\ref{sec:algEfficient}.
 
 \begin{figure}[htb]
-    \label{fig:runtime}
 	\scriptsize	
@@
 	};
-	\addlegendentry{$n^2log(n) \KlmApprox$}
+	\addlegendentry{$n^2log(n) \BinsApprox$}
 
@@
 	\end{tikzpicture}
-	\caption{Run-time of a long computation with $\OptTrim$, with $\Trim$, and without any trimming (exact computation).}
+	\caption{Run-time of a long computation with $\KlmApprox$, $\BinsApprox$, $\OptTrim$, $\Trim$, and without any trimming (exact computation).}
 	\label{fig:runtime}
@@
 
-% \paragraph{Comparison to Linear Programming.}
-% We also compared the run-time of $\KlmApprox$ with a linear programing (LP) algorithm that also guarantees optimality, as described and discussed for example in~\cite{pavlikov2016cvar}.
-% For that, we used the ``Minimize'' function of Wolfram Mathematica as a  state-of-the-art implementation of linear programing, encoding the problem by the LP problem $\min_{\alpha \in \mathbb{R}^n} \| x - \alpha\|_\infty$ subject to $\|\alpha\|_0 \leq m$ and $\| \alpha \|_1 =1$.
-% The run-time comparison results were clear and persuasive: $\KlmApprox$ significantly outperforms the LP algorithm.
+\paragraph{Comparison to Linear Programming.}
+We also compared the run-time of $\KlmApprox$ with a linear programming (LP) algorithm that also guarantees optimality, as described and discussed for example in~\cite{pavlikov2016cvar}.
+For that, we used the ``Minimize'' function of Wolfram Mathematica as a  state-of-the-art implementation of linear programming, encoding the problem by the LP problem $\min_{\alpha \in \mathbb{R}^n} \| x - \alpha\|_\infty$ subject to $\|\alpha\|_0 \leq m$ and $\| \alpha \|_1 =1$.
+The run-time comparison results were clear and persuasive: $\KlmApprox$ significantly outperforms the LP algorithm.
 For a random variable with support size $n=10$ and $m=5$, the LP algorithm run-time was $850$ seconds, where the $\KlmApprox$ algorithm run-time was less than a tenth of a second.
 For $n=100$ and $m=5$, the $\KlmApprox$ algorithm run-time was 0.14 seconds and the LP algorithm took more than a day.
-% Since it is not trivial to formally analyze the run-time of the LP algorithm, we conclude by the reported experiment that in this case the LP algorithm might not be as efficient as $\KlmApprox$ algorithm whose complexity is proven to be polynomial in Theorem~\ref{the:complexity}.
+Since it is not trivial to formally analyze the run-time of the LP algorithm, we conclude by the reported experiment that in this case the LP algorithm might not be as efficient as $\KlmApprox$ algorithm.
 
@@
 
-We developed an algorithm for computing optimal approximations of random variables where the approximation quality is measured by the Kolmogorov distance.
-As demonstrated in the experiments, our algorithm improves on the approach of Cohen et al.~\cite{cohen2015estimating} and~\cite{CohenGW18} in that it finds an optimal two sided Kolmogorov approximation, and not just one sided.
-Beyond the Kolmogorov measure studied here we believe that similar approaches may apply also to total variation, to the Wasserstein distance, and to other measures of approximations.
+We developed an efficient algorithm for computing optimal approximations of random variables where the approximation quality is measured by the Kolmogorov distance.
+As demonstrated in the experiments, our algorithm improves on the approach of Cohen et al.~\shortcite{cohen2015estimating} and~\shortcite{CohenGW18} in that it finds an optimal two sided Kolmogorov approximation, and not just one sided.
+Beyond the Kolmogorov measure studied here, we believe that similar approaches may apply also to total variation, to the Wasserstein distance, and to other measures of approximations.
 Another direction for future work is extensions to tables that represent other objects, not necessarily random variables.

### 2018-11-12 rebuttal.txt
Updates from ShareLaTeX

We thank the reviewers for the constructive and deep feedback. See the responses to all specific issues below. We will also fix the small typos identified by the reviewers.

Reviewer #1:
-----------------
Thank you for the corrections. We will incorporate them in the final version.

Regarding "dual(X,m) -> dual(X, e_m)" and "(m', e) -> (m', e_{i,j}) ". You are correct.

Regarding Algorithm 3, to make the algorithm more readable, we will move the update to a separate line and execute it iff $m' \geq m$. This does not change the complexity and only adds candidates to S (does not remove any candidate from it) thus it does not break the correctness of the algorithm.

Reviewer #2:
-----------------
Regarding interest to the broader AI community:  compression of random variables and of other objects used in AI, such as neural networks, is a broad problem with many applications. We focused on a specific problem in this paper in order to provide full details. We plan to continue with other results towards a complete theory and practices in this field.

In page 7, we will change "random variables of 100" to "random variables with $n=100$". Thank you.

We will insert full bibliographic details as proposed.

Reviewer #3:
-----------------
Cohen et al. (2018) is the state of the art to the best of our knowledge. There is also a recent draft on the arxiv that presents an attempt to tackle the optimal approximation problem that we deal with in this paper by extending the algorithm of Cohen et al. (2018). We compared the results of this algorithm with ours and made sure that they produce random variables with equal approximation quality (same Kolmogorov distance from the original random variable). However, the draft on the archive presents a quadratic algorithm while ours complexity is of O(n logn). We also tested that our algorithm runs faster in practice.

Reviewer #4:
-----------------
Indeed, we agree with the reviewer that this work can be seen as a compression algorithm. We believe our work is relevant to a wider audience and we plan to extend it to compression by other metrics and of other objects.

The following are answers to the "Detailed Comments":

- We will add to Section 1 a forward reference to the linear program described in Section 2. Liat, sec 1

- We have some preliminary work on possible extensions of our work to other distances. We believe that we can find optimal approximations relative to these distances in polynomial time, but not in linear time. We didn't add these to the paper because we don't want to publish half-baked results. We plan to add them to a journal version of the paper in the near future.

- We verified that the <= is correct in line 6 of Algorithm 1. The idea is that we extend the interval [b,e] until $c_{e+1}-c_b$ it is larger than $2\varepsilon$ and $c_{e}-c_b$ is smaller or equal to it.

- We agree that the proof of Algorithm 1 can be more detailed. We will elaborate in the final version. Specifically, we will explain that we are not only showing that the solution found is locally optimum, we are showing that it is a *global* optimum. The proof goes by showing that *any* change to the solution will either give a inferior or same approximation distance.

- We will add an example of execution of Algorithm 1 to explain the rationale.

- We will clarify in the proof of Algorithm 2 that the fact that the optimal error is one of the distances between any two steps of the CDFs is because we seek a random variable whose support is included in the original one. Thank you for pointing out this leap in the proof, we believe that the clarifications will improve the final version.

- We will note in the proof of Algorithm 2 the fact that the distance is monotonic with the support size. Thank you for this advice, we believe that it will significantly help future readers.

- Regarding the question "Why do you need k and k' in algorithm 2 and not just l and r": k' is needed for the termination condition. We tried to write the algorithm without m' and k and we felt that it comes too complex to read.

- Regarding the question about the second call to the dichotomy search: If m is not in the set of optimal solutions we may end up with a variable that is not optimal because it can be improved by using m'' such that $m < m'' < m'$. This issue is solved by a direct application of the dual algorithm with the computed $e_k$. We will elaborate.

- We will add some background and explanation on the use of the sorted matrix.

- Regarding 850s that the linear programming solver consumed: In the specific experiment discussed in this context the algorithms (LP and our algorithm) are both implemented in Wolfram Mathematica. Therefore, the run-time comparison is fair. We will report on the number of variables and constraints. Unfortunately, we don't have hand-on experience with cplex or gurobi. Note that the 850s is because this is not a pure continuous LP problem since it involves counting zeroes and optimizing for the maximum norm.

### 2018-11-12 Kolmogorov_Approx.tex
Updates from ShareLaTeX

@@
 \setlength{\pdfpageheight}{11in}  %Required
+\usepackage{float}
 
-\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=100]{microtype}
+\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=40]{microtype}
+
+\makeatletter
+
+% this creates a custom and simpler ruled box style
+\newcommand\floatc@simplerule[2]{{\@fs@cfont #1 #2}\par}
+\newcommand\fs@simplerule{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@simplerule
+  \def\@fs@pre{\hrule height.8pt depth0pt \kern4pt}%
+  \def\@fs@post{\kern4pt\hrule height.8pt depth0pt \kern4pt \relax}%
+  \def\@fs@mid{\kern8pt}%
+  \let\@fs@iftopcapt\iftrue}
+
+% this code block defines the new and custom floatbox float environment
+\floatstyle{simplerule}
+\newfloat{exmpl}{thp}{lob}[section]
+\floatname{exmpl}{Example}
 
@@
   \pdfinfo{
-	/Title (Optimal Approximation of Discrete Random Variables for Estimation of Probabilities of Missing Deadlines
+	/Title (Efficient Optimal Approximation of Discrete Random Variables for Estimation of Probabilities of Missing Deadlines
 	)
-	/Author ()}
-\setcounter{secnumdepth}{0}
+	/Author (Liat Cohen, Gera Weiss)}
 
+\setcounter{secnumdepth}{1}  
+\pgfplotsset{compat=1.5}
 \begin{document}
 
-\title{Optimal Approximation of Discrete Random Variables \\ for Estimation of Probabilities of Missing Deadlines}
-\author{}
+\title{Efficient Optimal Approximation of Discrete Random Variables \\ for Estimation of Probabilities of Missing Deadlines}
+\author{Liat Cohen \and Gera Weiss\\
+    Department of Computer Science\\
+		Ben-Gurion University of the Negev, Beer-Sheva 84105, Israel\\
+		\{liati,geraw\}@cs.bgu.ac.il\\}
 \maketitle
 \begin{abstract}
-We present an efficient algorithm that, given a discrete random variable $X$ and a number $m$, computes a random variable whose support if of size at most $m$ and whose Kolmogorov distance from $X$ is minimal.
-We present the algorithm, analyse its correctness and computational complexity, and present a detailed empirical evaluation that shows how it performs in practice.
+We present an efficient algorithm that, given a discrete random variable $X$ and a number $m$, computes a random variable whose support is of size at most $m$ and whose Kolmogorov distance from $X$ is minimal.
+We present some variants of the algorithm, analyse their correctness and computational complexity, and present a detailed empirical evaluation that shows how they performs in practice.
 The main application that we examine, which is our motivation for this work, is estimation of the probability missing deadlines in series-parallel schedules.
-Since exact computation of these probabilities is NP-hard, we propose to use the algorithm described in this paper to obtain an approximation.
+Since exact computation of these probabilities is NP-hard, we propose to use the algorithms described in this paper to obtain an approximation.
 \end{abstract}
@@
 In this paper we propose an approach for compressing the probability mass function of a random variable $X$ such that the errors added to queries such as $Pr(X\leq t)$, for  any $t>0$, is minimal.
-In other words, we minimise the Kolmogorov distance between the approximation and the original random variable.
-Our motivation for this is estimation of the probability for missing deadlines, as described, e.g., in Cohen et al.~\cite{cohen2015estimating,CohenGW18} and in~\cite{Kashef18}.
+In other words, we minimise the Kolmogorov distance between the approximation and the original variable, see alternative definition in Equation~\eqref{eq:linear}.
+
+Our main motivation for this work is estimation of the probability for missing deadlines, as described, e.g., in Cohen et al.~\cite{cohen2015estimating,CohenGW18} and in~\cite{Kashef18}.
 Specifically, when $X$ represents the probability distribution of the time to complete some complex schedule and we cannot afford to maintain the full table of its probability mass function, we propose an algorithm for producing a smaller table, whose size can be specified, such that probabilities for missing deadlines are preserved as much as possible.
@@
 
-The case study examined in this paper is the problem of task trees with deadlines~\cite{cohen2015estimating,CohenGW18}.
+%The case study examined in this paper is the problem of task trees with deadlines~\cite{cohen2015estimating,CohenGW18}.
 A hierarchical plan is a method for representing problems of automated planning in which the dependency among tasks can be given in the form of networks, here we focus on hierarchical plans represented by task trees.
@@
 
-A sequence node denotes a series of tasks that should be performed consecutively, whereas a parallel node denotes a set of tasks that begin at the same time.
+%A sequence node denotes a series of tasks that should be performed consecutively, whereas a parallel node denotes a set of tasks that begin at the same time.
 A \emph{valid} plan is one that is fulfilled before some given \emph{deadline}, i.e., its \emph{makespan} is less than or equal to the deadline.
@@
 
-The size of a random variable is measured here by the size of its support, the set of possible outcomes, $|X|=|X|=|\{x\colon Pr(X=x) \neq 0\}|$.
-When probability mass functions are maintained as explicit tables, as done in many implementations of statistical software, the size of the support of the variable is proportional to the amount of memory needed to store it and to the complexity of the computations that manipulate it.
+The size of a random variable is measured by the size of its support, the set of possible outcomes, $|X|{=}|\{x\colon Pr(X{=}x) \neq 0\}|$.
+When probability mass functions are maintained as tables, as done in many implementations of statistical software, the support size is proportional to the memory needed to store the variable and to the complexity of the computations that manipulate it.
+The exact notion of optimality of the approximation targeted in this paper is:
 
-Together, the exact notion of optimality of the approximation targeted in this paper is:
 \begin{definition}
@@
 
-In these terms, the main contribution of the paper is an efficient (polynomial time and memory) algorithm that takes $X$ and $m$ as parameters and constructs an optimal $m$-approximation of $X$.
+In these terms, the main contribution of the paper is an efficient (linear time and constant memory) algorithm that takes $X$ and $m$ as parameters and constructs an optimal $m$-approximation of $X$.
 
@@
 The motivation given in these papers for using this type of approximation is for cases where overestimation of the probability of missing a deadline is acceptable but underestimation is not.
-In Section~\ref{sec:exp}, we consider the same case-studies examined by Cohen et al.
+We consider in this paper the same case-studies examined by Cohen et al.
 and show how the algorithm proposed in this paper performs relative to the algorithms proposed there when both over- and under- estimations are allowed.
@@
 These cannot be addressed by adding a constant (two) to $m$ because the first step is always present and because the requirement to end with the value one, restricts the set of eligible step functions.
-See Section~\ref{sec:algEfficient} for more details.
 
 Another relevant prior work is the theory of Sparse Approximation (aka Sparse Representation) that deals with sparse solutions for systems of linear equations, as follows. 
-Given a matrix $D \in \mathbb{R}^{n \times p}$ and a vector $x \in \mathbb{R}^n$, the most studied sparse representation problem is finding the sparsest possible representation $\alpha \in \mathbb{R}^p$ satisfying $x = D\alpha$:
-\[
+Given a matrix $D \in \mathbb{R}^{n \times p}$ and a vector $x \in \mathbb{R}^n$, the most studied sparse representation problem is finding 
+%the sparsest possible representation $\alpha \in \mathbb{R}^p$ satisfying $x = D\alpha$:
+$$
 \min_{\alpha \in \mathbb{R}^p} \|\alpha\|_0 \text{ subject to } x = D\alpha
-\]
+$$
 where $\|\alpha\|_0 = |\{ i \in [p]: \alpha_i \neq 0 \}|$ is the $\ell_0$ pseudo-norm, counting the number of non-zero coordinates of $\alpha$.
@@
 In these terms, using also the $\ell_\infty$ norm that represents the maximal coordinate and the $\ell_1$ norm that represents the sum of the coordinates, our problem can be phrased as:
-\[
+\begin{equation}\label{eq:linear}
 \min_{\alpha \in [0,\infty)^p}\|x - D\alpha\|_{\infty} \text{ subject to }  \|\alpha\|_0 = m \text{ and } \|\alpha\|_1=1
-\]
+\end{equation}
 where $D$ is the lower unitriangular matrix, $x$ is related to $X$ such that the $i$th coordinate of $x$ is $F_X(x_i)$ where $\support(X)=\{x_1 < \cdots < x_n\}$ and $\alpha$ is related to $X'$ such that the $i$th coordinate of $\alpha$ is $f_{X'}(x_i)$.
 The functions $F_X$ and $f_{X'}$ represent, respectively, the cumulative distribution function of $X$ and the mass distribution function of $X'$, i.e.,  the coordinates of $x$ are positive and monotonically increasing and its last coordinate is one.
-We show that this specific sparse representation problem can be solved in $O(n^2m)$ time and $O(m^2)$ memory.
+%We show that this specific sparse representation problem can be solved in $O(n^2m)$ time and $O(m^2)$ memory.
 
-%The presented work is also related to the research on binning in statistical inference.
+The presented work is also related to the research on binning in statistical inference.
 Consider, for example, the problem of credit scoring~\cite{zeng2017comparison} that deals with separating good applicants from bad applicants where the Kolmogorov–Smirnov statistic KS is a standard measure.
-The KS comparison is often preceded by a procedure called binning where small values in the the probability mass function are moved to nearby values.
+The KS comparison is often preceded by a procedure called binning where small values in the probability mass function are moved to nearby values.
 There are many methods for binning~\cite{mays2001handbook,refaat2011credit,bolton2010logistic,siddiqi2012credit}.
-%In this context, our algorithm can be considered as a binning strategy that provides optimality guarantees with respect to the Kolmogorov distance.
+In this context, our algorithm can be considered as a binning strategy that provides optimality guarantees with respect to the Kolmogorov distance.
 
@@
 There, the author defines an information-theoretic based distance between discrete random variables and studies the problem of finding a variable whose support is of size $m$ and its distance from $X$ is as small as possible (where $X$ and $m$ are given).
-The only difference between this and the problem studied in this paper, is that Vidyasagar examines a different notion of distance.
+The main difference between this and the problem studied in this paper, is that Vidyasagar examines a different notion of distance.
 Vidyasagar proves that computing the distance (that he considers) between two probability distributions, and computing the optimal reduced order approximation, are both NP-hard problems, because they can both be reduced to nonstandard bin-packing problems.
@@
 \section{Algorithms for optimal approximation}\label{sec:algEfficient}
-%In the scope of this section, let $X$ be a random variable ket $m$ be such that  $0<m\leq |X|$. We present algorithms for finding optimal $m$-approximations of $X$.
-
-We begin with presenting an algorithm for solving a problem that is dual to the $m$-approximation problem.
-The dual problem is: given a random variable $X$ and $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $d_k(X,X')\leq \varepsilon$ and $|X'|$ is minimal.
+We begin with presenting an algorithm for solving a problem that is dual to the $m$-approximation problem: given a random variable $X$ and $0 \leq \varepsilon \leq 1$, find a new random variable $X'$ such that $d_k(X,X')\leq \varepsilon$ and $|X'|$ is minimal.
 
 We assume that the input to Algorithm~\ref{alg:dual} that solves the dual problem is a representation of the variable $X$ as a sorted CDF, i.e.,  as an array $X_{CDF}=\{(x_i, c_i)\}_{i=1}^n$ such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.
-In lines 2 we perform a single pass over $X_{CDF}$ starting from index 1 to find the last index where the cumulative distribution function of $X$ is less than $\varepsilon$, this index is now $f$.
-In line 3 we start from the last index of $X_{CDF}$ which is $n$, and in decreasing order seek for the last index where the cumulative distribution function of $X$ is less than $1-\varepsilon$, this index is now $l$.
-The last part of the algorithm is a pass on all elements in $X_{CDF}$ between the indices $f$ and $l$ in order to construct the $m$-approximation random variable of $X$, $X'$.
+In line~2 we perform a single pass over $X_{CDF}$ starting from the first index to find the last index where the cumulative distribution function of $X$ is less than $\varepsilon$, this index is stored in the variable $f$.
+In line 3 we start from the last index of $X_{CDF}$ which is $n$, and seek in decreasing order for the last index where the cumulative distribution function of $X$ is less than $1-\varepsilon$.
+This index is stored at the variable $l$.
+The last part of the algorithm is a pass on all elements of $X_{CDF}$ between the indices $f$ and $l$ in order to construct the random variable $X'$.
 In lines 6-7 we check if the difference between the first element in the current set of indices (which we call $b$) and the last element in the current set of indices (which we call $e+1$) is less than $2\varepsilon$.
-If yes, we add the pair $\{(x_{b}, (c_b+c_e)/2 - s) \}$ to the set $S$.
-Otherwise, we add one to the counter of $e$.
+If yes, we add the pair $(x_{b}, (c_b+c_e)/2 - s)$ to the set $S$.
+Otherwise, we add one to $e$.
+See running Example~\ref{exmpl:dual}.
 
@@
 	%Let $\{(x_i, c_i)\}_{i=1}^n$ be such that $c_i = Pr(X \leq x_i)$ and $\supp(X)=\{x_1 <\cdots < x_n\}$.\;
-    $f \gets 0$, $l \gets n$+1\; 
-    \lWhile{$c_{f +1} \leq \varepsilon$}{$f \gets f + 1$}
+    $f \gets 1$, $l \gets n$+1\; 
+    \lWhile{$c_{f} \leq \varepsilon$}{$f \gets f + 1$}
 
@@
 	\While{$e<l$}{
-	    \While{$c_{e+1}-c_{b} \leq 2\varepsilon \wedge e+1 <l$}{$e \gets e+1$}
+	    \While{$c_{e+1}-c_{b} \leq 2\varepsilon \wedge e <l$}{$e \gets e+1$}
 	    $S \gets S \cup \{(x_{b}, (c_b+c_e)/2 - s) \}$\;
-        $s \gets  (c_b+c_e)/2$, $b \gets e+1$\;
+        $s \gets  (c_b+c_e)/2$, $b \gets e\gets e+1$\;
 	}
@@
 \SetKwRepeat{Do}{do}{while}
-%which c? why -s? name without any meaning, cant understand
 
-\begin{theorem}\label{the:correctnessDual}
+\begin{example}
+\label{exmpl:dual}
+When $dual$ is invoked with the parameters  $X{=}\{(1, 0.3), (2, 0.7), (3, 0.9), (4,1)\}$ and $\varepsilon{=}0.1$: Lines 2 and 3 set $f=1$ and $l=4$.
+After an iteration of the main loop (line 5), $S = \{(1,0.3)\}$, $s=0.3$, and $b=e=2$.
+After a second iteration, $S = \{(1,0.3), (2, 0.5)\}$, $s=0.8$, and $b=e=4$.
+At the end, $S = \{(1,0.3), (2, 0.5), (4, 0.2)\}$.
+\end{example}
+
+\begin{proposition}\label{the:correctnessDual}
 	If  $\{(x_i, c_i)\}_{i=1}^n$ is such that $c_i=Pr(X \leq x_i)$ and $\supp(X)=\{x_1 < \cdots < x_n\}$ then  
     $$dual(\{(x_i, c_i)\}_{i=1}^n,\varepsilon) \in \underset{X'\in \bar{\mathcal{B}}(X,\varepsilon)}{\operatorname{arg\,min}}\, |X'|$$  where $\bar{\mathcal{B}}(X,\varepsilon)=\{X'\colon d_K(X,X')\leq \varepsilon\}$.
-\end{theorem}
+\end{proposition}
 \begin{proof}
 The number of level sets of the CDF of $X'$ is minimal: (1) The first and the last sets are of maximal length; (2) By construction, an extension of any of the other sets to the right will generate a random variable whose Kolmogorov distance from $X$ is bigger than $\varepsilon$; and (3) Extension of a level set to the left may either leave the number of level sets unchanged or combine it with the previous set, which will enlarge the Kolmogorov distance because it is equivalent to extending the previous set to the right.
+Thus, there is no random variable whose Kolmogorov distance from $X$ is smaller or equal to $\varepsilon$ and its support is smaller than $|X'|$.
 \end{proof}
 
-\begin{theorem}\label{the:complexityDual}
+\begin{proposition}\label{the:complexityDual}
 	$dual(\{(x_i, c_i)\}_{i=1}^n,\varepsilon)$ runs in time $O(n)$, using $O(n)$ memory.
-\end{theorem}
+\end{proposition}
 \begin{proof}
 This algorithm describes a single pass over $\{(x_i, c_i)\}_{i=1}^n$.
-Line 2 and line 3 are easy to follow, each takes $O(n)$ in the worst case.
+Lines 2 and 3 are easy to follow, each takes $O(n)$ in the worst case.
 Lines 5-9 also describe a single pass since the counter $e$ is updated to $e+1$ at most $n$ times.
 All together we get run-time complexity of $O(n)$.
-We are constructing the set $S$ which is of size $n$ in the worst case, therefore, memory complexity is also $O(n)$.
+We are constructing the set $S$ which is of size $n$ in the worst case, therefore, memory complexity is $O(n)$.
 \end{proof}
 
-The first technique we present is the $binsApprox(X,m)$ algorithm which is based on the work done by D{\'i}az-B{\'a}nez and Mesa~\cite{diaz2001fitting}.
+The first solution to the $m$-approximation problem we present is the $binsApprox(X,m)$ algorithm which is based on~\cite{diaz2001fitting}.
 There are couple of significant changes between our $binsApprox(X,m)$ algorithm and the algorithm suggested by D{\'i}az-B{\'a}nez and Mesa~\shortcite{diaz2001fitting} addressing the differences presented in the Related work section.
@@
 If the size of $|X'|>m$ then we know that the error $\varepsilon$ is too small and need to extend the search in the right side of $E$, if the size of $|X'|<m$ then we know that the error $\varepsilon$ is too big and need to extend the search in the left side of $E$, otherwise we found the correct $m$.
-We run the search twice to handle the extreme case where $m \notin \{\forall \varepsilon\in E: |dual(X,\varepsilon)|\}$ and return the smallest $m'$ closest to $m$.
+We run the search twice to handle the extreme case where $m \notin \{|dual(X,\varepsilon)| \colon \varepsilon\in E \}$.
+In this case we may end up with a variable that is not optimal because it can be improved by using $m''$ such that $m < m'' < m'$.
+We find the optimal $m''$  by the second round ($i=2$) that run after line 18 that sets $m$ to be the $m'$ found in the first round.
 
@@
 
-\begin{theorem}\label{the:correctnessBinsearch}
-
-    $binsApprox(X,m) \in \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
-\end{theorem}
+\begin{proposition}\label{the:correctnessBinsearch}
+	    $binsApprox(X,m) \in \underset{|X'| \leq m }{\operatorname{arg\,min}}\, d_K(X,X')$
+%     $binsApprox(X,m) \in \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
+\end{proposition}
 \begin{proof}
-Since lines 10-18 is a binary search of the smallest $e_k\in E$ such that $|dual(X,e_k)|\leq m$, we only need to prove that $E=E'=\{ d_K(X,dual(X,m)) \colon m=1,\dots,n\}$.
-To see that this is true, note that every element in $E'$ corresponds to a distance of a level set of the CDF of $dual(X,m)$ from the CDF of $X$.
-Line 6 of the algorithm adds all the distances from level sets of height zero, Line 8 adds the distances from level sets of heigt one, and Line 7 adds all the distances from all other possible level sets.
+Since lines 10-18 is a binary search of the smallest $e_k\in E$ such that $|dual(X,e_k)|\leq m$, we only need to prove that $E=E'=\{ d_K(X,dual(X,e_m)) \colon m=1,\dots,n\}$.
+To see that this is true, note that every element in $E'$ corresponds to a distance of a level set of the CDF of $dual(X,m)$ from the CDF of $X$ (because we seek a variable whose support is included in the original one).
+Line 6 of the algorithm adds all the distances from level sets of height zero, Line 8 adds the distances from level sets of height one, and Line 7 adds all the distances from all other possible level sets.
+Note that the distance is monotonic with the support size.
 \end{proof}
 
-\begin{theorem}\label{the:complexityBinsearch}
+\begin{proposition}\label{the:complexityBinsearch}
 	The $binsApprox(X,m)$ algorithm runs in time $O(n^2log(n))$, using $O(n^2)$ memory where $n=|X|$.
-\end{theorem}
+\end{proposition}
 \begin{proof}
@@
 \begin{proof}
-CDF representation of a random variable is a monotonically increasing function.
-Therefore, $\forall i,j$, $ 0\leq c_i - c_{n+1-j}\leq c_i - c_{n+1-(j+1)} $ and $ \forall i,j$, $0 \leq c_i - c_{n+1-j}\leq c_{i+1} - c_{n+1-j} $, moreover, 0 is the minimal value of $E$.
+Since the $c_i$s are monotonically increasing, $\forall i,j$, $ 0\leq c_i - c_{n+1-j}\leq c_i - c_{n+1-(j+1)} $ and $ \forall i,j$, $0 \leq c_i - c_{n+1-j}\leq c_{i+1} - c_{n+1-j} $, moreover, 0 is the minimal value of $E$.
 The elements in the last row and the last column in $E$ are keeping the terms of sorted matrix.
@@
 This assures that the minimal $e$ such that $|dual(X,e)| \leq m$ is visited after at most $n+1$ steps.
-Data is collected along the traversal and the optimal random variable is found by brute-force.
+The optimal random variable is found by brute-force search over the visited entries.
 
@@
 		\lIf {$m' > m$} {
-			$i \gets i + 1$, $S \gets S \cup (m',e)$			
+			$i \gets i + 1$
 		}
+		\lIf {$m' \geq m$} {
+			$S \gets S \cup (m',e_{i,j})$			
+		}
+
 	}
@@
 
-\begin{theorem}\label{the:correctnessSaddleback}
-
-    $sdlbkApprox(X,m) {\in} \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
-\end{theorem}
+\begin{proposition}\label{the:correctnessSaddleback}
+	   $sdlbkApprox(X,m) {\in} \underset{|X'| \leq m }{\operatorname{arg\,min}}\, d_K(X,X')$
+%     $sdlbkApprox(X,m) {\in} \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
+\end{proposition}
 \begin{proof}
@@
 
-\begin{theorem}\label{the:complexitySaddleback}
+\begin{proposition}\label{the:complexitySaddleback}
 	The $sdlbkApprox(X,m)$ algorithm runs in time $O(n^2)$, using $O(n)$ memory where $n=|X|$.
-\end{theorem}
+\end{proposition}
 \begin{proof}
 	At each step of the loop in lines 3-6, either $j$ decreases or $i$ increases, thus the loop can be executed at most $2n$ times.
-Since we execute $dual$ once ion a loop round, the total time complexity is $O(n^2)$.
+Since we execute $dual$ once in a loop round, the total time complexity is $O(n^2)$.
 Storing visited states in $S$ on line 6 requires  $O(n)$ memory.
@@
 The problem with the saddleback algorithm is that it needs to run $dual$ at every step so it has a quadratic time complexity.
-Since we cannot find the required entry of the matrix in less than $n$ steps, we can only reduce the complexity by proposing an algorithm that does not executes $dual$ in all the steps, only in $\log(n)$ of them.
-Such an algorithm, based on Section~2.1 in~\cite{Fournier2011}, is listed as Algorithm~\ref{alg:linear}.
-The algorithm maintains a set $S$ of sub-matrices.
+Since we cannot find the required entry of the matrix in less than $n$ steps, we can only reduce the complexity by proposing an algorithm that does not execute $dual$ in all the steps, only in $\log(n)$ of them.
+Such an algorithm, based on Section~2.1 of~\cite{Fournier2011}, is listed as Algorithm~\ref{alg:linear}.
+The algorithm maintains a set $S$ of sub-matrices of $(e_{i,j})_{i=1..2^{\lceil \log_2(n) \rceil},j=1..2^{\lceil \log_2(n+1) \rceil}}$.
 At each round of its execution, each sub-matrix is split to four and then about three quarters of the matrix are discarded.
 At the end, at most four scalar matrices remain containing the index of the entry we seek.
+Note that this algorithm runs on a matrix that, in the worst case, can be almost four times bigger than the matrix traversed by the saddleback algorithm.
+This, of course, does not affect the asymptotic  complexity, but it may matter when dealing with relatively small random variables.
 
@@
 
-		$S \gets  \{ ((1, 1),(n,n+1)) \}$, $S' \gets \emptyset$\;
+		$S \gets  \{ ((1, 1),
+		( 2^{\lceil \log_2(n) \rceil},2^{\lceil \log_2(n+1) \rceil})) \}$, $S' \gets \emptyset$\;
 
@@
 {
-	\begin{algorithm}
+	\begin{function}
 		\DontPrintSemicolon
@@
 
-		\caption{$split(((i_1,j_1),(i_2,j_2)))$}
+		\caption{{$split(((i_1,j_1),(i_2,j_2)))$}()}
 		\label{proc:split}
-	\end{algorithm}
+	\end{function}
 }
@@
 
-    $linApprox(X,m) {\in} \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
+   $linApprox(X,m) {\in} \underset{|X'|\leq m}{\operatorname{arg\,min}}\, d_K(X,X')$
+
+    % $linApprox(X,m) {\in} \underset{X' \in \bar{\mathcal{B}}(X,m) }{\operatorname{arg\,min}}\, d_K(X,X')$ where $\bar{\mathcal{B}}(X,m)=\{X'\colon |X'| \leq m\}$.
 \end{theorem}
@@
 
+% \begin{example}\label{exmpl:dual}
+% \small
+% Let $X$ be such that $P(X {\leq} 1) {=} 0.333$, $P(X {\leq} 2) {=} 0.733$, $P(X {\leq} 3) {=} 0.9$, and $P(X{\leq} 4) {=} 1$ and $\varepsilon = 0.0833$.
+After lines 2, 3 of Algorithm~\ref{alg:dual}, $f{=}1$ and $l{=}4$.
+The first iteration (line 5) starts with $b{=}e{=}1$, and since $1{<}4$ we enter the first loop but not the second loop (line 6) because $0.733{-}0.333 {>} 0.166$.
+This iteration results with $S {=} \{(1,0.333)\}$, $s{=}0.333$, and $b{=}e{=}2$.
+In the second iteration we enter the first loop since $2{<}4$ and also the second loop because $0.9 {-} 0.7333 {\leq} 0.166$, and now $e{=}3$.
+Next we check if $1-0.733 {\leq} 0.166$ which is not true, therefore we exit the second loop.
+This iteration results with $S {=} \{(1,0.333), (2, 0.483)\}$, $s{=}0.816$, and $b{=}e{=}4$.
+The run ends with $S {=} \{(1,0.333), (2, 0.483), (4, 0.183)\}$.
+Note that the set $S$ represents the approximation random variable $X'$ whose support is of size 3 and the $d_K(X,X'){=}0.0833$.
+% \end{example}
+
+% \begin{example}[Dual algorithm running example]\label{exmpl:dual}
+% Given the random variable $X$ in CDF representation: $P(X \leq 1) = 0.333, P(X \leq 2) = 0.733, P(X \leq 3) = 0.9, P(X\leq 4) = 1$ and some error $\varepsilon = 0.0833$.
+The dual algorithm first look for the range of $f$ and $l$.
+In this example, after running lines 2, 3: $f=1$ and $l=4$.
+The first iteration (line 5) starts with $b=e=1$, and since $1<4$ we enter the first loop but not the second loop (line 6) because $0.733-0.333 > 0.166$.
+This iteration results with $S = \{(1,0.333)\}, s=0.333, b=e=2$.
+In the second iteration we enter the first loop since $2<4$ and also the second loop because $0.9 - 0.7333 \leq 0.166$, and now $e=3$.
+Next we check if $1-0.733\leq 0.166$ which is not true, therefore we exit the second loop.
+This iteration results with $S = \{(1,0.333), (2, 0.483)\}, s=0.816, b=e=4$.
+The run ends with $S = \{(1,0.333), (2, 0.483), (4, 0.183)\}$.
+Note that the set $S$ represents the approximation random variable $X'$ which his support is of size 3 and the $d_K(X,X')=0.0833$.
+% \end{example}
+
 \section{Experimental evaluation}\label{sec:exp}
@@
 Previous work such as the work of Cohen et al.
-in ~\shortcite{cohen2015estimating,CohenGW18} handle this reduction using weaker or sub-optimal notion of approximation than ours, as discussed in Section~\ref{sec:relwork}.
+in ~\shortcite{cohen2015estimating,CohenGW18} handle this reduction using weaker or sub-optimal notion of approximation than ours.
 
-As proven in Section~\ref{sec:algEfficient}, given $m$, a single step of $\KlmApprox$ guarantees an optimal $m$-approximation.
+As we proved above, given $m$, a single step of $\KlmApprox$ guarantees an optimal $m$-approximation.
 However in the setting considered here we need to repetitively use $\KlmApprox$, thus the optimality of the eventually obtained random variable is not guaranteed.
@@
 We estimated the probability for meeting deadlines in plans, as described in Cohen et al.~\shortcite{cohen2015estimating,CohenGW18}, and experimented with four different methods of approximation.
-The first two, $\OptTrim$~\cite{CohenGW18} and the $\Trim$~\cite{cohen2015estimating}, are taken from the repository provided by the authors and are designed for achieving only a one-sided Kolmogorov approximation - a  weaker notion of approximation then the Kolmogorov approximation analyzed in this work.
+The first two, $\OptTrim$~\cite{CohenGW18} and the $\Trim$~\cite{cohen2015estimating}, are taken from the repository provided by the authors and are designed for achieving only a one-sided Kolmogorov approximation - a  weaker notion of approximation than the Kolmogorov approximation analyzed in this work.
 The third method is a simple sampling scheme and the fourth is our Kolmogorov approximation obtained by the proposed $\KlmApprox$ algorithm.
@@
 The quality of the solutions obtained with the $\KlmApprox$ operator are better than those obtained by the $\Trim$ and $\OptTrim$ operators as expected.
-In some of the task trees, the sampling method produced better results than the approximation algorithm with $\KlmApprox$.
-Still, the $\KlmApprox$ approximation algorithm comes with an inherent advantage of providing an exact quality guarantees, as opposed to sampling where the best one can hope for is probabilistic guarantees.
+In some of the task trees, the sampling method produced better results than $\KlmApprox$.
+Still, the $\KlmApprox$ approximation algorithm comes with an inherent advantage of providing exact quality guarantees, as opposed to sampling where the best one can hope for is probabilistic guarantees.
 
-\paragraph{Run time comparison.}
+\paragraph{Run-time comparison.}
 Similarly to accuracy and error computation, we also conducted empirical evaluation to examine the run-time in practice of the discussed algorithms.
@@
 These results illuminate the advantage of the proposed $\KlmApprox$ algorithm that balances between solution quality and run-time performance -- while there exist other, faster, methods (e.g., $\Trim$), $\KlmApprox$ provides high-quality solutions in $O(n log(n))$ time, which is especially important when an exact computation is not feasible, due to time or memory.
-In general, Figure~\ref{fig:runtime} is consistent with the theory and show a good fit to the complexity analysis presented in Section~\ref{sec:algEfficient}.
+In general, Figure~\ref{fig:runtime} is consistent with the theory and show a good fit to the complexity analysis.
 
@@
 	xmin=6, xmax=19,
-	ymin=0, ymax=327,
+	%ymin=0, 
+	ymax=327,
 	xtick={6,10,15,19},
@@
 	\end{tikzpicture}
-	\caption{Run-time of a long computation with $\KlmApprox$, $\BinsApprox$, $\OptTrim$, $\Trim$, and without any trimming (exact computation).}
+	\caption{Run-time of a long computation with $\KlmApprox$, $\BinsApprox$, $\OptTrim$, $\Trim$, and without any trimming.}
 	\label{fig:runtime}
@@
 \paragraph{Single step support minimisation.}
-In order to better understand the quality gaps in practice between $\KlmApprox$, $\OptTrim$, and $\Trim$, we tested their relative errors when applied on single random variables with support size $n = 100$, and different $m$s.
+To better understand the quality gaps in practice between $\KlmApprox$, $\OptTrim$, and $\Trim$, we tested their performance on random variables with $n{=}100$, and different $m$s.
 Note that the error obtained by $\KlmApprox$ is optimal while the other methods are not optimised for the Kolmogorv distance.
-In each instance of this experiment, a random variable is randomly generated by choosing the probabilities of each element in the support uniformly and then normalising these probabilities so that they sum to one.
+In each instance of the experiment, a random variable is randomly generated by choosing the probabilities of each element in the support uniformly and then normalise these probabilities to sum to 1.
 
@@
 It is evident from this graphs that increasing the support size of the approximation $m$ reduces the error, as expected, in all three methods.
-However, the (optimal) errors produced by the $\KlmApprox$ are significantly smaller, a half of the error produced by $\OptTrim$ and $\Trim$.
+However, the errors produced by the $\KlmApprox$ are significantly smaller, a half of the error produced by $\OptTrim$ and $\Trim$.
 
@@
 	\end{tikzpicture}
-	\caption{Error comparison between $\KlmApprox$, $\OptTrim$, and $\Trim$ on randomly generated random variables as function of $m$.}
+	\caption{Error comparison between $\KlmApprox$, $\OptTrim$, and $\Trim$ on randomly generated variables as function of $m$.}
 	\label{fig:error}
@@
 \paragraph{Comparison to Linear Programming.}
-We also compared the run-time of $\KlmApprox$ with a linear programming (LP) algorithm that also guarantees optimality, as described and discussed for example in~\cite{pavlikov2016cvar}.
-For that, we used the ``Minimize'' function of Wolfram Mathematica as a  state-of-the-art implementation of linear programming, encoding the problem by the LP problem $\min_{\alpha \in \mathbb{R}^n} \| x - \alpha\|_\infty$ subject to $\|\alpha\|_0 \leq m$ and $\| \alpha \|_1 =1$.
+We also compared the run-time of $\KlmApprox$ with a linear programming (LP) algorithm that guarantees optimality, as described and discussed in~\cite{pavlikov2016cvar}.
+We used the ``Minimize'' function of Wolfram Mathematica as a state-of-the-art implementation of linear programming, encoding the problem by the LP problem $\min_{\alpha \in \mathbb{R}^n} \| x - \alpha\|_\infty$ subject to $\|\alpha\|_0 \leq m$ and $\| \alpha \|_1{=}1$.
 The run-time comparison results were clear and persuasive: $\KlmApprox$ significantly outperforms the LP algorithm.
-For a random variable with support size $n=10$ and $m=5$, the LP algorithm run-time was $850$ seconds, where the $\KlmApprox$ algorithm run-time was less than a tenth of a second.
-For $n=100$ and $m=5$, the $\KlmApprox$ algorithm run-time was 0.14 seconds and the LP algorithm took more than a day.
-Since it is not trivial to formally analyze the run-time of the LP algorithm, we conclude by the reported experiment that in this case the LP algorithm might not be as efficient as $\KlmApprox$ algorithm.
+For a random variable with support size $n{=}10$ and $m=5$, the LP algorithm run-time was $850$ seconds, where the $\KlmApprox$ algorithm run-time was less than a second.
+For $n{=}100$ and $m{=}5$, the $\KlmApprox$ algorithm run-time was 0.14 seconds and the LP algorithm took more than a day.
+Since it is not trivial to formally analyze the run-time of the LP algorithm, we conclude by the reported experiment that in this case the LP algorithm might not be as efficient as $\KlmApprox$.
 
@@
 As demonstrated in the experiments, our algorithm improves on the approach of Cohen et al.~\shortcite{cohen2015estimating} and~\shortcite{CohenGW18} in that it finds an optimal two sided Kolmogorov approximation, and not just one sided.
+In addition, the algorithm $\KlmApprox$ presented in this paper is very efficient with complexity of $O(n log(n))$ as proved in Theorem~\ref{the:complexityLinear} and showed in Figure~\ref{fig:runtime}.
 Beyond the Kolmogorov measure studied here, we believe that similar approaches may apply also to total variation, to the Wasserstein distance, and to other measures of approximations.
-Another direction for future work is extensions to tables that represent other objects, not necessarily random variables.
+%Another direction for future work is extensions to tables that represent other objects, not necessarily random variables.
 To this end, we need to extend the algorithm to support tables that do not always sum to one and tables that may contain negative entries.
+
+%\begin{example}
+%Given $m=3$ and the random variable $X$ in CDF representation: $P(X \leq 1) = 0.3333, P(X \leq 2) = 0.7333, P(X \leq 3) = 0.9, P(X\leq 4) = 1$.
+Find an approximation of $X$ with support of size 3.
+First step, find all differences: $E= \{0, 0.05, 0.0833, 0.1, 0.133, 0.2, 0.266, 0.2833, 0.333, 0.666,\\ 0.7333, 0.9, 1\}$.
+Next, perform a binary search over $E$, in order to compute the dual support size.
+Starting with $E[7] = 0.266$ results with support size of 2, therefore, we adjust the search to smaller $E$ values, in this case $E[3] =  0.0833$ where the dual support size is 3.
+Even though $m=3$, we also seek for optimal (minimal) error, leading to check $e[2]=0.05$ as well which produce dual support size of 4.
+Therefore, we know $\varepsilon =  0.0833$ is the optimal error for $m=3$.
+%\end{example}
+
+\paragraph{Acknowledgments.} This research was supported by the Lynn and William Frankel Centre for Computer Science at Ben-Gurion University and by the Israel Science Foundation.
 
